### 2022-10-06 paper.tex
first commit

% Template for ICASSP-2021 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\input{preamble.tex}

% Title.
% ------
\title{SOMETHING ABOUT THE DISTRIBUTED AVERAGING BASED APPROXIMATION IN SENSOR NETWORKS}
%
% Single address.
% ---------------
\name{Matthias Blochberger\(^1\), Filip Elvander\(^2\), Toon, ...\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network. This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.}}
\address{\(^1\)KU Leuven, Dept. of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept. of Signal Processing and Acoustics, 02150 Espoo, Finland}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
% \twoauthors{M. Blochberger
%     \thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network. This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369. This research received funding in part from the Research Foundation - Flanders (FWO) grant 12ZD622N.}}
%         {KU Leuven\\
%         Dept. of Electrical Engineering (ESAT), STADIUS\\
%         % STADIUS\\
%         3001 Leuven, Belgium}
%         {Filip Elvander}
%         {Aalto University\\
%         Dept. of Electronic Systems\\
%         % Section on Artificial Intelligence and Sound\\
%         9220 Aalborg, Finland}
%
\begin{document}
% \ninept
%
\maketitle
%
\begin{abstract}
  Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce transmission cost and computational complexity or avoid reliance on a single device for processing. In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the knowledge of a stacked network-wide solution vector at each node, the computation of which requires either broadcasting or relaying of node-specific values to all other nodes. The extended algorithm employs a distributed-averaging-based estimation scheme to estimate the network-wide norm value by only using the information provided by neighboring sensor nodes. We introduce a mixing factor between instantaneous and recursion values for adaptivity in a time-varying system. The extension leads to a decreased number of transmissions while maintaining estimation performance close to the optimal case. Simulation results show how the mixing factor and the averaging scheme's number of iterations influence performance.
\end{abstract}
%
\begin{keywords}
multi-channel signal processing, distributed signal processing, wireless sensor networks, blind system identification, distributed averaging
\end{keywords}
%
\section{INTRODUCTION}
\label{sec:intro}

Main contribution: Avoid broadcasting or relaying of norm values, with distributed averaging approach and low iteration count.
Algorithms using a similar approach: \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, however these use high numbers of iterations (30) which leads to many per-frame transmissions.
Argument against broadcasting: (1)Large-scale networks, where not all nodes can physically communicate with each other, but that is not really that relevant for room acoustics... (2) just because. this is the network topology and configuratinos that was chosen as in a lot of literature.

Important context in introduction: BSI, WSN, topology, connection matrix,

What to show:
\begin{itemize}
  \item Algorithm extension
  \item Results
  \begin{itemize}
    \item compare results of unextended algorithm (optimal case)
    \item with extended: varied iteration count (more iterations: better result, BUT also even 1 iteration can lead to good results)
    \item varied mixing factor (there is some optimal \(\gamma\) apparently)
    \item Show transmission cost: transmission cost over number of nodes
  \end{itemize}
\end{itemize}

\section{DISTRIBUTED ADAPTIVE BLIND SYSTEM IDENTIFICATION}
\label{sec:dbsi}
Introduction of the algorithm from iwaenc paper. \cite{blochbergerDBSI}
\begin{align}
  \wf_i^{k+1} &= \underset{\wf_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\wf,\hf^k,\uuf^k)\label{eq:general_consensus_admm:local}\\
  \hf^{k+1} &= \underset{\hf, \|\hf\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\wf^{k+1},\hf,\uuf^k)\label{eq:general_consensus_admm:global}\\
  \uuf_i^{k+1} &= \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right),\label{eq:general_consensus_admm:dual}
\end{align}

The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
\begin{equation}
    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right),\label{eq:online_admm:local_update}
\end{equation}
where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the regularized inverse Hessian of the problem.
The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce computational complexity, we introduce the approximation
\begin{equation}
    \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1},
\end{equation}
which is straightforward to compute.
It may be readily verified (cf. \cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by an update step which computes
\begin{equation}
    \hf_i^{m+1} = \frac{\bar{\hf}_i^{m+1}}{\sqrt{\sum_{j \in \Mset} \|\bar{\hf}_j^{m+1}\|^2}}\label{eq:online_admm:consensus_update}
\end{equation}
for each node \(i \in \Mset\) with the local unnormalized consensus
\begin{equation}
    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}.
\end{equation}
Here, \(\bar{\wf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\wf_j)_i\) and \(\bar{\uuf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uuf_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) respectively, computed at node \(i\). The values of all \(\|\bar{\hf}_i^{m+1}\|^2\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
Finally, the update of the dual variables is given by
\begin{equation}
    \uuf_i^{m+1} = \uuf_i^{m} + \rho \left( \wf_i^{m+1} - \tilde{\hf}_i^{m+1} \right).\label{eq:online_admm:dual_update}
\end{equation}

POINT: update \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\hf}_i^{m+1}\|^2\), \(i \in \Mset\) and we introduce a distributed averaging-based approach to tackle this.

\section{Adaptive Norm Estimation}
\label{sec:adaptivenormest}
Distributed averaging:
\begin{mini}{}{\|\W - \bm{1}\bm{1}^\T/n\|_2} {\label{eq1}}{}
  \addConstraint{\W}{\in \mathcal{C}}
  \addConstraint{\bm{1}^\T \W}{= \bm{1}^\T}
  \addConstraint{\W \bm{1}}{= \bm{1}}
\end{mini}
gives us the optimal weights \(\mtxb{W}_{opt}\). The distributed averaging approach is an iterative approach, however here, we will try to find a way to limit the number of iterations necessary. This goal comes from the fact that the iterations require data from neighboring nodes leading to additional transmissions (per frame).

We take avantage of the fact that the squared norm of the stacked solution vector can be separated into
\begin{equation}
  \| \h \|^2 = \sum_{j \in \Mset} \|\h_j\|^2.
\end{equation}
Then, we define the approximation of the global norm \(\hat{\phi}_i \approx \|\h\|^2\) at each node \(i\) at frame \(m\) as follows:
\begin{align}
  \phi_i^1 &= \hat{\phi}_i^{m}\\
  \phi_i^{k+1} &= \sum_{j \in \Tset_i} W_{opt,ij} \phi_j^{k}\label{eq:dist_norm_est_iter}\\
  \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K
\end{align}
where \(\gamma\) is a exponential smoothing factor balancing new norm data with previous iterative estimate and \eqref{eq:dist_norm_est_iter} is applied \(K\) times.

The special case of \(K=1\) leads to the update step:
\begin{equation}
  \hat{\phi}_i^{m+1} = \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \sum_{j \in \Tset_i} W_{opt,ij} \hat{\phi}_j^m
\end{equation}

We use these in an inbetween step to estimate the norms of the channel impulse responses recursively. The full algorithm then looks like
\begin{align}
  \w_i^{m+1} &= \operatorname{argmin} \mathcal{L}_\rho(\w,\h,\uu)\\
  \bar{\h}_i^{m+1} &= \bar{\w}_i^{m+1} + \frac{1}{\rho} \bar{\uu}_i^m\\
  \phi_i^1 &= \hat{\phi}_i^{m}\\
  \phi_i^{k+1} &= \sum_{j \in \Tset_i} W_{opt,ij} \phi_j^{k} \qquad\text{for } k=1...K\\
  \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K\\
  \h_i^{m+1} &= \frac{\bar{\h}_i^{m+1}}{\sqrt{\hat{\phi}_i^K\,M}}\\
  \uu_i^{m+1} &= \uu_i^{m} + \rho \left(\w_i^{m+1} - \tilde{\h}_i^{m+1}\right).
\end{align}

\section{Transmission cost}
\label{sec:transcost}
Show effect on number of transmissions. Scale up to high numbers of nudes so neigborhoods \(<<\) entire network.

\section{Simulations}
\label{sec:simulations}
Simulations and results.
\begin{itemize}
  \item compare results of unextended algorithm (optimal case where all norm values are known)
  \item varied iteration count (more iterations: better result, BUT also even 1 iteration can lead to good results, which doesnt need additional communitation per frame)
  \item varied mixing factor (the is some optimum apparently, but unknown why and what it means)
  \item evaluate on time-varying norms of IRs
\end{itemize}

\section[]{Conclusions}
\label{sec:conclusions}
Good results coming close to optimal case with less transmissions.

% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------
% \begin{figure}[htb]

% \begin{minipage}[b]{1.0\linewidth}
%   \centering
%   \centerline{\includegraphics[width=8.5cm]{image1}}
% %  \vspace{2.0cm}
%   \centerline{(a) Result 1}\medskip
% \end{minipage}
% %
% \begin{minipage}[b]{.48\linewidth}
%   \centering
%   \centerline{\includegraphics[width=4.0cm]{image3}}
% %  \vspace{1.5cm}
%   \centerline{(b) Results 3}\medskip
% \end{minipage}
% \hfill
% \begin{minipage}[b]{0.48\linewidth}
%   \centering
%   \centerline{\includegraphics[width=4.0cm]{image4}}
% %  \vspace{1.5cm}
%   \centerline{(c) Result 4}\medskip
% \end{minipage}
% %
% \caption{Example of placing a figure with experimental results.}
% \label{fig:res}
% %
% \end{figure}

\vfill\pagebreak

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2022-10-07 simulations/admm_fq.py
simulation

@@ -1,0 +1,316 @@
+import numpy as np
+
+
+class NodeProcessor:
+    def __init__(self, id, filter_len, rho) -> None:
+        # identifier for node
+        self.id = id
+        # iterator
+        self.k = 0
+        # local solver type
+        self.type = type
+        # definition of signal connections
+        self.group = None
+        # number of FIR filter taps
+        self.L = filter_len
+        # step size / penalty parameter
+        self.rho = rho
+        # step size / penalty parameter
+        self.mu = 1
+        self.eta = 0.98
+        # number of "channels"
+        self.N = None
+        # signal block
+        self.block = None
+        # local primal
+        self.x = None
+        # local dual
+        self.y = None
+        # local dual est old
+        self.z_l = None
+        # estimated
+        self.R_xp_ = None
+        # buffer
+        self.R_buffer = None
+
+        self.setBufferSize(1)
+        pass
+
+    def setLocalSize(self, N) -> None:
+        self.N = N
+        # global indices
+        self.global_indices = None
+        self.reset()
+        pass
+
+    def setBufferSize(self, buffer_size) -> None:
+        self.buffer_size = buffer_size
+        self.buffer_ind = 0
+        # self.reset()
+        pass
+
+    def reset(self) -> None:
+        # signal block
+        self.block = np.zeros(shape=(self.L, self.N), dtype=np.complex128)
+        # local primal
+        self.x = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # self.x[0::self.L] = 1
+        # local dual
+        self.y = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # local copy of global primal
+        self.z_l = np.ones(shape=(self.L * self.N, 1), dtype=np.complex128) / np.sqrt(
+            self.L
+        )
+
+        F_LxL = self.DFT_matrix(self.L)
+        F_2Lx2L = self.DFT_matrix(2 * self.L)
+
+        W_01_Lx2L = np.concatenate([np.zeros(shape=(self.L, self.L)), np.eye(self.L)]).T
+        W_10_2LxL = np.concatenate([np.eye(self.L), np.zeros(shape=(self.L, self.L))])
+
+        self.W_01_Lx2L_fq = F_LxL @ W_01_Lx2L @ np.linalg.inv(F_2Lx2L)
+        self.W_10_2LxL_fq = F_2Lx2L @ W_10_2LxL @ np.linalg.inv(F_LxL)
+
[…]

### 2022-10-07 simulations/admm_fq_distavg.py

@@ -1,0 +1,442 @@
+import numpy as np
+
+# import cvxpy as cp
+# from cvxpy import Variable, sum_squares, Minimize, Problem, vec
+
+
+class NodeProcessor:
+    id: int
+    L: int
+    rho: float
+    mu: float
+    eta: float
+    N: int
+    block: np.ndarray
+    x: np.ndarray
+    y: np.ndarray
+    z_l: np.ndarray
+    R_xp_: np.ndarray
+    transmit_set: list
+    receive_set: list
+
+    def __init__(self, id, filter_len, rho) -> None:
+        # identifier for node
+        self.id = id
+        # iterator
+        self.k = 0
+        # local solver type
+        self.type = type
+        # definition of signal connections
+        self.group = None
+        # number of FIR filter taps
+        self.L = filter_len
+        # step size / penalty parameter
+        self.rho = rho
+        # step size / penalty parameter
+        self.mu = 1
+        self.eta = 0.98
+        # number of "channels"
+        self.N = None
+        # signal block
+        self.block = None
+        # local primal
+        self.x = None
+        # local dual
+        self.y = None
+        # local dual est old
+        self.z_l = None
+        # estimated
+        self.R_xp_ = None
+        # buffer
+        self.R_buffer = None
+
+        self.setBufferSize(1)
+        pass
+
+    def setLocalSize(self, N) -> None:
+        self.N = N
+        # global indices
+        self.global_indices = None
+        self.reset()
+        pass
+
+    def setNeigborhood(self, T, R, davg) -> None:
+        self.transmit_set = T
+        self.receive_set = R
+        self.davg = davg
+
+        # self.N = len(self.receive_set)
+
+        pass
+
+    def setBufferSize(self, buffer_size) -> None:
+        self.buffer_size = buffer_size
+        self.buffer_ind = 0
+        # self.reset()
+        pass
+
+    def reset(self) -> None:
+        # signal block
+        self.block = np.zeros(shape=(self.L, self.N), dtype=np.complex128)
+        # local primal
+        self.x = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # self.x[0::self.L] = 1
+        # local dual
+        self.y = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # local copy of global primal
[…]

### 2022-10-07 simulations/static.py

@@ -1,0 +1,177 @@
+# %%
+import os
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import python_utils.utils as utils
+import python_utils.simulation as simulation
+
+
+# %%
+# Define the simulation function.
+# You can define any number of arguments instead of a, b.
+# Remember to add them in SimConfig
+# DO NOT CHANGE run and seed arguments and argument positions!
+def simulate(alg, SNR, gamma, iters, run: int, seed: int):
+    ## %%
+    # All required imports for simulation need to be in here, e.g.,
+    import numpy as np
+
+    if alg == "opt":
+        import admm_fq as adf
+    if alg == "davg":
+        import admm_fq_distavg as adf
+
+    rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
+    ## %%
+    # ################################################################
+    # Put the simulation code here
+    L = 16
+    nw = adf.Network(L)
+    nw.addNode(0, 1)
+    nw.addNode(1, 1)
+    nw.addNode(2, 1)
+    nw.setConnection(0, [1])
+    nw.setConnection(1, [2])
+    nw.setConnection(2, [0])
+
+    W = np.array([[0.5, 0.0, 0.5], [0.5, 0.5, 0.0], [0.0, 0.5, 0.5]])
+    if alg != "opt":
+        nw.setAveragingWeights(W)
+
+    rho = 1.0
+    stepsize = 0.5
+    eta = 0.98
+    N_sens = nw.N
+    N_s = 80000
+    SNR = 10
+
+    true_norms = [2.2, 0.5, 1.2, 0.7]
+
+    h = np.array([]).reshape(0, 1)
+    for n in range(N_sens):
+        h_ = rng.normal(size=(L, 1))
+        h_ = h_ / np.linalg.norm(h_) * true_norms[n]
+        h = np.concatenate([h, h_])
+
+    u = rng.normal(size=(N_s, 1))
+    s = u / u.max()
+
+    hopsize = L
+    s_ = np.concatenate([np.zeros(shape=(L - 1, 1)), s])
+    var_s = np.var(s)
+
+    x_ = np.zeros(shape=(N_s, N_sens))
+    n_var = 10 ** (-SNR / 20) * var_s * np.linalg.norm(h) ** 2 / N_sens
+    H = np.reshape(h, (N_sens, L))
+    for k in range(N_s - L):
[…]

### 2022-10-07 simulations/transcost.py
transmission cost

@@ -1,0 +1,84 @@
+# %%
+import numpy as np
+import python_utils.utils as utils
+
+import matplotlib
+
+matplotlib.use("pgf")
+import matplotlib.pyplot as plt
+plt.rcParams.update(
+    {
+        "font.family": "serif",  # use serif/main font for text elements
+        "text.usetex": True,  # use inline math for ticks
+        "pgf.rcfonts": False,  # don't setup fonts from rc parameters
+    }
+)
+
+# %%
+M = np.arange(10,5000)
+
+# %%
+N_bar = [5, 10]
+
+# %%
+R = [1, 50]
+
+# %%
+# fig = plt.figure(figsize=(6, 4))
+# # plt.title("Title")
+# plt.xlabel("Network size M [1]")
+# plt.ylabel(r"$\log \mathcal{O}(.)$ [1]")
+# plt.plot(M,2*M**2, "k--", label="full direct")
+# plt.plot(M,M+M**2, "-.", label="broadcast")
+# for n_bar in N_bar:
+#     for r in R:
+#         plt.plot(M,M*n_bar*r + M*n_bar*r, label=r"$\bar{N}=$%d,$R=$%d"%(n_bar, r))
+# plt.legend()
+# plt.grid()
+# plt.tight_layout()
+# plt.show()
+
+# %%
+styles = ["-<", "->", "-v", "-s", "-o"]
+fig = plt.figure(figsize=utils.set_size(245, 1.0, (1,1)))
+# plt.title("Title")
+plt.xlabel("Network size M [1]")
+plt.ylabel(r"$\mathcal{O}(.)$ [1]")
+plt.plot(M,2*M**2, "k-", label="full direct")
+plt.plot(M,M+M**2, "--", label="broadcast")
+ss = 0
+for n_bar in N_bar:
+    for r in R:
+        plt.plot(M,M*n_bar*r + M*n_bar*r, styles.pop(), label=r"$\bar{N}=$%d,$R=$%d"%(n_bar, r), markevery=(ss,500), markersize=3)
+        ss += 50
+plt.legend(ncol=2,prop={'size': 7})
+plt.grid()
+plt.yscale("log")
+plt.xlim(0,5000)
+plt.tight_layout()
+plt.show()
+# %%
+utils.savefig(fig,"transcost", format="pgf", pgf_font="serif")
+
+# %%
+styles = ["-<", "->", "-v", "-s", "-o"]
[…]

### 2022-10-10 paper.tex
transmission cost
intro

@@
 
-Main contribution: Avoid broadcasting or relaying of norm values, with distributed averaging approach and low iteration count.
-Algorithms using a similar approach: \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, however these use high numbers of iterations (30) which leads to many per-frame transmissions.
-Argument against broadcasting: (1)Large-scale networks, where not all nodes can physically communicate with each other, but that is not really that relevant for room acoustics...
+Distributed algorithms have been an active area of research for quite some time, with numerous control, optimization, and signal processing applications.
+With the ever-growing number of smart multimedia devices in today's surroundings providing ubiquitous processing and communication capabilities, distributed audio and speech signal processing also found their way into the spotlight.
+Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154} amongst others, have been proposed.
+The task of distributed single-input-multiple-output (SIMO) blind system identification (BSI) had contributions such as the adaptive cross-relation-based (CR) \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
+Furthermore, we recently introduced an adaptive CR-based algorithm \cite{blochbergerDBSI} using the alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011}.
+All of the mentioned distributed BSI algorithms rely on information shared between neighboring sensor nodes within the network.
+However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to e.g.
+\cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003}), which manifests itself as one or more global variables.
+In this case, a global variable is a variable, the computation of which requires information from all nodes within the network.
+To overcome the need for the network to be fully connected, \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} use an average consensus \cite{xiaoFastLinearIterations2004} approach where a secondary recursion estimates the global variable for each signal frame.
+The algorithm in \cite{blochbergerDBSI} relies on node-wise values being relayed throughout the network.
+Both approaches introduce additional transmissions of variables between nodes, the number of which, depending on network and neighborhood size, can be substantial and even unfeasable.
+
+In this paper, we extend \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable with the introduction of a mixing factor to include instantaneous values into the averaging recursion.
+The mixing factor allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
+Simulation results show how the extension leads to BSI performance close to an optimal case where all information is available without the need of broadcasting variables to all nodes or a large number of estimation iterations.
+
+% Main contribution: Avoid broadcasting or relaying of norm values, with distributed averaging approach and low iteration count.
+% Algorithms using a similar approach: \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, however these use high numbers of iterations (30) which leads to many per-frame transmissions.
+% Argument against broadcasting: (1)Large-scale networks, where not all nodes can physically communicate with each other, but that is not really that relevant for room acoustics...
 (2) just because.
@@
 
-Important context in introduction: BSI, WSN, topology, connection matrix,
+% Important context in introduction: BSI, WSN, topology, connection matrix,
 
-What to show:
-\begin{itemize}
-  \item Algorithm extension
-  \item Results
-  \begin{itemize}
-    \item compare results of unextended algorithm (optimal case)
-    \item with extended: varied iteration count (more iterations: better result, BUT also even 1 iteration can lead to good results)
-    \item varied mixing factor (there is some optimal \(\gamma\) apparently)
-    \item Show transmission cost: transmission cost over number of nodes
-  \end{itemize}
-\end{itemize}
+% What to show:
+% \begin{itemize}
+%   \item Algorithm extension
+%   \item Results
+%   \begin{itemize}
+%     \item compare results of unextended algorithm (optimal case)
+%     \item with extended: varied iteration count (more iterations: better result, BUT also even 1 iteration can lead to good results)
+%     \item varied mixing factor (there is some optimal \(\gamma\) apparently)
+%     \item Show transmission cost: transmission cost over number of nodes
+%   \end{itemize}
+% \end{itemize}
 
-\section{DISTRIBUTED ADAPTIVE BLIND SYSTEM IDENTIFICATION}
+\section{DISTRIBUTED ADAPTIVE BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM}
 \label{sec:dbsi}
-Introduction of the algorithm from iwaenc paper. \cite{blochbergerDBSI}
+In \cite{blochbergerDBSI}, we proposed an adaptive SIMO BSI algorithm based on Online-ADMM.
+In this section, we will introduce parts which are necessary for the reader to understand the extension.
+For the full algorithm, we refer the reader to the previous publication.
+
+The coss-realtion problem 
 \begin{align}
@@
 
-The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
-\begin{equation}
-    \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right),\label{eq:online_admm:local_update}
-\end{equation}
-where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the regularized inverse Hessian of the problem.
-The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce computational complexity, we introduce the approximation
-\begin{equation}
-    \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1},
-\end{equation}
-which is straightforward to compute.
+% The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
+% \begin{equation}
+%     \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right),\label{eq:online_admm:local_update}
+% \end{equation}
+% where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the regularized inverse Hessian of the problem.
+% The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce computational complexity, we introduce the approximation
+% \begin{equation}
+%     \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1},
+% \end{equation}
+% which is straightforward to compute.
 It may be readily verified (cf. \cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by an update step which computes
@@
 The values of all \(\|\bar{\hf}_i^{m+1}\|^2\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
-Finally, the update of the dual variables is given by
-\begin{equation}
-    \uuf_i^{m+1} = \uuf_i^{m} + \rho \left( \wf_i^{m+1} - \tilde{\hf}_i^{m+1} \right).\label{eq:online_admm:dual_update}
-\end{equation}
+% Finally, the update of the dual variables is given by
+% \begin{equation}
+%     \uuf_i^{m+1} = \uuf_i^{m} + \rho \left( \wf_i^{m+1} - \tilde{\hf}_i^{m+1} \right).\label{eq:online_admm:dual_update}
+% \end{equation}
 
@@
 \end{mini}
-gives us the optimal weights \(\mtxb{W}_{opt}\).
+gives us the optimal weights \(\mtxb{W}_{o}\) where the weights used by node \(i\) to combine values from neighbor nodes \(j \in \Rset_i\) are given at the \(i\)-th row.
 The distributed averaging approach is an iterative approach, however here, we will try to find a way to limit the number of iterations necessary.
@@
 
-We take avantage of the fact that the squared norm of the stacked solution vector can be separated into
+% We take avantage of the fact that the squared norm of the stacked solution vector can be separated into
+% \begin{equation}
+%   \| \h \|^2 = \sum_{j \in \Mset} \|\h_j\|^2.
+% \end{equation}
+We define the approximation of the global norm \(\hat{\phi}_i \approx \|\h\|^2\) at each node \(i\) at frame \(m\) as follows:
 \begin{equation}
-  \| \h \|^2 = \sum_{j \in \Mset} \|\h_j\|^2.
+  \phi_i^{m,k+1} = \sum_{j \in \Rset_i} w_{ij} \phi_j^{m,k}\quad\text{for }k=1,\ldots,K\label{eq:dist_norm_est_iter}
 \end{equation}
-Then, we define the approximation of the global norm \(\hat{\phi}_i \approx \|\h\|^2\) at each node \(i\) at frame \(m\) as follows:
-\begin{align}
-  \phi_i^1 &= \hat{\phi}_i^{m}\\
-  \phi_i^{k+1} &= \sum_{j \in \Tset_i} W_{opt,ij} \phi_j^{k}\label{eq:dist_norm_est_iter}\\
-  \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K
-\end{align}
-where \(\gamma\) is a exponential smoothing factor balancing new norm data with previous iterative estimate and \eqref{eq:dist_norm_est_iter} is applied \(K\) times.
+with the initial value at \(m=1,k=1\) defined as \(\phi_i^{1,1}=\|\h_i^{1}\|^2\).
+\eqref{eq:dist_norm_est_iter} is applied \(K\) times.
+We now define the frame estimate of the global squared norm as
+\begin{equation}
+  \hat{\phi}_i^{m+1} = \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m,K}
+\end{equation}
+where \(\bar{\phi}_i^{m} = \sum_{j \in \Rset_i} w_{ij} \|\h_i^m\|^2\) is an instantaneous weighted neighborhood average of node-wise squared norm values and \(\gamma_i\) is a mixing factor.
+This factor can be chosen as a fixed value, where simulations have shown that values around \(\gamma_i = 0.02\) lead to satisfying results (cf. FIGURE) or adaptively.
+For this, we use the instantaneous values to track stationarity of the squared norms by setting the factor \(\gamma_i^{m}\) proportional to \(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |\), the absolute difference between instantaneous neighborhood norm values of subsequent frames.
 
@@
 \begin{equation}
-  \hat{\phi}_i^{m+1} = \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \sum_{j \in \Tset_i} W_{opt,ij} \hat{\phi}_j^m
+  \hat{\phi}_i^{m+1} = \gamma_i \sum_{j \in \Rset_i} w_{ij} \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma_i) \sum_{j \in \Rset_i} w_{ij} \hat{\phi}_j^m
 \end{equation}
@@
 We use these in an inbetween step to estimate the norms of the channel impulse responses recursively. The full algorithm then looks like
-\begin{align}
-  \w_i^{m+1} &= \operatorname{argmin} \mathcal{L}_\rho(\w,\h,\uu)\\
-  \bar{\h}_i^{m+1} &= \bar{\w}_i^{m+1} + \frac{1}{\rho} \bar{\uu}_i^m\\
-  \phi_i^1 &= \hat{\phi}_i^{m}\\
-  \phi_i^{k+1} &= \sum_{j \in \Tset_i} W_{opt,ij} \phi_j^{k} \qquad\text{for } k=1...K\\
-  \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K\\
-  \h_i^{m+1} &= \frac{\bar{\h}_i^{m+1}}{\sqrt{\hat{\phi}_i^K\,M}}\\
-  \uu_i^{m+1} &= \uu_i^{m} + \rho \left(\w_i^{m+1} - \tilde{\h}_i^{m+1}\right).
-\end{align}
+
+\begin{algorithm}
+  \caption{Estimation of norm values}\label{alg:davg_norm_est}
+  $i\gets 10$\;
+  \eIf{$i\geq 5$}
+  {
+      $i\gets i-1$\;
+  }{
+      \If{$i\leq 3$}
+      {
+          $i\gets i+2$\;
+      }
+  }
+\end{algorithm}
+
+% \begin{align}
+%   \w_i^{m+1} &= \operatorname{argmin} \mathcal{L}_\rho(\w,\h,\uu)\\
+%   \bar{\h}_i^{m+1} &= \bar{\w}_i^{m+1} + \frac{1}{\rho} \bar{\uu}_i^m\\
+%   \phi_i^1 &= \hat{\phi}_i^{m}\\
+%   \phi_i^{k+1} &= \sum_{j \in \Rset_i} w_{ij} \phi_j^{k} \qquad\text{for } k=1,\ldots,K\\
+%   \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K\\
+%   \h_i^{m+1} &= \frac{\bar{\h}_i^{m+1}}{\sqrt{\hat{\phi}_i^K\,M}}\\
+%   \uu_i^{m+1} &= \uu_i^{m} + \rho \left(\w_i^{m+1} - \tilde{\h}_i^{m+1}\right).
+% \end{align}
 
@@
 \label{sec:transcost}
-Show effect on number of transmissions. Scale up to high numbers of nudes so neigborhoods \(<<\) entire network.
+Show effect on number of transmissions. Scale up to high numbers of nodes so neigborhoods \(<<\) entire network.
+
+\begin{align}
+  \mathcal{O}(&(M-1)^2) & &+ & \mathcal{O}(&(M-1)^2)\\
+  \mathcal{O}(&M-1) & &+ & \mathcal{O}(&(M-1)^2)\\
+  \mathcal{O}(&M \bar{N}_i R) & &+ & \mathcal{O}(&M \bar{N}_i R)
+\end{align}
+
+Or per node:
+\begin{align}
+  \mathcal{O}(&M-1) & &+ & \mathcal{O}(&M-1)\\
+  \mathcal{O}(&1) & &+ & \mathcal{O}(&M-1)\\
+  \mathcal{O}(&\bar{N}_i R) & &+ & \mathcal{O}(&\bar{N}_i R)
+\end{align}
+
+\begin{figure}
+  \centering
+  \input{simulations/plots/transcost/transcost.pgf}
+  \input{simulations/plots/transcostnode/transcostnode.pgf}
+  \vspace*{-0.8cm}
+  \caption[]{The order of transmission cost of entire network or single node (choose which to keep if at all.).}
+  \label{fig:transcost:bigo}
+\end{figure}
 

### 2022-10-10 paper.tex
notation change

@@
 \name{Matthias Blochberger\(^1\), Filip Elvander\(^2\), Toon, ...\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
-This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.}}
+This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
+This research received funding in part from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
+This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.}}
 \address{\(^1\)KU Leuven, Dept. of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept. of Signal Processing and Acoustics, 02150 Espoo, Finland}
@@
 The algorithm in \cite{blochbergerDBSI} relies on node-wise values being relayed throughout the network.
-Both approaches introduce additional transmissions of variables between nodes, the number of which, depending on network and neighborhood size, can be substantial and even unfeasable.
+Both approaches introduce additional transmissions of variables between nodes, the number of which, depending on network and neighborhood size, can be substantial or even unfeasable.
 
@@
 In this section, we will introduce parts which are necessary for the reader to understand the extension.
-For the full algorithm, we refer the reader to the previous publication.
+For the full derivation and algorithm, we refer the reader to the cited publication.
 
-The coss-realtion problem 
+The coss-relation problem formulation is used relative information between sensor signals to identify the system, i.e., the acoutic or communication channels.
+The solution to this problem is found by the minimization problem
+\begin{equation}
+  \begin{aligned}
+      \hat{\h} = \arg \min_{\h} \quad &\h^\herm \hat{\R} \h \\
+      \text{s.t. } \quad &\h^\herm \h = 1.
+  \end{aligned}\label{eq:frequency_domain:min_prob}
+\end{equation}
+where 
 \begin{align}
-  \wf_i^{k+1} &= \underset{\wf_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\wf,\hf^k,\uuf^k)\label{eq:general_consensus_admm:local}\\
-  \hf^{k+1} &= \underset{\hf, \|\hf\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\wf^{k+1},\hf,\uuf^k)\label{eq:general_consensus_admm:global}\\
-  \uuf_i^{k+1} &= \uuf_i^{k} + \rho \left( \wf_i^{k+1} - \tilde{\hf}_i^{k+1} \right),\label{eq:general_consensus_admm:dual}
+  \w_i^{k+1} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^k,\uu^k)\label{eq:general_consensus_admm:local}\\
+  \h^{k+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{k+1},\h,\uu^k)\label{eq:general_consensus_admm:global}\\
+  \uu_i^{k+1} &= \uu_i^{k} + \rho \left( \w_i^{k+1} - \tilde{\h}_i^{k+1} \right),\label{eq:general_consensus_admm:dual}
 \end{align}
 
-% The minimization problem for the local variable \(\wf_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
+% The minimization problem for the local variable \(\w_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
 % \begin{equation}
-%     \wf_i^{m+1} = \wf_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \wf_i^m + \uuf_i^m + \rho\left(\wf_i^m - \tilde{\hf}_i^{m}\right)\right),\label{eq:online_admm:local_update}
+%     \w_i^{m+1} = \w_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \w_i^m + \uu_i^m + \rho\left(\w_i^m - \tilde{\h}_i^{m}\right)\right),\label{eq:online_admm:local_update}
 % \end{equation}
@@
 \begin{equation}
-    \hf_i^{m+1} = \frac{\bar{\hf}_i^{m+1}}{\sqrt{\sum_{j \in \Mset} \|\bar{\hf}_j^{m+1}\|^2}}\label{eq:online_admm:consensus_update}
+    \h_i^{m+1} = \frac{\bar{\h}_i^{m+1}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{m+1}\|^2}}\label{eq:online_admm:consensus_update}
 \end{equation}
@@
 \begin{equation}
-    \bar{\hf}_i^{m+1} = \bar{\wf}_i^{m+1} + \frac{1}{\rho} \bar{\uuf}_i^{m}.
+    \bar{\h}_i^{m+1} = \bar{\w}_i^{m+1} + \frac{1}{\rho} \bar{\uu}_i^{m}.
 \end{equation}
-Here, \(\bar{\wf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\wf_j)_i\) and \(\bar{\uuf}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uuf_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) respectively, computed at node \(i\).
-The values of all \(\|\bar{\hf}_i^{m+1}\|^2\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
+Here, \(\bar{\w}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\w_j)_i\) and \(\bar{\uu}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uu_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) respectively, computed at node \(i\).
+The values of all \(\|\bar{\h}_i^{m+1}\|^2\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
 % Finally, the update of the dual variables is given by
 % \begin{equation}
-%     \uuf_i^{m+1} = \uuf_i^{m} + \rho \left( \wf_i^{m+1} - \tilde{\hf}_i^{m+1} \right).\label{eq:online_admm:dual_update}
+%     \uu_i^{m+1} = \uu_i^{m} + \rho \left( \w_i^{m+1} - \tilde{\h}_i^{m+1} \right).\label{eq:online_admm:dual_update}
 % \end{equation}
 
-POINT: update \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\hf}_i^{m+1}\|^2\), \(i \in \Mset\) and we introduce a distributed averaging-based approach to tackle this.
+POINT: update \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i^{m+1}\|^2\), \(i \in \Mset\) and we introduce a distributed averaging-based approach to tackle this.
 
@@
 % \end{minipage}
-% \hfill
+% \hill
 % \begin{minipage}[b]{0.48\linewidth}

### 2022-10-11 paper.tex
tuesday party

@@
 
-\section{DISTRIBUTED ADAPTIVE BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM}
+\section{DISTRIBUTED ADAPTIVE BSI IN SENSOR NETWORKS WITH ONLINE-ADMM}
 \label{sec:dbsi}
-In \cite{blochbergerDBSI}, we proposed an adaptive SIMO BSI algorithm based on Online-ADMM.
-In this section, we will introduce parts which are necessary for the reader to understand the extension.
-For the full derivation and algorithm, we refer the reader to the cited publication.
+\begin{todo}
+  Introduce signal model, \(\h\),...
+\end{todo}
+% In \cite{blochbergerDBSI}, we proposed an adaptive SIMO BSI algorithm based on Online-ADMM.
+In this section, we will introduce certain parts of an adaptive SIMO BSI algorithm based on Online-ADMM \cite{blochbergerDBSI}, which are necessary for the reader to understand its extension of it.
+We refer the reader to the publication cited above for the full derivation of the algorithm.
 
-The coss-relation problem formulation is used relative information between sensor signals to identify the system, i.e., the acoutic or communication channels.
-The solution to this problem is found by the minimization problem
+We assume a set \(\Mset \triangleq \{1,\ldots,M\}\) sensor nodes and a set of edges \(\mathcal{E}\) which connect the nodes forming a sensor network.
+Each edge is an unordered pair of nodes \(\{i,j\} \in \mathcal{E}\), which represents the communication link between them.
+From this follows the neighborhood of a node \(i\), i.e., the other nodes it is directly connected to, defined as \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\).
+Furthermore, we can define the symmetric adjacency matrix \(\mtxb{C}\) with elements
+\begin{equation}
+  c_{ij} = \begin{cases}
+    1 \quad \text{if } i = j\\
+    1 \quad \text{if } i \neq j \text{ and }\{i,j\} \in \mathcal{E}\\
+    0 \quad \text{otherwise}.
+  \end{cases}
+\end{equation}
+It is to note that in \cite{blochbergerDBSI}, the pairs \(\{i,j\} \in \mathcal{E}\) are ordered, which yields a directed graph and leads to two sets of neighborhoods ("transmit" and "receive") and therefore a non-symmetric adjacency matrix.
+In this paper, we limit the explanation to the undirected graph to save space, as the extension is straightforward.
+
+In BSI, the coss-relation problem formulation uses relative information between sensor signals to identify the system, i.e., the acoustic or communication channels.
+The solution to this problem is found by the minimization problem (cf. e.g. \cite{langtongBlindIdentificationEqualization1994,huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003})
 \begin{equation}
@@
 \end{equation}
-where 
+\begin{todo}
+  Introduce \(\w, \uu\)
+\end{todo}
+Separating the cost function and appying general-form consensus ADMM as an adaptive algorithm leads to the update steps
 \begin{align}
-  \w_i^{k+1} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^k,\uu^k)\label{eq:general_consensus_admm:local}\\
-  \h^{k+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{k+1},\h,\uu^k)\label{eq:general_consensus_admm:global}\\
-  \uu_i^{k+1} &= \uu_i^{k} + \rho \left( \w_i^{k+1} - \tilde{\h}_i^{k+1} \right),\label{eq:general_consensus_admm:dual}
+  \w_i^{m+1} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^m,\uu^m)\label{eq:general_consensus_admm:local}\\
+  \h^{m+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{m+1},\h,\uu^m)\label{eq:general_consensus_admm:global}\\
+  \uu_i^{m+1} &= \uu_i^{m} + \rho \left( \w_i^{m+1} - \tilde{\h}_i^{m+1} \right).\label{eq:general_consensus_admm:dual}
 \end{align}
+Here, the second step, the update of the so-called consensus variables are of interest for this extension.
+It is defined \cite{blochbergerDBSI} as
+\begin{equation}
+    \h_i^{m+1} = \frac{\bar{\h}_i^{m+1}}{\|\h^{m+1}\|}\label{eq:online_admm:consensus_update}
+\end{equation}
+for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{m+1}\), a combination of neigborhood averages of the channel response estimates and the dual variables of channel \(i\) respectively, computed at node \(i\).
+The denominator of \eqref{eq:online_admm:consensus_update}, \(\|\h\|\), is the stacked vector of the full system. This vector, however, is not available at any of the nodes in the network.
+In \cite{blochbergerDBSI}, we assume that partial squared norms of \(\|\h\|^2 = \sum_{i \in \Mset} \|\h_i\|^2\) are relayed throughout the network until all nodes have the information necessary.
+In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}, a similar global value is estimated by a distributed averaging approach, iteratively combining values within neighborhoods until convergence to a network-wide average.
 
-% The minimization problem for the local variable \(\w_i\) \eqref{eq:general_consensus_admm:local} can be solved by various algorithms, in this case however we perform the adaptive update step as
-% \begin{equation}
-%     \w_i^{m+1} = \w_i^{m} - \mu \bm{{V}}_i^m \left( \hat{\aRhof}_i^m \w_i^m + \uu_i^m + \rho\left(\w_i^m - \tilde{\h}_i^{m}\right)\right),\label{eq:online_admm:local_update}
-% \end{equation}
-% where \(\mu\), (\(0  < \mu\leq 1\)), is a step size and \(\bm{{V}}_i^m = \left(\hat{\aRhof}_i^m + \rho \I \right)^{-1}\) is the regularized inverse Hessian of the problem.
-% The implicit overlap-save matrices in \(\bm{{V}}_i^m\) make this a constrained update step which is costly to compute, so in order to reduce computational complexity, we introduce the approximation
-% \begin{equation}
-%     \hat{\bm{{V}}}_i^m = \operatorname{diag} \left\{ \operatorname{diag} \left\{ \hat{\aRhof}_i^m \right\} + \rho \mtxb{1} \right\}^{-1},
-% \end{equation}
-% which is straightforward to compute.
-It may be readily verified (cf. \cite{boydDistributedOptimizationStatistical2011}) that the solution to \eqref{eq:general_consensus_admm:global} is given by an update step which computes
+Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} with the further introduction of a mixing factor to include instantaneous values in the recursion.
+
+\section{FDLA-based adaptive norm estimation}
+\label{sec:adaptivenormest}
+We define 
+The FDLA problem, as introduced in \cite{xiaoFastLinearIterations2004}, looks to find optimal weights for distributed linear combinations of the form \(\bm{\phi}^{k+1} = \W \bm{\phi}^{k}\) where \(\bm{\phi}^k = \begin{bmatrix} \phi_1^k & \ldots & \phi_M^k \end{bmatrix}^\T\) is a vector, which initially, at \(k=1\), contains a set of variables, of which an average should be computed iteratively.
+The problem comes in the form of a minimization problem
 \begin{equation}
-    \h_i^{m+1} = \frac{\bar{\h}_i^{m+1}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{m+1}\|^2}}\label{eq:online_admm:consensus_update}
+  \begin{aligned}
+    \min& \quad \| \W - \bm{1}\bm{1}^\T/n\|_2\\
+    \text{s.t.}& \quad \W \in \mathcal{C},\, \bm{1}^\T \W = \bm{1}^\T,\, \W \bm{1}= \bm{1}
+  \end{aligned}
 \end{equation}
-for each node \(i \in \Mset\) with the local unnormalized consensus
-\begin{equation}
-    \bar{\h}_i^{m+1} = \bar{\w}_i^{m+1} + \frac{1}{\rho} \bar{\uu}_i^{m}.
-\end{equation}
-Here, \(\bar{\w}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\w_j)_i\) and \(\bar{\uu}_i = \frac{1}{N_i} \sum_{j \in \Tset_i} (\uu_j)_i\), with \(N_i = | \Tset_i |\), are neigborhood averages of the channel response estimate and the dual variable of channel \(i\) respectively, computed at node \(i\).
-The values of all \(\|\bar{\h}_i^{m+1}\|^2\), \(i \in \Mset\) are transmitted and relayed through the network until all nodes can compute the denominator in \eqref{eq:online_admm:consensus_update}.
-% Finally, the update of the dual variables is given by
-% \begin{equation}
-%     \uu_i^{m+1} = \uu_i^{m} + \rho \left( \w_i^{m+1} - \tilde{\h}_i^{m+1} \right).\label{eq:online_admm:dual_update}
-% \end{equation}
 
-POINT: update \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i^{m+1}\|^2\), \(i \in \Mset\) and we introduce a distributed averaging-based approach to tackle this.
+The set \(\mathcal{C} = \{\W \in \mathbb{R}^{M \times M} \vert W_{ij} = 0 \text{ if } \{i,j\} \notin \mathcal{E}\}\) describes all matrices with the same sparsity pattern as the adjacency matrix \(\mtxb{C}\).
 
-\section{Adaptive Norm Estimation}
-\label{sec:adaptivenormest}
-Distributed averaging:
-\begin{mini}{}{\|\W - \bm{1}\bm{1}^\T/n\|_2} {\label{eq1}}{}
-  \addConstraint{\W}{\in \mathcal{C}}
-  \addConstraint{\bm{1}^\T \W}{= \bm{1}^\T}
-  \addConstraint{\W \bm{1}}{= \bm{1}}
-\end{mini}
-gives us the optimal weights \(\mtxb{W}_{o}\) where the weights used by node \(i\) to combine values from neighbor nodes \(j \in \Rset_i\) are given at the \(i\)-th row.
+where the weights used by node \(i\) to combine values from neighbor nodes \(j \in \Nset_i\) are given at the \(i\)-th row.
 The distributed averaging approach is an iterative approach, however here, we will try to find a way to limit the number of iterations necessary.
@@
 \begin{equation}
-  \phi_i^{m,k+1} = \sum_{j \in \Rset_i} w_{ij} \phi_j^{m,k}\quad\text{for }k=1,\ldots,K\label{eq:dist_norm_est_iter}
+  \phi_i^{m,k+1} = \sum_{j \in \Nset_i} W_{ij} \phi_j^{m,k}\quad\text{for }k=1,\ldots,K\label{eq:dist_norm_est_iter}
 \end{equation}
@@
 \end{equation}
-where \(\bar{\phi}_i^{m} = \sum_{j \in \Rset_i} w_{ij} \|\h_i^m\|^2\) is an instantaneous weighted neighborhood average of node-wise squared norm values and \(\gamma_i\) is a mixing factor.
+where \(\bar{\phi}_i^{m} = \sum_{j \in \Nset_i} W_{ij} \|\h_i^m\|^2\) is an instantaneous weighted neighborhood average of node-wise squared norm values and \(\gamma_i\) is a mixing factor.
 This factor can be chosen as a fixed value, where simulations have shown that values around \(\gamma_i = 0.02\) lead to satisfying results (cf. FIGURE) or adaptively.
-For this, we use the instantaneous values to track stationarity of the squared norms by setting the factor \(\gamma_i^{m}\) proportional to \(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |\), the absolute difference between instantaneous neighborhood norm values of subsequent frames.
+For this, we use the instantaneous values to track stationarity of the squared norms by setting the factor \(\gamma_i^{m}\) proportional to the absolute difference between instantaneous neighborhood norm values of subsequent frames
+\begin{equation}
+  \gamma_i^{m} = \min \left\lbrace \frac{| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |}{\bar{\phi}_i^{m-1}},\,1\right\rbrace.
+\end{equation}
 
@@
 \begin{equation}
-  \hat{\phi}_i^{m+1} = \gamma_i \sum_{j \in \Rset_i} w_{ij} \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma_i) \sum_{j \in \Rset_i} w_{ij} \hat{\phi}_j^m
+  \hat{\phi}_i^{m+1} = \gamma_i \sum_{j \in \Nset_i} W_{ij} \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma_i) \sum_{j \in \Nset_i} w_{ij} \hat{\phi}_j^m
 \end{equation}
@@
 %   \phi_i^1 &= \hat{\phi}_i^{m}\\
-%   \phi_i^{k+1} &= \sum_{j \in \Rset_i} w_{ij} \phi_j^{k} \qquad\text{for } k=1,\ldots,K\\
+%   \phi_i^{k+1} &= \sum_{j \in \Nset_i} w_{ij} \phi_j^{k} \qquad\text{for } k=1,\ldots,K\\
 %   \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K\\

### 2022-10-11 simulations/transcost.py

@@ -6,6 +6,7 @@ import matplotlib
 
 matplotlib.use("pgf")
 import matplotlib.pyplot as plt
+
 plt.rcParams.update(
     {
         "font.family": "serif",  # use serif/main font for text elements
@@ -15,7 +16,7 @@ plt.rcParams.update(
 )
 
 # %%
-M = np.arange(10,5000)
+M = np.arange(10, 5000)
 
 # %%
 N_bar = [5, 10]
@@ -40,45 +41,59 @@ R = [1, 50]
 
 # %%
 styles = ["-<", "->", "-v", "-s", "-o"]
-fig = plt.figure(figsize=utils.set_size(245, 1.0, (1,1)))
+fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
 # plt.title("Title")
 plt.xlabel("Network size M [1]")
 plt.ylabel(r"$\mathcal{O}(.)$ [1]")
-plt.plot(M,2*M**2, "k-", label="full direct")
-plt.plot(M,M+M**2, "--", label="broadcast")
+plt.plot(M, 2 * M**2, "k-", label="full direct")
+plt.plot(M, M + M**2, "--", label="broadcast")
 ss = 0
 for n_bar in N_bar:
     for r in R:
-        plt.plot(M,M*n_bar*r + M*n_bar*r, styles.pop(), label=r"$\bar{N}=$%d,$R=$%d"%(n_bar, r), markevery=(ss,500), markersize=3)
+        plt.plot(
+            M,
+            M * n_bar * r + M * n_bar * r,
+            styles.pop(),
+            label=r"$\bar{N}=$%d,$R=$%d" % (n_bar, r),
+            markevery=(ss, 500),
+            markersize=3,
+        )
         ss += 50
-plt.legend(ncol=2,prop={'size': 7})
+plt.legend(ncol=2, prop={"size": 7})
 plt.grid()
 plt.yscale("log")
-plt.xlim(0,5000)
+plt.xlim(0, 5000)
 plt.tight_layout()
 plt.show()
 # %%
-utils.savefig(fig,"transcost", format="pgf", pgf_font="serif")
+utils.savefig(fig, "transcost", format="pgf", pgf_font="serif")
 
 # %%
 styles = ["-<", "->", "-v", "-s", "-o"]
-fig = plt.figure(figsize=utils.set_size(245, 1.0, (1,1)))
[…]

### 2022-10-12 simulations/admm_fq_distavg_ad.py
adaptive simulation

@@ -1,0 +1,455 @@
+import numpy as np
+
+# import cvxpy as cp
+# from cvxpy import Variable, sum_squares, Minimize, Problem, vec
+
+
+class NodeProcessor:
+    id: int
+    L: int
+    rho: float
+    mu: float
+    eta: float
+    N: int
+    block: np.ndarray
+    x: np.ndarray
+    y: np.ndarray
+    z_l: np.ndarray
+    R_xp_: np.ndarray
+    transmit_set: list
+    receive_set: list
+
+    def __init__(self, id, filter_len, rho) -> None:
+        # identifier for node
+        self.id = id
+        # iterator
+        self.k = 0
+        # local solver type
+        self.type = type
+        # definition of signal connections
+        self.group = None
+        # number of FIR filter taps
+        self.L = filter_len
+        # step size / penalty parameter
+        self.rho = rho
+        # step size / penalty parameter
+        self.mu = 1
+        self.eta = 0.98
+        # number of "channels"
+        self.N = None
+        # signal block
+        self.block = None
+        # local primal
+        self.x = None
+        # local dual
+        self.y = None
+        # local dual est old
+        self.z_l = None
+        # estimated
+        self.R_xp_ = None
+        # buffer
+        self.R_buffer = None
+
+        self.setBufferSize(1)
+        pass
+
+    def setLocalSize(self, N) -> None:
+        self.N = N
+        # global indices
+        self.global_indices = None
+        self.reset()
+        pass
+
+    def setNeigborhood(self, T, R, davg) -> None:
+        self.transmit_set = T
+        self.receive_set = R
+        self.davg = davg
+
+        # self.N = len(self.receive_set)
+
+        pass
+
+    def setBufferSize(self, buffer_size) -> None:
+        self.buffer_size = buffer_size
+        self.buffer_ind = 0
+        # self.reset()
+        pass
+
+    def reset(self) -> None:
+        # signal block
+        self.block = np.zeros(shape=(self.L, self.N), dtype=np.complex128)
+        # local primal
+        self.x = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # self.x[0::self.L] = 1
+        # local dual
+        self.y = np.zeros(shape=(self.L * self.N, 1), dtype=np.complex128)
+        # local copy of global primal
[…]

### 2022-10-12 simulations/rnd_con.py

@@ -21,7 +21,7 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
     if alg == "opt":
         import admm_fq as adf
     if alg == "davg":
-        import admm_fq_distavg as adf
+        import admm_fq_distavg_opt as adf
 
     rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
     ## %%

### 2022-10-12 simulations/static.py

@@ -20,7 +20,9 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
     if alg == "opt":
         import admm_fq as adf
     if alg == "davg":
-        import admm_fq_distavg as adf
+        import admm_fq_distavg_opt as adf
+    if alg == "davgad":
+        import admm_fq_distavg_ad as adf
 
     rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
     ## %%
@@ -52,13 +54,13 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
         nw.setAveragingWeights(W)
 
     rho = 1.0
-    stepsize = 0.8
+    stepsize = 0.5
     eta = 0.98
     N_sens = nw.N
-    N_s = 80000
+    N_s = 100000
 
     # true_norms = [2.2, 0.5, 1.2, 0.7, 1.0]
-    true_norms = [rng.uniform(0.5, 3.0) for i in range(N_sens)]
+    true_norms = [rng.uniform(0.5, 2.0) for i in range(N_sens)]
 
     h = np.array([]).reshape(0, 1)
     for n in range(N_sens):
@@ -107,10 +109,11 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
 if __name__ == "__main__":  # Necessary for module loading in condor processes :(
     cfg = simulation.SimConfig(
         id="icassp2023-static",
-        runs=50,
+        runs=30,
         seed=573438,
         variables=[
             {"alg": ["opt"], "SNR": [10], "gamma": [1.0], "iters": [1]},
+            {"alg": ["davgad"], "SNR": [10], "gamma": [1.0], "iters": [1, 2, 10]},
             {
                 "alg": ["davg"],
                 "SNR": [10],
@@ -162,12 +165,12 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     # Define condor job parameters
     user_submit = {
-        "request_walltime": "86000",  # Time in seconds
+        "request_walltime": "3600",  # Time in seconds
         "initialdir": ".",
         "notification": "Error",
         "executable": "/users/sista/mblochbe/python_venvs/admmstuff/bin/python",
         "request_cpus": "1",
-        "request_memory": "8GB",
+        "request_memory": "1GB",
     }
     # %%
     # Submit the condor jobs
[…]

### 2022-10-12 simulations/static.py
static plot

@@ -2,9 +2,23 @@
 import os
 import pandas as pd
 import numpy as np
-import matplotlib.pyplot as plt
+
+# import matplotlib.pyplot as plt
 import python_utils.utils as utils
 import python_utils.simulation as simulation
+
+import matplotlib
+
+matplotlib.use("pgf")
+import matplotlib.pyplot as plt
+
+plt.rcParams.update(
+    {
+        "font.family": "serif",  # use serif/main font for text elements
+        "text.usetex": True,  # use inline math for ticks
+        "pgf.rcfonts": False,  # don't setup fonts from rc parameters
+    }
+)
 
 
 # %%
@@ -113,7 +127,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         seed=573438,
         variables=[
             {"alg": ["opt"], "SNR": [10], "gamma": [1.0], "iters": [1]},
-            {"alg": ["davgad"], "SNR": [10], "gamma": [1.0], "iters": [1, 2, 10]},
+            {"alg": ["davgad"], "SNR": [10], "gamma": [1.0], "iters": [1]},
             {
                 "alg": ["davg"],
                 "SNR": [10],
@@ -158,7 +172,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     sim.clearTmpData()
     # %%
     # Run the simulation locally with n processes
-    sim.runLocal(nprocesses=4, showprogress=True)
+    sim.runLocal(nprocesses=8, showprogress=True)
     # %%
     # Get the result after completion
     result = sim.getResult()
@@ -203,7 +217,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     utils.savefig(fig, "icassp2023-static_plot", format="png")
 
     # %%
-    fig = plt.figure(figsize=(6, 4))
+    styles = ["--<", "-->", "--v", "--s", "--o"]
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"$\gamma$ [1]")
     plt.ylabel("Avg NPM [dB]")
@@ -213,7 +228,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         20
         * np.log10(data.median().T.tail(200).mean()["opt", 1.0, 1])
[…]

### 2022-10-12 simulations/static.py
static plot

@@ -262,9 +262,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     )
 
     plt.grid()
-    plt.ylim(-50, 0)
+    plt.ylim(-40, 0)
     plt.xlim(0, 0.04)
-    plt.legend()
+    plt.legend(ncol=2, prop={"size": 7})
     plt.tight_layout()
     plt.show()
 

### 2022-10-12 simulations/static.py
static plot

@@ -217,11 +217,11 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     utils.savefig(fig, "icassp2023-static_plot", format="png")
 
     # %%
-    styles = ["--<", "-->", "--v", "--s", "--o"]
+    styles = ["-<", "->", "-v", "-s", "-o"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
-    plt.xlabel(r"$\gamma$ [1]")
-    plt.ylabel("Avg NPM [dB]")
+    plt.xlabel(r"Mixing factor $\gamma$ [1]")
+    plt.ylabel("Avg. NPM [dB]")
 
     plt.plot(
         cfg.variable_values[2]["gamma"],

### 2022-10-12 simulations/static.py
static plot

@@ -217,7 +217,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     utils.savefig(fig, "icassp2023-static_plot", format="png")
 
     # %%
-    styles = ["-<", "->", "-v", "-s", "-o"]
+    styles = ["-<", "->", "-v", "-o", "-s"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma$ [1]")
@@ -228,7 +228,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         20
         * np.log10(data.median().T.tail(200).mean()["opt", 1.0, 1])
         * np.ones_like(cfg.variable_values[2]["gamma"]),
-        "k-.",
+        styles.pop(),
         label=f"optimal",
     )
     plt.plot(
@@ -236,7 +236,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         20
         * np.log10(data.median().T.tail(200).mean()["davgad", 1.0, 1])
         * np.ones_like(cfg.variable_values[2]["gamma"]),
-        "-",
+        styles.pop(),
         label=rf"adaptive $\gamma_i$",
     )
     plt.plot(
@@ -262,7 +262,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     )
 
     plt.grid()
-    plt.ylim(-40, 0)
+    plt.ylim(-40, -10)
     plt.xlim(0, 0.04)
     plt.legend(ncol=2, prop={"size": 7})
     plt.tight_layout()

### 2022-10-12 simulations/static.py
static plot

@@ -230,6 +230,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
         label=f"optimal",
+        markersize=3,
+        markevery=(1, 3),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -238,6 +240,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
         label=rf"adaptive $\gamma_i$",
+        markersize=3,
+        markevery=(2, 3),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -245,6 +249,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"$K=1$",
         markersize=3,
+        markevery=(3, 3),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -252,6 +257,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"$K=2$",
         markersize=3,
+        markevery=(4, 3),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -259,6 +265,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"$K=10$",
         markersize=3,
+        markevery=(5, 3),
     )
 
     plt.grid()

### 2022-10-12 simulations/static.py
static plot

@@ -231,7 +231,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=f"optimal",
         markersize=3,
-        markevery=(1, 3),
+        markevery=(1, 2),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -241,7 +241,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"adaptive $\gamma_i$",
         markersize=3,
-        markevery=(2, 3),
+        markevery=(2, 2),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -249,7 +249,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"$K=1$",
         markersize=3,
-        markevery=(3, 3),
+        markevery=(3, 2),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -257,7 +257,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"$K=2$",
         markersize=3,
-        markevery=(4, 3),
+        markevery=(4, 2),
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -265,11 +265,11 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=rf"$K=10$",
         markersize=3,
-        markevery=(5, 3),
+        markevery=(5, 2),
     )
 
     plt.grid()
-    plt.ylim(-40, -10)
+    plt.ylim(-40, -20)
     plt.xlim(0, 0.04)
     plt.legend(ncol=2, prop={"size": 7})
     plt.tight_layout()

### 2022-10-12 paper.tex
fdla, cost, algo

@@
 \address{\(^1\)KU Leuven, Dept. of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept. of Signal Processing and Acoustics, 02150 Espoo, Finland}
-%
-% For example:
-% ------------
-%\address{School\\
-%	Department\\
-%	Address}
-%
-% Two addresses (uncomment and modify for two-address case).
-% ----------------------------------------------------------
-% \twoauthors{M. Blochberger
-%     \thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
-This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
-This research received funding in part from the Research Foundation - Flanders (FWO) grant 12ZD622N.}}
-%         {KU Leuven\\
-%         Dept. of Electrical Engineering (ESAT), STADIUS\\
-%         % STADIUS\\
-%         3001 Leuven, Belgium}
-%         {Filip Elvander}
-%         {Aalto University\\
-%         Dept. of Electronic Systems\\
-%         % Section on Artificial Intelligence and Sound\\
-%         9220 Aalborg, Finland}
-%
+
 \begin{document}
@@
 
-% Main contribution: Avoid broadcasting or relaying of norm values, with distributed averaging approach and low iteration count.
-% Algorithms using a similar approach: \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017}, however these use high numbers of iterations (30) which leads to many per-frame transmissions.
-% Argument against broadcasting: (1)Large-scale networks, where not all nodes can physically communicate with each other, but that is not really that relevant for room acoustics...
-(2) just because.
-this is the network topology and configuratinos that was chosen as in a lot of literature.
-
-% Important context in introduction: BSI, WSN, topology, connection matrix,
-
-% What to show:
-% \begin{itemize}
-%   \item Algorithm extension
-%   \item Results
-%   \begin{itemize}
-%     \item compare results of unextended algorithm (optimal case)
-%     \item with extended: varied iteration count (more iterations: better result, BUT also even 1 iteration can lead to good results)
-%     \item varied mixing factor (there is some optimal \(\gamma\) apparently)
-%     \item Show transmission cost: transmission cost over number of nodes
-%   \end{itemize}
-% \end{itemize}
-
 \section{DISTRIBUTED ADAPTIVE BSI IN SENSOR NETWORKS WITH ONLINE-ADMM}
@@
 \end{todo}
-% In \cite{blochbergerDBSI}, we proposed an adaptive SIMO BSI algorithm based on Online-ADMM.
 In this section, we will introduce certain parts of an adaptive SIMO BSI algorithm based on Online-ADMM \cite{blochbergerDBSI}, which are necessary for the reader to understand its extension of it.
@@
 From this follows the neighborhood of a node \(i\), i.e., the other nodes it is directly connected to, defined as \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\).
+It is to note, that we define the set with \(i \in \Nset_i\) for ease of notation later.
+This does however not represent an actual inter-node link.
 Furthermore, we can define the symmetric adjacency matrix \(\mtxb{C}\) with elements
@@
 \end{align}
-Here, the second step, the update of the so-called consensus variables are of interest for this extension.
+Here, the second step, the update of the so-called consensus variables, is of interest for this extension.
 It is defined \cite{blochbergerDBSI} as
@@
 The denominator of \eqref{eq:online_admm:consensus_update}, \(\|\h\|\), is the stacked vector of the full system. This vector, however, is not available at any of the nodes in the network.
-In \cite{blochbergerDBSI}, we assume that partial squared norms of \(\|\h\|^2 = \sum_{i \in \Mset} \|\h_i\|^2\) are relayed throughout the network until all nodes have the information necessary.
+In \cite{blochbergerDBSI}, we assume that partial squared norms of \(\|\h\|^2 = \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) are relayed throughout the network until all nodes have the information necessary.
 In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}, a similar global value is estimated by a distributed averaging approach, iteratively combining values within neighborhoods until convergence to a network-wide average.
 
-Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} with the further introduction of a mixing factor to include instantaneous values in the recursion.
+Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need of network wide data transmission, with the further introduction of an adaptive mixing factor to include instantaneous values in the recursion.
 
@@
 \label{sec:adaptivenormest}
-We define 
-The FDLA problem, as introduced in \cite{xiaoFastLinearIterations2004}, looks to find optimal weights for distributed linear combinations of the form \(\bm{\phi}^{k+1} = \W \bm{\phi}^{k}\) where \(\bm{\phi}^k = \begin{bmatrix} \phi_1^k & \ldots & \phi_M^k \end{bmatrix}^\T\) is a vector, which initially, at \(k=1\), contains a set of variables, of which an average should be computed iteratively.
-The problem comes in the form of a minimization problem
+
+The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\h_i\|^2\) at each node \(i \in \Mset\).
+To avoid the large number of transmission, which would be necessary to facilitate this, we will approximate the separable squared norm \(\hat{\phi}_i \approx \|\h\|^2= \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
+
+The FDLA problem, as introduced in \cite{xiaoFastLinearIterations2004}, looks to find optimal weights for distributed linear combinations of the form
+\begin{equation}
+    \phi_i({k+1}) = \sum_{j \in \Nset_i} W_{ij} \phi_j({k}),\quad i\in \Mset,\label{eq:adaptivenormest:distlincomb}
+\end{equation}
+which can be written in vector form as \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\), a vector, which initially, at \(k=1\), contains a set of variables, of which an average should be computed.
+To find the optimal weights, the minimization problem
 \begin{equation}
@@
         \text{s.t.}& \quad \W \in \mathcal{C},\, \bm{1}^\T \W = \bm{1}^\T,\, \W \bm{1}= \bm{1}
-  \end{aligned}
+    \end{aligned}\label{eq:adaptivenormest:fdlaminprob}
 \end{equation}
-
+is solved.
 The set \(\mathcal{C} = \{\W \in \mathbb{R}^{M \times M} \vert W_{ij} = 0 \text{ if } \{i,j\} \notin \mathcal{E}\}\) describes all matrices with the same sparsity pattern as the adjacency matrix \(\mtxb{C}\).
-
-where the weights used by node \(i\) to combine values from neighbor nodes \(j \in \Nset_i\) are given at the \(i\)-th row.
-The distributed averaging approach is an iterative approach, however here, we will try to find a way to limit the number of iterations necessary.
-This goal comes from the fact that the iterations require data from neighboring nodes leading to additional transmissions (per frame).
-
-% We take avantage of the fact that the squared norm of the stacked solution vector can be separated into
-% \begin{equation}
-%   \| \h \|^2 = \sum_{j \in \Mset} \|\h_j\|^2.
-% \end{equation}
-We define the approximation of the global norm \(\hat{\phi}_i \approx \|\h\|^2\) at each node \(i\) at frame \(m\) as follows:
+Now, the \(i\)-th row of the optimal \(\W\) contains the neigborhood weights for node \(i\) as non-zero entries.
+\begin{todo}
+    This section reads awkward
+\end{todo}
+In usual applications of the iteration \eqref{eq:adaptivenormest:distlincomb}, it is applied \(K \in \mathbb{N}\) times until convergence of the averages is reached.
+This means that in an adaptive algorithm, where the resulting variable is required at each time frame \(m\), it introduces a secondary iteration of \(K\) loops per frame (e.g.
+\cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}).
+Each iteration requires information exchange within neighborhoods, which is why our approach is to try to split iterations over frames to keep \(K\) low.
+For this, we further introduce an instantaneous weighted neighborhood average of node-wise squared norm values \(\bar{\phi}_i^{m} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^m\|^2\) which is then combined with the FDLA estimate into
 \begin{equation}
-  \phi_i^{m,k+1} = \sum_{j \in \Nset_i} W_{ij} \phi_j^{m,k}\quad\text{for }k=1,\ldots,K\label{eq:dist_norm_est_iter}
+    \hat{\phi}_i^{m+1} = \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m}(K)
 \end{equation}
-with the initial value at \(m=1,k=1\) defined as \(\phi_i^{1,1}=\|\h_i^{1}\|^2\).
-\eqref{eq:dist_norm_est_iter} is applied \(K\) times.
-We now define the frame estimate of the global squared norm as
-\begin{equation}
-  \hat{\phi}_i^{m+1} = \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m,K}
-\end{equation}
-where \(\bar{\phi}_i^{m} = \sum_{j \in \Nset_i} W_{ij} \|\h_i^m\|^2\) is an instantaneous weighted neighborhood average of node-wise squared norm values and \(\gamma_i\) is a mixing factor.
-This factor can be chosen as a fixed value, where simulations have shown that values around \(\gamma_i = 0.02\) lead to satisfying results (cf. FIGURE) or adaptively.
-For this, we use the instantaneous values to track stationarity of the squared norms by setting the factor \(\gamma_i^{m}\) proportional to the absolute difference between instantaneous neighborhood norm values of subsequent frames
+where \(\gamma_i\) is a mixing factor.
+To avoid choosing a fixed value for \(\gamma_i\), we track stationarity of the instantaneous \(\bar{\phi}_i^{m}\) and set \(\gamma_i^{m}\) proportional to the absolute difference between subsequent frames
 \begin{equation}
@@
 \end{equation}
-
-The special case of \(K=1\) leads to the update step:
-\begin{equation}
-  \hat{\phi}_i^{m+1} = \gamma_i \sum_{j \in \Nset_i} W_{ij} \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma_i) \sum_{j \in \Nset_i} w_{ij} \hat{\phi}_j^m
-\end{equation}
-
-We use these in an inbetween step to estimate the norms of the channel impulse responses recursively. The full algorithm then looks like
+\begin{todo}
+    explain better why.
+Thought process: smaller difference \(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |\) means estimate approaches some steady-state, which then means that putting more emphasis on norm estimation might lead to improvement: make \(\gamma\) smaller.
+\(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} | \rightarrow 0\) then \(\gamma_i \rightarrow 0\)
+\end{todo}
+The combination of instantaneous values and distributed averaging estimate leads to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed increases as well.
+\autoref{alg:davg_norm_est} summarizes the procedure.
 
 \begin{algorithm}
-  \caption{Estimation of norm values}\label{alg:davg_norm_est}
-  $i\gets 10$\;
-  \eIf{$i\geq 5$}
+    \caption{ADMM BSI with FDLA-based adaptive estimation of norm values}\label{alg:davg_norm_est}
+    \(m\gets 1\)\;
+    \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
+    \(\bar{\phi}_i^{0} \gets 1, \forall i \in \Mset\)\;
+    \For(){\(m=1\dots\)}
     {
-      $i\gets i-1$\;
-  }{
-      \If{$i\leq 3$}
+        \For(){\(i \in \Mset\)}
         {
-          $i\gets i+2$\;
+            \,\\
+            \dots\\
+            \(\w_i^m \gets \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^m,\uu^m)\)\;
+            \(\bar{\h}_i^{m} \gets \) as defined in \cite{blochbergerDBSI}\;
+            Transmit \(\bar{\h}_i^{m}\) to nodes  \(j \in \Nset_i\)\;
+            \(\bar{\phi}_i^{m} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^m\|^2\)\;
+            \(\gamma_i^{m} \gets \min \left\lbrace \frac{| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |}{\bar{\phi}_i^{m-1}},\,1\right\rbrace\)\;
+            \eIf(){\(m = 1\)}
+            {
+                \(\phi_i^{m}(1) \gets \|\bar{\h}_i^m\|^2\)\;
+            }
+            {
+                \(\phi_i^{m}(1) \gets \phi_i^{m-1}(K)\)\;
+            }
+            \For(){\(k=1,\dots,K-1\)}
+            {
+                Transmit \(\phi_i(k)\) to nodes  \(j \in \Nset_i\)\;
+                \(\phi_i({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j({k})\)\;
+            }
+            \(\hat{\phi}_i^{m} \gets \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m}(K)\)\;
+            \(\h_i^{m} \gets \frac{\bar{\h}_i^{m}}{\sqrt{\hat{\phi}_i^{m}M}}\)\;
+            \dots\\
+            \(\uu_i^{m} \gets \uu_i^{m-1} + \rho \left( \w_i^{m} - \tilde{\h}_i^{m} \right)\)\;
+            \dots\\
+            % \,\\
         }
@@
 
-% \begin{align}
-%   \w_i^{m+1} &= \operatorname{argmin} \mathcal{L}_\rho(\w,\h,\uu)\\
-%   \bar{\h}_i^{m+1} &= \bar{\w}_i^{m+1} + \frac{1}{\rho} \bar{\uu}_i^m\\
-%   \phi_i^1 &= \hat{\phi}_i^{m}\\
-%   \phi_i^{k+1} &= \sum_{j \in \Nset_i} w_{ij} \phi_j^{k} \qquad\text{for } k=1,\ldots,K\\
-%   \hat{\phi}_i^{m+1} &= \gamma \| \bar{\h}_j^{m+1} \|^2 + (1-\gamma) \phi_i^K\\
-%   \h_i^{m+1} &= \frac{\bar{\h}_i^{m+1}}{\sqrt{\hat{\phi}_i^K\,M}}\\
-%   \uu_i^{m+1} &= \uu_i^{m} + \rho \left(\w_i^{m+1} - \tilde{\h}_i^{m+1}\right).
-% \end{align}
-
-\section{Transmission cost}
+\section{Effect on transmission cost}
 \label{sec:transcost}
-Show effect on number of transmissions. Scale up to high numbers of nodes so neigborhoods \(<<\) entire network.
-
-\begin{align}
-  \mathcal{O}(&(M-1)^2) & &+ & \mathcal{O}(&(M-1)^2)\\
-  \mathcal{O}(&M-1) & &+ & \mathcal{O}(&(M-1)^2)\\
-  \mathcal{O}(&M \bar{N}_i R) & &+ & \mathcal{O}(&M \bar{N}_i R)
-\end{align}
-
-Or per node:
-\begin{align}
-  \mathcal{O}(&M-1) & &+ & \mathcal{O}(&M-1)\\
-  \mathcal{O}(&1) & &+ & \mathcal{O}(&M-1)\\
-  \mathcal{O}(&\bar{N}_i R) & &+ & \mathcal{O}(&\bar{N}_i R)
-\end{align}
+To describe the communication cost within the network, we adopt the Big-O notation similar to the complexity analysis of algorithms.
+We consider the communication of a variable from one node to another as \(\mathcal{O}(1)+\mathcal{O}(1)\), where the two terms represent transmit and receive operations, respectively, as both require computational resources at a node.
+The most useful measure in the case of this work is to analyze the cost per node.
+For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
+We compare the following communication schemes: (1) a fully connected network, i.e., all nodes are linked with all other nodes by direct links; (2) network with broadcasting, i.e., the nodes transmit to all other nodes without direct links; (3) nodes only communicate with neighboring nodes.
+For (1), the cost increases quadratically with increasing network size \(M\) both in transmit and receive operations, whereas for (2), the quadratic increase happens only at the latter.
+Using communication scheme (3), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed in this paper, cost in proportional to neighborhood size and iteration count \(K\).
+Refer to \autoref{tab:transcost:table} for the collected orders of communication cost.
+\begin{todo}
+    this seems small for a full section header
+\end{todo}
+\begin{table}
+    \centering
+    \begin{tabular}{ |c|c|c| } 
+        \hline
+        & Transmit & Receive \\
+        \hline\hline
+        Full & \(\mathcal{O}(M-1)\) & \(\mathcal{O}(M-1)\) \\
+        \hline
+        Broadcast & \(\mathcal{O}(1)\) & \(\mathcal{O}(M-1)\) \\ 
+        \hline
+        Neigborhood & \(\mathcal{O}(\bar{N}_i K)\) & \(\mathcal{O}(\bar{N}_i K)\) \\ 
+        \hline
+    \end{tabular}
+    \caption[]{}
+    \label{tab:transcost:table}
+\end{table}
 
@@
     \centering
-  \input{simulations/plots/transcost/transcost.pgf}
+    % \input{simulations/plots/transcost/transcost.pgf}
     \input{simulations/plots/transcostnode/transcostnode.pgf}
     \vspace*{-0.8cm}
-  \caption[]{The order of transmission cost of entire network or single node (choose which to keep if at all.).}
+    \caption[]{A graphical representation of the order of transmission cost of a single node within the network dependent on network size. One can observe that with neighborhood }
     \label{fig:transcost:bigo}
@@
 \begin{itemize}
-  \item compare results of unextended algorithm (optimal case where all norm values are known)
-  \item varied iteration count (more iterations: better result, BUT also even 1 iteration can lead to good results, which doesnt need additional communitation per frame)
-  \item varied mixing factor (the is some optimum apparently, but unknown why and what it means)
     \item evaluate on time-varying norms of IRs
 \end{itemize}
+
+\begin{figure}
+    \centering
+    \input{simulations/plots/icassp2023-static/icassp2023-static.pgf}
+    \caption[]{}
+\end{figure}
 

### 2022-10-12 simulations/static.py
static plot

@@ -239,7 +239,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         * np.log10(data.median().T.tail(200).mean()["davgad", 1.0, 1])
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
-        label=rf"adaptive $\gamma_i$",
+        label=rf"adaptive $\gamma_i,\,K=1$",
         markersize=3,
         markevery=(2, 2),
     )
@@ -247,7 +247,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         cfg.variable_values[2]["gamma"],
         20 * np.log10(data.median().T.tail(200).mean()["davg", :, 1]),
         styles.pop(),
-        label=rf"$K=1$",
+        label=rf"fixed $\gamma_i,\,K=1$",
         markersize=3,
         markevery=(3, 2),
     )
@@ -255,7 +255,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         cfg.variable_values[2]["gamma"],
         20 * np.log10(data.median().T.tail(200).mean()["davg", :, 2]),
         styles.pop(),
-        label=rf"$K=2$",
+        label=rf"fixed $\gamma_i,\,K=2$",
         markersize=3,
         markevery=(4, 2),
     )
@@ -263,7 +263,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         cfg.variable_values[2]["gamma"],
         20 * np.log10(data.median().T.tail(200).mean()["davg", :, 10]),
         styles.pop(),
-        label=rf"$K=10$",
+        label=rf"fixed $\gamma_i,\,K=10$",
         markersize=3,
         markevery=(5, 2),
     )

### 2022-10-12 simulations/static.py
static plot

@@ -271,7 +271,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(-40, -20)
     plt.xlim(0, 0.04)
-    plt.legend(ncol=2, prop={"size": 7})
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.8)
     plt.tight_layout()
     plt.show()
 

### 2022-10-12 simulations/static.py
static plot

@@ -271,8 +271,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(-40, -20)
     plt.xlim(0, 0.04)
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.8)
-    plt.tight_layout()
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.6)
+    # plt.tight_layout()
     plt.show()
 
     # %%

### 2022-10-12 simulations/static.py
static plot

@@ -271,8 +271,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(-40, -20)
     plt.xlim(0, 0.04)
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.6)
-    # plt.tight_layout()
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
+    plt.tight_layout(pad=0.5)
     plt.show()
 
     # %%

### 2022-10-12 simulations/static.py
static plot

@@ -278,4 +278,53 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     utils.savefig(fig, "icassp2023-static", format="pgf", pgf_font="serif")
 
+    # %%
+    # Plot
+    styles = ["-<", "->", "-v", "-o", "-s"]
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
+    # plt.title("Title")
+    plt.xlabel("Time [frames]")
+    plt.ylabel("NPM [dB]")
+    plt.plot(
+        20 * np.log10(data.median().T["opt", 1.0, 1]),
+        styles.pop(),
+        label=f"optimal",
+        markersize=3,
+        markevery=(1, 2),
+    )
+    plt.plot(
+        20 * np.log10(data.median().T["davgad", 1.0, 1]),
+        styles.pop(),
+        label=rf"adaptive $\gamma_i,\,K=1$",
+        markersize=3,
+        markevery=(2, 2),
+    )
+    plt.plot(
+        20 * np.log10(data.median().T["davg", 0.01, 1]),
+        styles.pop(),
+        label=rf"fixed $\gamma_i,\,K=1$",
+        markersize=3,
+        markevery=(1, 2),
+    )
+    plt.plot(
+        20 * np.log10(data.median().T["davg", 0.01, 2]),
+        styles.pop(),
+        label=rf"fixed $\gamma_i,\,K=2$",
+        markersize=3,
+        markevery=(1, 2),
+    )
+    plt.plot(
+        20 * np.log10(data.median().T["davg", 0.01, 1]),
+        styles.pop(),
+        label=rf"fixed $\gamma_i,\,K=10$",
+        markersize=3,
+        markevery=(1, 2),
+    )
+    plt.legend()
+    plt.grid()
+    plt.tight_layout(pad=0.5)
+    plt.show()
+    # %%
+    utils.savefig(fig, "icassp2023-static-time", format="pgf", pgf_font="serif")
+
 # %%

### 2022-10-12 simulations/static.py
plot time

@@ -290,35 +290,35 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=f"optimal",
         markersize=3,
-        markevery=(1, 2),
+        markevery=(1, 500),
     )
     plt.plot(
         20 * np.log10(data.median().T["davgad", 1.0, 1]),
         styles.pop(),
         label=rf"adaptive $\gamma_i,\,K=1$",
         markersize=3,
-        markevery=(2, 2),
+        markevery=(50, 500),
     )
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.01, 1]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=1$",
         markersize=3,
-        markevery=(1, 2),
+        markevery=(100, 500),
     )
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.01, 2]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=2$",
         markersize=3,
-        markevery=(1, 2),
+        markevery=(150, 500),
     )
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.01, 1]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=10$",
         markersize=3,
-        markevery=(1, 2),
+        markevery=(200, 500),
     )
     plt.legend()
     plt.grid()

### 2022-10-12 simulations/static.py
plot time

@@ -280,7 +280,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    styles = ["-<", "->", "-v", "-o", "-s"]
+    styles = ["-+", "-x", "-<", "->", "-v", "-o", "-s"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
@@ -290,37 +290,58 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         styles.pop(),
         label=f"optimal",
         markersize=3,
-        markevery=(1, 500),
+        markevery=(1, 200),
     )
     plt.plot(
         20 * np.log10(data.median().T["davgad", 1.0, 1]),
         styles.pop(),
         label=rf"adaptive $\gamma_i,\,K=1$",
         markersize=3,
-        markevery=(50, 500),
+        markevery=(20, 200),
     )
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.01, 1]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=1$",
         markersize=3,
-        markevery=(100, 500),
+        markevery=(40, 200),
     )
+    # plt.plot(
+    #     20 * np.log10(data.median().T["davg", 0.01, 2]),
+    #     styles.pop(),
+    #     label=rf"fixed $\gamma_i,\,K=2$",
+    #     markersize=3,
+    #     markevery=(60, 200),
+    # )
     plt.plot(
-        20 * np.log10(data.median().T["davg", 0.01, 2]),
-        styles.pop(),
-        label=rf"fixed $\gamma_i,\,K=2$",
-        markersize=3,
-        markevery=(150, 500),
-    )
-    plt.plot(
-        20 * np.log10(data.median().T["davg", 0.01, 1]),
+        20 * np.log10(data.median().T["davg", 0.01, 10]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=10$",
         markersize=3,
-        markevery=(200, 500),
+        markevery=(80, 200),
     )
-    plt.legend()
+    plt.plot(
+        20 * np.log10(data.median().T["davg", 0.04, 1]),
+        styles.pop(),
+        label=rf"fixed $\gamma_i,\,K=1$",
+        markersize=3,
+        markevery=(40, 200),
[…]

### 2022-10-12 simulations/static.py
plots

@@ -217,7 +217,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     utils.savefig(fig, "icassp2023-static_plot", format="png")
 
     # %%
-    styles = ["-<", "->", "-v", "-o", "-s"]
+    styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma$ [1]")
@@ -280,7 +280,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    styles = ["-+", "-x", "-<", "->", "-v", "-o", "-s"]
+    styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
@@ -302,42 +302,42 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.01, 1]),
         styles.pop(),
-        label=rf"fixed $\gamma_i,\,K=1$",
+        label=rf"$\gamma_i = 0.01,\,K=1$",
         markersize=3,
         markevery=(40, 200),
     )
     # plt.plot(
     #     20 * np.log10(data.median().T["davg", 0.01, 2]),
     #     styles.pop(),
-    #     label=rf"fixed $\gamma_i,\,K=2$",
+    #     label=rf"$\gamma_i,\,K=2$",
     #     markersize=3,
     #     markevery=(60, 200),
     # )
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.01, 10]),
         styles.pop(),
-        label=rf"fixed $\gamma_i,\,K=10$",
+        label=rf"$\gamma_i = 0.01,\,K=10$",
         markersize=3,
         markevery=(80, 200),
     )
     plt.plot(
         20 * np.log10(data.median().T["davg", 0.04, 1]),
         styles.pop(),
-        label=rf"fixed $\gamma_i,\,K=1$",
+        label=rf"$\gamma_i = 0.04,\,K=1$",
         markersize=3,
[…]

### 2022-10-12 simulations/static.py
plot time

@@ -7,6 +7,11 @@ import numpy as np
 import python_utils.utils as utils
 import python_utils.simulation as simulation
 
+# %%
+# import matplotlib
+# import matplotlib.pyplot as plt
+
+# %%
 import matplotlib
 
 matplotlib.use("pgf")
@@ -169,7 +174,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     sim = simulation.Simulation(cfg, os.path.realpath(__file__), simulate)
     # %%
     # Delete generated data if necessary
-    sim.clearTmpData()
+    # sim.clearTmpData()
     # %%
     # Run the simulation locally with n processes
     sim.runLocal(nprocesses=8, showprogress=True)
@@ -201,20 +206,6 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         result = sim.getResult()
     # %%
     data = result.df.groupby(["alg", "gamma", "iters"])
-    # %%
-    # Plot
-    fig = plt.figure(figsize=(6, 4))
-    plt.title("Title")
-    plt.xlabel("Series [1]")
-    plt.ylabel("Value [1]")
-    # labels = [rf"{label}" for label in data.groups.keys()]
-    plt.plot(20 * np.log10(data.median().T["opt", 1.0, 1]))
-    plt.legend()
-    plt.grid()
-    plt.tight_layout()
-    plt.show()
-    # %%
-    utils.savefig(fig, "icassp2023-static_plot", format="png")
 
     # %%
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
@@ -280,67 +271,145 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
+    mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")
-    plt.plot(
+    # #########
+    (line,) = plt.plot(
         20 * np.log10(data.median().T["opt", 1.0, 1]),
-        styles.pop(),
+        "k-",
+        label=f"_optimal",
+        markersize=3,
+        markevery=(1, 200),
+        alpha=0.25,
+    )
+    plt.plot(
+        20
+        * np.log10(
+            np.convolve(
[…]

### 2022-10-12 simulations/static.py
plots

@@ -208,7 +208,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     data = result.df.groupby(["alg", "gamma", "iters"])
 
     # %%
-    styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
+    styles = ["-v", "-+", "-x", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma$ [1]")
@@ -221,7 +221,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
         label=f"optimal",
-        markersize=3,
+        markersize=4,
         markevery=(1, 2),
     )
     plt.plot(
@@ -231,7 +231,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
         label=rf"adaptive $\gamma_i,\,K=1$",
-        markersize=3,
+        markersize=4,
         markevery=(2, 2),
     )
     plt.plot(
@@ -239,7 +239,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         20 * np.log10(data.median().T.tail(200).mean()["davg", :, 1]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=1$",
-        markersize=3,
+        markersize=4,
         markevery=(1, 2),
     )
     plt.plot(
@@ -247,7 +247,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         20 * np.log10(data.median().T.tail(200).mean()["davg", :, 2]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=2$",
-        markersize=3,
+        markersize=4,
         markevery=(2, 2),
     )
     plt.plot(
@@ -255,7 +255,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         20 * np.log10(data.median().T.tail(200).mean()["davg", :, 10]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=10$",
-        markersize=3,
+        markersize=4,
         markevery=(1, 2),
     )
 
[…]

### 2022-10-12 simulations/static.py
plots

@@ -412,6 +412,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # #########
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
+    plt.ylim(-40, 0)
+    plt.xlim(0, 6000)
     plt.tight_layout(pad=0.5)
     plt.show()
     # %%

### 2022-10-13 simulations/static.py
plots

@@ -223,6 +223,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=f"optimal",
         markersize=4,
         markevery=(1, 2),
+        markerfacecolor="none",
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -233,6 +234,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=rf"adaptive $\gamma_i,\,K=1$",
         markersize=4,
         markevery=(2, 2),
+        markerfacecolor="none",
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -241,6 +243,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=rf"fixed $\gamma_i,\,K=1$",
         markersize=4,
         markevery=(1, 2),
+        markerfacecolor="none",
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -249,6 +252,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=rf"fixed $\gamma_i,\,K=2$",
         markersize=4,
         markevery=(2, 2),
+        markerfacecolor="none",
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -257,6 +261,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=rf"fixed $\gamma_i,\,K=10$",
         markersize=4,
         markevery=(1, 2),
+        markerfacecolor="none",
     )
 
     plt.grid()
@@ -298,6 +303,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(1, 500),
         color=line.get_color(),
+        markerfacecolor="none",
     )
     # #########
     (line,) = plt.plot(
@@ -320,6 +326,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(20, 500),
         color=line.get_color(),
+        markerfacecolor="none",
     )
     # #########
     (line,) = plt.plot(
@@ -342,6 +349,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(40, 500),
         color=line.get_color(),
+        markerfacecolor="none",
     )
     # #########
     (line,) = plt.plot(
[…]

### 2022-10-13 paper.tex
simulation plots and transmission cost plot
first content complete version

@@
 \label{sec:dbsi}
-\begin{todo}
-    Introduce signal model, \(\h\),...
-\end{todo}
 In this section, we will introduce certain parts of an adaptive SIMO BSI algorithm based on Online-ADMM \cite{blochbergerDBSI}, which are necessary for the reader to understand its extension of it.
@@
 
+\subsection[]{Sensor network}
 We assume a set \(\Mset \triangleq \{1,\ldots,M\}\) sensor nodes and a set of edges \(\mathcal{E}\) which connect the nodes forming a sensor network.
@@
 \begin{equation}
-    c_{ij} = \begin{cases}
+    C_{ij} = \begin{cases}
         1 \quad \text{if } i = j\\
@@
 
-In BSI, the coss-relation problem formulation uses relative information between sensor signals to identify the system, i.e., the acoustic or communication channels.
-The solution to this problem is found by the minimization problem (cf. e.g. \cite{langtongBlindIdentificationEqualization1994,huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003})
+\subsection[]{Signal model}
+We consider a SIMO system with input signal \(\mtxb{s}(n) = [s(n),\,\ldots,\,s(n-2L+2)]^{\T}\) and \(M\) output signals \(\x_i(n)= [x_i(n),\,\ldots,\,x_i(n-L+1)]^{\T}\).
+Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated with \(\mtxb{s}(n)\).
+The signal model is \(\x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n),\)
+with \(\mtxb{H}_i\), the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) of length \(L\).
+For the purpose of this paper, the length \(L\) of the impulse responses is assumed to be known.
+
+\subsection[]{Distributed BSI with Online-ADMM}
+In BSI, the coss-relation problem formulation only uses output signals \(\x_i(n)\), exploiting relative information between them, to identify the system, i.e., the acoustic or communication channels \(\h_t = [\h_1^\T,\,...,\,\h_M^\T]^\T\) (subscript \(t\) indicates \emph{true} system as opposed to an estimate).
+The solution to this problem is found by the minimization problem (cf.
+e.g.
+\cite{langtongBlindIdentificationEqualization1994,huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003,blochbergerDBSI})
 \begin{equation}
     \begin{aligned}
-        \hat{\h} = \arg \min_{\h} \quad &\h^\herm \hat{\R} \h \\
+        \h = \arg \min_{\h} \quad &\h^\herm \R \h \\
         \text{s.t. } \quad &\h^\herm \h = 1.
@@
 \end{equation}
-\begin{todo}
-    Introduce \(\w, \uu\)
-\end{todo}
-Separating the cost function and appying general-form consensus ADMM as an adaptive algorithm leads to the update steps
+Separating the cost function and applying general-form consensus ADMM as an adaptive algorithm leads to the update steps
 \begin{align}
@@
     \h^{m+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{m+1},\h,\uu^m)\label{eq:general_consensus_admm:global}\\
-    \uu_i^{m+1} &= \uu_i^{m} + \rho \left( \w_i^{m+1} - \tilde{\h}_i^{m+1} \right).\label{eq:general_consensus_admm:dual}
+    \uu_i^{m+1} &= \uu_i^{m} + \rho \left( \w_i^{m+1} - \tilde{\h}_i^{m+1} \right),\label{eq:general_consensus_admm:dual}
 \end{align}
-Here, the second step, the update of the so-called consensus variables, is of interest for this extension.
+where \(\w_i\) represents channels estimates of lower dimensional subproblems, solved locally by node \(i\), \(\h = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) the consensus variable (estimate of the system), and \(\uu_i\) are the dual variables.
+The updates of \(\hat{\h}_i\) are of interest for this extension.
 It is defined \cite{blochbergerDBSI} as
 \begin{equation}
-    \h_i^{m+1} = \frac{\bar{\h}_i^{m+1}}{\|\h^{m+1}\|}\label{eq:online_admm:consensus_update}
+    \hat{\h_i}^{m+1} = \frac{\bar{\h}_i^{m+1}}{\|\h^{m+1}\|}\label{eq:online_admm:consensus_update}
 \end{equation}
-for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{m+1}\), a combination of neigborhood averages of the channel response estimates and the dual variables of channel \(i\) respectively, computed at node \(i\).
+for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{m+1}\), a combination of neigborhood averages of \(\w_j\) and \(\uu_j\), \(j \in \Nset_i\).
 The denominator of \eqref{eq:online_admm:consensus_update}, \(\|\h\|\), is the stacked vector of the full system. This vector, however, is not available at any of the nodes in the network.
@@
 
-The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\h_i\|^2\) at each node \(i \in \Mset\).
+\subsection[]{Distributed averaging}
+The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\hat{\h_i}\|^2\) at each node \(i \in \Mset\).
 To avoid the large number of transmission, which would be necessary to facilitate this, we will approximate the separable squared norm \(\hat{\phi}_i \approx \|\h\|^2= \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
@@
 \end{equation}
-which can be written in vector form as \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\), a vector, which initially, at \(k=1\), contains a set of variables, of which an average should be computed.
+which can be written in vector form as \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\), a vector, which initially, at \(k=1\), contains a set of variables, an average of which should be computed.
 To find the optimal weights, the minimization problem
@@
     \begin{aligned}
-        \min& \quad \| \W - \bm{1}\bm{1}^\T/n\|_2\\
+        \min& \quad \| \W - \bm{1}\bm{1}^\T/M\|_2\\
         \text{s.t.}& \quad \W \in \mathcal{C},\, \bm{1}^\T \W = \bm{1}^\T,\, \W \bm{1}= \bm{1}
@@
 Now, the \(i\)-th row of the optimal \(\W\) contains the neigborhood weights for node \(i\) as non-zero entries.
-\begin{todo}
-    This section reads awkward
-\end{todo}
-In usual applications of the iteration \eqref{eq:adaptivenormest:distlincomb}, it is applied \(K \in \mathbb{N}\) times until convergence of the averages is reached.
-This means that in an adaptive algorithm, where the resulting variable is required at each time frame \(m\), it introduces a secondary iteration of \(K\) loops per frame (e.g.
-\cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}).
-Each iteration requires information exchange within neighborhoods, which is why our approach is to try to split iterations over frames to keep \(K\) low.
-For this, we further introduce an instantaneous weighted neighborhood average of node-wise squared norm values \(\bar{\phi}_i^{m} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^m\|^2\) which is then combined with the FDLA estimate into
+% \begin{todo}
+%     This section reads awkward
+% \end{todo}
+% In usual applications of the iteration \eqref{eq:adaptivenormest:distlincomb}, it is applied \(K \in \mathbb{N}\) times until convergence of the averages is reached.
+In an adaptive algorithm, where the resulting variable is required at each time frame \(m\) such as e.g.
+\cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} and \cite{blochbergerDBSI}, it introduces \(K\) secondary iterations per frame.
+Each iteration requires information exchange within neighborhoods, adding to the communication cost of the algorithm.
+We split iterations over frames to keep \(K\) as low as possible.
+For this, we further introduce an instantaneous weighted neighborhood average of node-wise squared norm values \(\bar{\phi}_i^{m} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^m\|^2\) which is then combined with the iterative average into
 \begin{equation}
@@
 where \(\gamma_i\) is a mixing factor.
-To avoid choosing a fixed value for \(\gamma_i\), we track stationarity of the instantaneous \(\bar{\phi}_i^{m}\) and set \(\gamma_i^{m}\) proportional to the absolute difference between subsequent frames
+The factor balances instantaneous values and the distributed averaging iterations.
+This facilitates introduction of new information and the convergence of the distributed averaging, respectively.
+% The factor balances instantaneous values and the distributed averaging iterations, and we shoudl look at the two extreme cases for further insight.
+% For \(\gamma_i = 0\), only instantaneous neighborhood averages are used, which effectively leads to suboptimal computation, as \(\hat{\phi}_1^{m} = \hat{\phi}_2^{m} = \ldots = \hat{\phi}_M^{m}\) for large enough \(m\) will never be reached.
+% For \(\gamma_i=1\), only the distributed averaging iterations are considered, i.e., we effectively combine the per-frame secondary recursion \eqref{eq:adaptivenormest:distlincomb} from \(K\) to \(mK\) iterations.
+% There however, no new data is introduced which leads to performance degradadation in the adaptive algorithm as it only considers inital estimates from \(m=1\), which might be far of the optimum.
+
+\subsection[]{Adaptive mixing factor}
+To avoid choosing a fixed value for \(\gamma_i\), we track stationarity of the instantaneous \(\bar{\phi}_i^{m}\).
+If the absolute difference between subsequent frames \(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |\) nears 0, then this means that the estimation of \(\w_i, \bar{\h}_i\) is converging to a steady state.
+Is this the case, then the emphasis of the algorithm should lie on norm estimation, i.e. the distributed averaging recursion, which in turn means \(\gamma_i\) should go towards 0 as well.
+We set \(\gamma_i^{m}\) proportional to the absolute difference between subsequent frames and set an upper limit at 1,
 \begin{equation}
-    \gamma_i^{m} = \min \left\lbrace \frac{| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |}{\bar{\phi}_i^{m-1}},\,1\right\rbrace.
+    \gamma_i^{m} = \min \left\lbrace \frac{| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |}{\bar{\phi}_i^{m-1}},\,1\right\rbrace.\label{eq:adaptivenormest:adaptivegamma}
 \end{equation}
-\begin{todo}
-    explain better why.
-Thought process: smaller difference \(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |\) means estimate approaches some steady-state, which then means that putting more emphasis on norm estimation might lead to improvement: make \(\gamma\) smaller.
-\(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} | \rightarrow 0\) then \(\gamma_i \rightarrow 0\)
-\end{todo}
-The combination of instantaneous values and distributed averaging estimate leads to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed increases as well.
-\autoref{alg:davg_norm_est} summarizes the procedure.
+The combination of instantaneous values and distributed averaging estimate should lead to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed should increase as well.
+\autoref{alg:davg_norm_est} summarizes the procedure as is is introduced in this section.
 
-\begin{algorithm}
+\begin{algorithm}[t]
     \caption{ADMM BSI with FDLA-based adaptive estimation of norm values}\label{alg:davg_norm_est}
-    \(m\gets 1\)\;
     \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
@@
         {
-            \,\\
-            \dots\\
-            \(\w_i^m \gets \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^m,\uu^m)\)\;
-            \(\bar{\h}_i^{m} \gets \) as defined in \cite{blochbergerDBSI}\;
+            % \(\cdots\)\\
+            % \(\w_i^m \gets \operatorname{argmin}_{\w_i}\, \mathcal{L}_{\rho} (\w,\h^m,\uu^m)\)\;
+            % Compute \(\bar{\h}_i^{m}\)\;
+            % \(\cdots\)\\
+            \emph{The steps before are as introduced in }\cite{blochbergerDBSI}\\
+            \dotfill\\
             Transmit \(\bar{\h}_i^{m}\) to nodes  \(j \in \Nset_i\)\;
@@
             }
-            \For(){\(k=1,\dots,K-1\)}
+            \For(){\(k=1,\dots,K\)}
             {
@@
             \(\hat{\phi}_i^{m} \gets \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m}(K)\)\;
-            \(\h_i^{m} \gets \frac{\bar{\h}_i^{m}}{\sqrt{\hat{\phi}_i^{m}M}}\)\;
-            \dots\\
-            \(\uu_i^{m} \gets \uu_i^{m-1} + \rho \left( \w_i^{m} - \tilde{\h}_i^{m} \right)\)\;
-            \dots\\
-            % \,\\
+            \(\hat{\h_i}^{m} \gets \frac{\bar{\h}_i^{m}}{\sqrt{\hat{\phi}_i^{m}M}}\)\;
+            \dotfill\\
+            \emph{The steps after are as introduced in }\cite{blochbergerDBSI}\\
+            % \(\cdots\)\\
+            % \(\uu_i^{m} \gets \uu_i^{m-1} + \rho \left( \w_i^{m} - \tilde{\h}_i^{m} \right)\)\;
+            % \(\cdots\)\\
+            % % \,\\
         }
@@
 
-\section{Effect on transmission cost}
+% \section{Transmission cost}
+
+\section{Evaluation}
+\label{sec:simulations}
+\subsection[]{Transmission cost}
 \label{sec:transcost}
-To describe the communication cost within the network, we adopt the Big-O notation similar to the complexity analysis of algorithms.
+\begin{table}[t]
+    \centering
+    \begin{tabular}{ |l|l|l| } 
+        \hline
+        & Transmit & Receive \\
+        \hline\hline
+        (1) Full & \(\mathcal{O}(M-1)\) & \(\mathcal{O}(M-1)\) \\
+        \hline
+        (2) Broadcast & \(\mathcal{O}(1)\) & \(\mathcal{O}(M-1)\) \\ 
+        \hline
+        (3) Neigborhood & \(\mathcal{O}(\bar{N}_i K)\) & \(\mathcal{O}(\bar{N}_i K)\) \\ 
+        \hline
+    \end{tabular}
+    \caption[]{Comparison of communication cost.}
+    \label{tab:transcost:table}
+\end{table}
+To describe the communication cost within the network, we adopt the Big-\(\mathcal{O}\) notation, similar to the complexity analysis of algorithms.
 We consider the communication of a variable from one node to another as \(\mathcal{O}(1)+\mathcal{O}(1)\), where the two terms represent transmit and receive operations, respectively, as both require computational resources at a node.
@@
 For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
-We compare the following communication schemes: (1) a fully connected network, i.e., all nodes are linked with all other nodes by direct links; (2) network with broadcasting, i.e., the nodes transmit to all other nodes without direct links; (3) nodes only communicate with neighboring nodes.
-For (1), the cost increases quadratically with increasing network size \(M\) both in transmit and receive operations, whereas for (2), the quadratic increase happens only at the latter.
+We compare the following communication schemes:
+\begin{itemize}
+    \itemsep-0.2em
+    \item[(1)] A fully connected network, i.e., all nodes are linked with all other nodes by direct links, \(\Nset_i = \Mset\).
+    \item[(2)] The nodes employ broadcasting, i.e., the nodes transmit to all other nodes without direct links.
+    \item[(3)] The nodes only communicate with neighboring nodes, \(\Nset_i \subset \Mset\).
+\end{itemize}
+For (1), the cost increases quadratically with increasing network size \(M\), both in transmit and receive operations, whereas for (2), the quadratic increase happens only at the latter.
 Using communication scheme (3), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed in this paper, cost in proportional to neighborhood size and iteration count \(K\).
 Refer to \autoref{tab:transcost:table} for the collected orders of communication cost.
-\begin{todo}
-    this seems small for a full section header
-\end{todo}
-\begin{table}
+
+% \begin{figure}[t]
+%     \centering
+%     \input{simulations/plots/transcostnode/transcostnode.pgf}
+%     % \vspace*{-0.8cm}
+%     \caption[]{A graphical representation of the order of transmission cost of a single node within the network dependent on network size.
+One can observe that for the neigborhood-only communication scheme, cost stays constant.
+(This plot might be unnecessary and space consuming)}
+%     \label{fig:transcost:bigo}
+% \end{figure}
+
+\subsection[]{Simulation}
+\begin{figure}[t]
     \centering
-    \begin{tabular}{ |c|c|c| } 
-        \hline
-        & Transmit & Receive \\
-        \hline\hline
-        Full & \(\mathcal{O}(M-1)\) & \(\mathcal{O}(M-1)\) \\
-        \hline
-        Broadcast & \(\mathcal{O}(1)\) & \(\mathcal{O}(M-1)\) \\ 
-        \hline
-        Neigborhood & \(\mathcal{O}(\bar{N}_i K)\) & \(\mathcal{O}(\bar{N}_i K)\) \\ 
-        \hline
-    \end{tabular}
-    \caption[]{}
-    \label{tab:transcost:table}
-\end{table}
-
-\begin{figure}
-    \centering
-    % \input{simulations/plots/transcost/transcost.pgf}
-    \input{simulations/plots/transcostnode/transcostnode.pgf}
-    \vspace*{-0.8cm}
-    \caption[]{A graphical representation of the order of transmission cost of a single node within the network dependent on network size. One can observe that with neighborhood }
-    \label{fig:transcost:bigo}
+    \input{simulations/plots/icassp2023-static-time/icassp2023-static-time.pgf}
+    \caption[]{Median NPM of 30 randomized runs over time for optimal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
+The adaptive method yields results very close to the optimal method.
+A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).}
+    \label{fig:simulations:NPMtime}
 \end{figure}
-
-\section{Simulations}
-\label{sec:simulations}
-Simulations and results.
-\begin{itemize}
-    \item evaluate on time-varying norms of IRs
-\end{itemize}
-
-\begin{figure}
+\begin{figure}[t]
     \centering
     \input{simulations/plots/icassp2023-static/icassp2023-static.pgf}
-    \caption[]{}
+    \caption[]{Mean over time of median NPM of 30 randomized runs after convergence for varied values for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
+Results for optimal method, and adaptive \(\gamma_i\) included for comparison.}
+    \label{fig:simulations:avgNPMgamma}
 \end{figure}
+To evaluate the effectiveness of the proposed method, simulations were run.
+For this we define the error measure, the normalized projection misalignment
+\begin{equation}
+    \begin{aligned}
+        \text{NPM}(m) &= 20\,\log_{10} \frac{\left\| \mtxb{e} \right\|}{\left\|\h(m)\right\|},\\
+        \text{with}\quad \mtxb{e} &= \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m),
+    \end{aligned}
+\end{equation}
+commonly used in BSI to compare estimated \(\h\) and true \(\h_t\).
+The simulation setup is a network with \(M=5\) nodes arranged in a ring topology, each node having \(|N_i|=2\) neighbors.
+The input signal is zero-mean white Gaussian noise (WGN), the impulse responses of length \(L=16\) are zero-mean WGN as well, and at each channel, independent WGN is added with \(\text{SNR}=10\,\text{dB}\).
+The norms of the impulse responses are scaled to random values from the uniform distribution \(\mathcal{U}_{[0.5,2.0]}\).
+A comparison is made between the following cases:
+\begin{itemize}
+    \itemsep-0.2em
+    \item[(a)] all information is available for global norm computation ("optimal" in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
+    \item[(b)] neighborhood communication with fixed \(\gamma_i \in [0.0, 0.4]\) and \(K \in \{1,2,10\}\),
+    \item[(b)] neighborhood communication with adaptive \(\gamma_i\) \eqref{eq:adaptivenormest:adaptivegamma} and \(K=1\).
+\end{itemize}
+\autoref{fig:simulations:NPMtime} shows the median of 30 Monte-Carlo runs.
+We can observe that when fixing \(\gamma_i\), a tradeoff between convergence speed and steady-state error arises at low iteration counts (cf. also \autoref{fig:simulations:avgNPMgamma}).
+With \(K=10\), the performance comes close to the optimal case at the cost of additional communication between nodes.
+Compare that to the case with adaptive \(\gamma_i\) where even at \(K=1\), i.e., no additional communication for the recursive estimation scheme, convergence speed and steady-state error are close to the optimal case.
+
+\begin{todo}
+    Now that I write this, i wonder if evaluating this extension would rather revolve around measuring how well the norms are approximated\dots
+\end{todo}
+\begin{todo}
+    evaluate on time-varying norms of IRs if there is space
+\end{todo}
 
@@
 \label{sec:conclusions}
-Good results coming close to optimal case with less transmissions.
+In this contribution, we propose an extension to a distributed adaptive BSI algorithm applied in sensor networks.
+Based on distributed averaging, only using the information provided by neighboring nodes in the sensor network, we compute estimates of norm values of channel estimates in order to enforce a norm constraint.
+By balancing the averaging with introducing new data into the recursion, we allow the algorithm to follow an adaptive updating scheme.
+The mixing factor, which balances new data with recursion data, is set adaptively dependent on instantaneous channel estimate norms.
+
+These introductions reduce inter-node transmissions for each time frame and improve steady-state estimation performance to values close to the optimal case, where network-wide information is available at all nodes.
 

### 2022-10-14 simulations/static.py
plot

@@ -22,6 +22,7 @@ plt.rcParams.update(
         "font.family": "serif",  # use serif/main font for text elements
         "text.usetex": True,  # use inline math for ticks
         "pgf.rcfonts": False,  # don't setup fonts from rc parameters
+        "font.size": 9,
     }
 )
 
@@ -209,7 +210,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     styles = ["-v", "-+", "-x", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma$ [1]")
     plt.ylabel("Avg. NPM [dB]")
@@ -278,7 +279,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # Plot
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")

### 2022-10-14 simulations/admm_fq_distavg_ad.py
fix mistake

@@ -411,7 +411,7 @@ class Network:
         delta_norm_inst = np.abs(self.norm_inst - norm_inst)
         # gamma_ad = delta_norm_inst / self.norm_inst
 
-        gamma_ad = np.clip(self.gamma * delta_norm_inst / self.norm_inst, 0, 0.5) * 2
+        gamma_ad = np.clip(delta_norm_inst / self.norm_inst, 0.0, 1)
 
         self.gamma_ad.append(gamma_ad)
 
@@ -421,11 +421,12 @@ class Network:
             norms_ = self.W_opt @ norms_
 
         self.norms = gamma_ad * norm_inst + (1 - gamma_ad) * norms_
+        self.norms_ = norms_.copy()
 
         for node_key, node in self.nodes.items():
             self.z[node_key * self.L : (node_key + 1) * self.L] = pp[
                 node_key * self.L : (node_key + 1) * self.L
-            ] / (np.sqrt(norms_[node_key] * self.N))
+            ] / (np.sqrt(self.norms[node_key] * self.N))
 
         self.norm_t.append(np.linalg.norm(self.z))
 

### 2022-10-14 simulations/dynamic.py
dynamic

@@ -1,0 +1,434 @@
+# %%
+import os
+import pandas as pd
+import numpy as np
+
+# import matplotlib.pyplot as plt
+import python_utils.utils as utils
+import python_utils.simulation as simulation
+
+# %%
+import matplotlib
+import matplotlib.pyplot as plt
+
+# %%
+import matplotlib
+
+matplotlib.use("pgf")
+import matplotlib.pyplot as plt
+
+plt.rcParams.update(
+    {
+        "font.family": "serif",  # use serif/main font for text elements
+        "text.usetex": True,  # use inline math for ticks
+        "pgf.rcfonts": False,  # don't setup fonts from rc parameters
+        "font.size": 9,
+    }
+)
+
+
+# %%
+# Define the simulation function.
+# You can define any number of arguments instead of a, b.
+# Remember to add them in SimConfig
+# DO NOT CHANGE run and seed arguments and argument positions!
+def simulate(alg, SNR, gamma, iters, run: int, seed: int):
+    ## %%
+    # All required imports for simulation need to be in here, e.g.,
+    import numpy as np
+
+    if alg == "opt":
+        import admm_fq as adf
+    if alg == "davg":
+        import admm_fq_distavg_opt as adf
+    if alg == "davgad":
+        import admm_fq_distavg_ad as adf
+
+    rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
+    ## %%
+    # ################################################################
+    # Put the simulation code here
+    L = 16
+    nw = adf.Network(L)
+    nw.addNode(0, 1)
+    nw.addNode(1, 1)
+    nw.addNode(2, 1)
+    nw.setConnection(0, [1])
+    nw.setConnection(1, [2])
+    nw.setConnection(2, [0])
+
+    W = np.array(
+        [
+            [0.5, 0.0, 0.5],
+            [0.5, 0.5, 0.0],
+            [0.0, 0.5, 0.5],
+        ]
+    )
+    nw.setAveragingWeights(W)
+
+    rho = 1.0
+    stepsize = 0.5
+    eta = 0.98
+    N_sens = nw.N
+    N_s = 80000
+    SNR = 10
+    iters = 1
+    gamma = 0.000
+
+    h_s = []
+    for n in range(N_sens):
+        h_ = rng.normal(size=(L, 1))
[…]

### 2022-10-14 simulations/rnd_con.py

@@ -1,212 +1,0 @@
-# %%
-import os
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import python_utils.utils as utils
-import python_utils.simulation as simulation
-from cvxpy import Variable, sum_squares, Minimize, Problem, vec
-
-
-# %%
-# Define the simulation function.
-# You can define any number of arguments instead of a, b.
-# Remember to add them in SimConfig
-# DO NOT CHANGE run and seed arguments and argument positions!
-def simulate(alg, SNR, gamma, iters, run: int, seed: int):
-    ## %%
-    # All required imports for simulation need to be in here, e.g.,
-    import numpy as np
-
-    if alg == "opt":
-        import admm_fq as adf
-    if alg == "davg":
-        import admm_fq_distavg_opt as adf
-
-    rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
-    ## %%
-    # ################################################################
-    # Put the simulation code here
-    connectivity_matrix_reshaped = nw.A_.reshape(nw.N * nw.N, 1)
-    pp = np.where(connectivity_matrix_reshaped == 0)
-    connectivity_matrix_zero_indices = pp[0].reshape(-1, 1)
-
-    W_opt = Variable((nw.N, nw.N))
-    objective = Minimize(
-        sum_squares(W_opt - np.divide((np.ones((nw.N, 1)) * np.ones((1, nw.N))), nw.N))
-    )
-    W_vec = vec(W_opt)
-    constraints = (
-        W_vec[connectivity_matrix_zero_indices] == 0,
-        np.ones([1, nw.N]) @ W_opt == np.ones([1, nw.N]),
-        W_opt @ np.ones([nw.N, 1]) == np.ones([nw.N, 1]),
-    )
-    prob = Problem(objective, constraints)
-    result = prob.solve()
-    W = W_opt.value.copy()
-
-    L = 16
-    nw = adf.Network(L)
-    nw.addNode(0, 1)
-    nw.addNode(1, 1)
-    nw.addNode(2, 1)
-    nw.addNode(3, 1)
-    nw.addNode(4, 1)
-    nw.setConnection(0, [1])
-    nw.setConnection(1, [2])
-    nw.setConnection(2, [3])
-    nw.setConnection(3, [4])
-    nw.setConnection(4, [0])
-
-    W = np.array(
-        [
-            [0.5, 0.0, 0.0, 0.0, 0.5],
-            [0.5, 0.5, 0.0, 0.0, 0.0],
[…]

### 2022-10-14 simulations/dynamic.py
plots

@@ -198,30 +198,6 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")
-    # #########
-    # (line,) = plt.plot(
-    #     20 * np.log10(data.median().T["opt", 1.0, 1]),
-    #     "k-",
-    #     label=f"_optimal",
-    #     markersize=4,
-    #     markevery=(1, 500),
-    #     alpha=0.25,
-    # )
-    # plt.plot(
-    #     20
-    #     * np.log10(
-    #         np.convolve(
-    #             data.median().T["opt", 1.0, 1], np.ones(mavg) / mavg, mode="valid"
-    #         )
-    #     ),
-    #     "-",
-    #     label=f"optimal",
-    #     markersize=4,
-    #     markevery=(1, 500),
-    #     color=line.get_color(),
-    #     markerfacecolor="none",
-    # )
-    # #########
     (line,) = plt.plot(
         20 * np.log10(data.median().T["davgad", 0.0, 1][:frames]),
         "-",
@@ -246,103 +222,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         color=line.get_color(),
         markerfacecolor="none",
     )
-    # #########
-    # (line,) = plt.plot(
-    #     20 * np.log10(data.median().T["davg", 0.01, 1]),
-    #     "-",
-    #     label=rf"_$\gamma_i = 0.01,\,K=1$",
-    #     markersize=4,
-    #     markevery=(40, 500),
-    #     alpha=0.25,
-    # )
-    # plt.plot(
-    #     20
-    #     * np.log10(
-    #         np.convolve(
-    #             data.median().T["davg", 0.01, 1], np.ones(mavg) / mavg, mode="valid"
-    #         )
-    #     ),
-    #     "-s",
-    #     label=rf"$\gamma_i = 0.01,\,K=1$",
-    #     markersize=4,
-    #     markevery=(40, 500),
-    #     color=line.get_color(),
-    #     markerfacecolor="none",
-    # )
-    # # #########
-    # (line,) = plt.plot(
-    #     20 * np.log10(data.median().T["davg", 0.01, 10]),
-    #     "-",
[…]

### 2022-10-14 simulations/dynamic.py
plots

@@ -240,7 +240,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\|\mathbf{h}\|\|$ [1]")
     (line,) = plt.plot(
-        data.mean().T["davgad", 0.0, 1][frames : 2 * frames],
+        data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy(),
         "-",
     )
     # #########

### 2022-10-14 simulations/dynamic.py
plots

@@ -222,6 +222,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         color=line.get_color(),
         markerfacecolor="none",
     )
+    plt.vlines(
+        [5000, 10000], 0.75, 1.25, colors=["k", "k"], linestyles=["dashed", "dashed"]
+    )
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
     plt.ylim(-30, 0)
@@ -238,15 +241,18 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
-    plt.ylabel(r"$\|\|\mathbf{h}\|\|$ [1]")
+    plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
     (line,) = plt.plot(
         data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy(),
         "-",
     )
+    plt.vlines(
+        [5000, 10000], 0.75, 1.25, colors=["k", "k"], linestyles=["dashed", "dashed"]
+    )
     # #########
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
-    # plt.ylim(-30, 0)
+    plt.ylim(0.75, 1.25)
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
     plt.show()
@@ -275,6 +281,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         data.mean().T["davgad", 0.0, 1][4 * frames : 5 * frames].to_numpy(),
         "-",
         label=r"$\|\mathbf{h}_2\|$",
+    )
+    plt.vlines(
+        [5000, 10000], 0.75, 1.25, colors=["k", "k"], linestyles=["dashed", "dashed"]
     )
     # #########
     plt.legend(ncol=3, prop={"size": 7}, columnspacing=0.5)

### 2022-10-14 simulations/dynamic.py
plots

@@ -223,7 +223,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markerfacecolor="none",
     )
     plt.vlines(
-        [5000, 10000], 0.75, 1.25, colors=["k", "k"], linestyles=["dashed", "dashed"]
+        [5000, 10000], -30, 0, colors=["k", "k"], linestyles=["dashed", "dashed"]
     )
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
@@ -282,13 +282,11 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         "-",
         label=r"$\|\mathbf{h}_2\|$",
     )
-    plt.vlines(
-        [5000, 10000], 0.75, 1.25, colors=["k", "k"], linestyles=["dashed", "dashed"]
-    )
+    plt.vlines([5000, 10000], 0, 1, colors=["k", "k"], linestyles=["dashed", "dashed"])
     # #########
     plt.legend(ncol=3, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
-    # plt.ylim(-30, 0)
+    plt.ylim(0, 1)
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
     plt.show()

### 2022-10-14 paper.tex
smaller font size for more space

@@
 \begin{document}
-% \ninept
+\ninept
 %
@@
 \begin{abstract}
-  Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce transmission cost and computational complexity or avoid reliance on a single device for processing.
+    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce communication cost and computational complexity or avoid reliance on a single device for processing.
     In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the knowledge of a stacked network-wide solution vector at each node, the computation of which requires either broadcasting or relaying of node-specific values to all other nodes.
     The extended algorithm employs a distributed-averaging-based estimation scheme to estimate the network-wide norm value by only using the information provided by neighboring sensor nodes.
-We introduce a mixing factor between instantaneous and recursion values for adaptivity in a time-varying system.
-The extension leads to a decreased number of transmissions while maintaining estimation performance close to the optimal case.
-Simulation results show how the mixing factor and the averaging scheme's number of iterations influence performance.
+    We introduce an adaptive mixing factor between instantaneous and recursion values for adaptivity in a time-varying system.
+    Simulation results show that the extension provides estimation results close to the optimal fully-connected-network case while reducing inter-node transmission significantly.
 \end{abstract}
@@
 It is to note that in \cite{blochbergerDBSI}, the pairs \(\{i,j\} \in \mathcal{E}\) are ordered, which yields a directed graph and leads to two sets of neighborhoods ("transmit" and "receive") and therefore a non-symmetric adjacency matrix.
-In this paper, we limit the explanation to the undirected graph to save space, as the extension is straightforward.
+For the sake of brevity, we limit the explanations in this paper to the undirected case.
 
@@
             {
-                \(\phi_i^{m}(1) \gets \phi_i^{m-1}(K)\)\;
+                \(\phi_i^{m}(1) \gets \hat{\phi}_i^{m-1}(K)\)\;
             }
@@
 \label{sec:simulations}
-\subsection[]{Transmission cost}
+\subsection[]{Communication cost}
 \label{sec:transcost}
@@
     \item[(b)] neighborhood communication with fixed \(\gamma_i \in [0.0, 0.4]\) and \(K \in \{1,2,10\}\),
-    \item[(b)] neighborhood communication with adaptive \(\gamma_i\) \eqref{eq:adaptivenormest:adaptivegamma} and \(K=1\).
+    \item[(c)] neighborhood communication with adaptive \(\gamma_i\) \eqref{eq:adaptivenormest:adaptivegamma} and \(K=1\).
 \end{itemize}
@@
 \begin{todo}
-    Now that I write this, i wonder if evaluating this extension would rather revolve around measuring how well the norms are approximated\dots
+    TODO: dynamic scenario: add comparisons with optimal and static \(\gamma\) case, and describe in text, add figure captions, extend conclusion
 \end{todo}
-\begin{todo}
-    evaluate on time-varying norms of IRs if there is space
-\end{todo}
+
+\begin{figure}[t]
+    \centering
+    \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
+    \caption[]{}
+    \label{fig:simulations:NPMtimedyn}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}
+    \caption[]{}
+    \label{fig:simulations:normtime}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}
+    \caption[]{}
+    \label{fig:simulations:normstime}
+\end{figure}
 

### 2022-10-15 simulations/dynamic.py
plots

@@ -198,6 +198,14 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")
+    plt.vlines(
+        [5000, 10000],
+        -30,
+        0,
+        colors=["tab:gray", "tab:gray"],
+        linestyles=["dashed", "dashed"],
+        linewidth=[0.5, 0.5],
+    )
     (line,) = plt.plot(
         20 * np.log10(data.median().T["davgad", 0.0, 1][:frames]),
         "-",
@@ -222,9 +230,6 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         color=line.get_color(),
         markerfacecolor="none",
     )
-    plt.vlines(
-        [5000, 10000], -30, 0, colors=["k", "k"], linestyles=["dashed", "dashed"]
-    )
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
     plt.ylim(-30, 0)
@@ -242,12 +247,17 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
+    plt.vlines(
+        [5000, 10000],
+        0.75,
+        1.25,
+        colors=["tab:gray", "tab:gray"],
+        linestyles=["dashed", "dashed"],
+        linewidth=[0.5, 0.5],
+    )
     (line,) = plt.plot(
         data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy(),
         "-",
-    )
-    plt.vlines(
-        [5000, 10000], 0.75, 1.25, colors=["k", "k"], linestyles=["dashed", "dashed"]
     )
     # #########
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
@@ -266,7 +276,15 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
-    plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
+    plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")
+    plt.vlines(
[…]

### 2022-10-15 simulations/dynamic.py
plots

@@ -202,9 +202,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         [5000, 10000],
         -30,
         0,
-        colors=["tab:gray", "tab:gray"],
+        colors=["k", "k"],
         linestyles=["dashed", "dashed"],
-        linewidth=[0.5, 0.5],
+        linewidth=[0.75, 0.75],
     )
     (line,) = plt.plot(
         20 * np.log10(data.median().T["davgad", 0.0, 1][:frames]),
@@ -251,9 +251,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         [5000, 10000],
         0.75,
         1.25,
-        colors=["tab:gray", "tab:gray"],
+        colors=["k", "k"],
         linestyles=["dashed", "dashed"],
-        linewidth=[0.5, 0.5],
+        linewidth=[0.75, 0.75],
     )
     (line,) = plt.plot(
         data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy(),
@@ -281,9 +281,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         [5000, 10000],
         0,
         1,
-        colors=["tab:gray", "tab:gray"],
+        colors=["k", "k"],
         linestyles=["dashed", "dashed"],
-        linewidth=[0.5, 0.5],
+        linewidth=[0.75, 0.75],
     )
     (line,) = plt.plot(
         data.mean().T["davgad", 0.0, 1][2 * frames : 3 * frames].to_numpy(),

### 2022-10-15 simulations/dynamic.py
plots

@@ -245,7 +245,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title("Title")
-    plt.xlabel("Time [frames]")
+    # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
     plt.vlines(
         [5000, 10000],
@@ -264,6 +264,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(0.75, 1.25)
     plt.xlim(0, 15000)
+    plt.xticks([])
     plt.tight_layout(pad=0.5)
     plt.show()
     # %%
@@ -275,7 +276,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title("Title")
-    plt.xlabel("Time [frames]")
+    # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")
     plt.vlines(
         [5000, 10000],
@@ -305,6 +306,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(0, 1)
     plt.xlim(0, 15000)
+    plt.xticks([])
     plt.tight_layout(pad=0.5)
     plt.show()
     # %%

### 2022-10-15 simulations/dynamic.py
plots

@@ -264,7 +264,6 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(0.75, 1.25)
     plt.xlim(0, 15000)
-    plt.xticks([])
     plt.tight_layout(pad=0.5)
     plt.show()
     # %%
@@ -306,7 +305,6 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(0, 1)
     plt.xlim(0, 15000)
-    plt.xticks([])
     plt.tight_layout(pad=0.5)
     plt.show()
     # %%

### 2022-10-15 simulations/dynamic.py
plots

@@ -236,6 +236,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
     plt.show()
+
+    ax = plt.gca()
+    box = ax.get_position()
     # %%
     utils.savefig(fig, "icassp2023-dynamic-time", format="pgf", pgf_font="serif")
 
@@ -260,12 +263,15 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         "-",
     )
     # #########
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
+    # plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
     plt.ylim(0.75, 1.25)
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
+    ax = plt.gca()
+    ax.set_position(box)
     plt.show()
+
     # %%
     utils.savefig(fig, "icassp2023-dynamic-norm", format="pgf", pgf_font="serif")
 
@@ -306,6 +312,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.ylim(0, 1)
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
+    ax = plt.gca()
+    ax.set_position(box)
     plt.show()
     # %%
     utils.savefig(fig, "icassp2023-dynamic-norms", format="pgf", pgf_font="serif")

### 2022-10-15 simulations/dynamic.py
plots

@@ -269,6 +269,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
     ax = plt.gca()
+    ax.set_xticklabels([])
     ax.set_position(box)
     plt.show()
 
@@ -313,6 +314,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
     ax = plt.gca()
+    ax.set_xticklabels([])
     ax.set_position(box)
     plt.show()
     # %%

### 2022-10-15 simulations/dynamic.py
plots

@@ -315,7 +315,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.tight_layout(pad=0.5)
     ax = plt.gca()
     ax.set_xticklabels([])
-    ax.set_position(box)
+    ax.set_position(box.shrunk(1.0, 0.6))
     plt.show()
     # %%
     utils.savefig(fig, "icassp2023-dynamic-norms", format="pgf", pgf_font="serif")

### 2022-10-15 simulations/dynamic.py
plots

@@ -244,9 +244,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
+    relative_height = 0.6
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5 * relative_height))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
@@ -270,7 +271,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.tight_layout(pad=0.5)
     ax = plt.gca()
     ax.set_xticklabels([])
-    ax.set_position(box)
+    ax.set_position(box.shrunk(1.0, relative_height))
     plt.show()
 
     # %%
@@ -278,9 +279,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
+    relative_height = 1.0
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5 * relative_height))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")
@@ -315,7 +317,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.tight_layout(pad=0.5)
     ax = plt.gca()
     ax.set_xticklabels([])
-    ax.set_position(box.shrunk(1.0, 0.6))
+    ax.set_position(box.shrunk(1.0, relative_height))
     plt.show()
     # %%
     utils.savefig(fig, "icassp2023-dynamic-norms", format="pgf", pgf_font="serif")

### 2022-10-15 simulations/dynamic.py
plots

@@ -244,7 +244,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    relative_height = 0.6
+    relative_height = 0.75
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5 * relative_height))
@@ -279,7 +279,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    relative_height = 1.0
+    relative_height = 0.75
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5 * relative_height))

### 2022-10-15 simulations/dynamic.py
plots

@@ -247,7 +247,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     relative_height = 0.75
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5 * relative_height))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.3))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
@@ -268,7 +268,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(0.75, 1.25)
     plt.xlim(0, 15000)
-    plt.tight_layout(pad=0.5)
+    # plt.tight_layout(pad=0.5)
     ax = plt.gca()
     ax.set_xticklabels([])
     ax.set_position(box.shrunk(1.0, relative_height))
@@ -282,7 +282,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     relative_height = 0.75
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5 * relative_height))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.3))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")
@@ -314,7 +314,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(0, 1)
     plt.xlim(0, 15000)
-    plt.tight_layout(pad=0.5)
+    # plt.tight_layout(pad=0.5)
     ax = plt.gca()
     ax.set_xticklabels([])
     ax.set_position(box.shrunk(1.0, relative_height))

### 2022-10-15 simulations/dynamic.py
plots

@@ -244,10 +244,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    relative_height = 0.75
+    relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.3))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.25))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
@@ -279,10 +279,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    relative_height = 0.75
+    relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.3))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.25))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")

### 2022-10-15 simulations/dynamic.py
plots

@@ -192,6 +192,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
+    plt.close("all")
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
@@ -247,7 +248,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.25))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
@@ -282,7 +283,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.25))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")

### 2022-10-15 simulations/dynamic.py
plots

@@ -248,7 +248,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.35))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
@@ -283,7 +283,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.35))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")

### 2022-10-15 simulations/dynamic.py
plots

@@ -193,9 +193,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     # Plot
     plt.close("all")
-    mavg = 200
+    mavg = 10
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")
@@ -245,10 +245,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.35))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
@@ -272,7 +271,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # plt.tight_layout(pad=0.5)
     ax = plt.gca()
     ax.set_xticklabels([])
-    ax.set_position(box.shrunk(1.0, relative_height))
+    # ax.set_position(box.shrunk(1.0, relative_height))
+    ax.set_position(box)
     plt.show()
 
     # %%
@@ -280,10 +280,9 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    relative_height = 0.8
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.35))
+    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
     # plt.title("Title")
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\mathbf{h}_i\|$ [1]")
@@ -318,7 +317,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
[…]

### 2022-10-15 simulations/dynamic.py
plots

@@ -310,7 +310,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=r"$\|\mathbf{h}_2\|$",
     )
     # #########
-    plt.legend(ncol=3, prop={"size": 7}, columnspacing=0.5)
+    plt.legend(ncol=1, prop={"size": 7}, columnspacing=0.5)
     plt.grid()
     plt.ylim(0, 1)
     plt.xlim(0, 15000)

### 2022-10-17 simulations/static.py
static plots

@@ -209,16 +209,16 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     data = result.df.groupby(["alg", "gamma", "iters"])
 
     # %%
+    conv_frames = 500
     styles = ["-v", "-+", "-x", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
-    plt.xlabel(r"Mixing factor $\gamma$ [1]")
+    plt.xlabel(r"Mixing factor $\gamma_i$ [1]")
     plt.ylabel("Avg. NPM [dB]")
-
     plt.plot(
         cfg.variable_values[2]["gamma"],
         20
-        * np.log10(data.median().T.tail(200).mean()["opt", 1.0, 1])
+        * np.log10(data.median().T.tail(conv_frames).mean()["opt", 1.0, 1])
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
         label=f"optimal",
@@ -229,7 +229,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.plot(
         cfg.variable_values[2]["gamma"],
         20
-        * np.log10(data.median().T.tail(200).mean()["davgad", 1.0, 1])
+        * np.log10(data.median().T.tail(conv_frames).mean()["davgad", 1.0, 1])
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
         label=rf"adaptive $\gamma_i,\,K=1$",
@@ -239,7 +239,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
-        20 * np.log10(data.median().T.tail(200).mean()["davg", :, 1]),
+        20 * np.log10(data.median().T.tail(conv_frames).mean()["davg", :, 1]),
         styles.pop(),
         label=rf"fixed $\gamma_i,\,K=1$",
         markersize=4,
@@ -248,7 +248,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
-        20 * np.log10(data.median().T.tail(200).mean()["davg", :, 2]),
[…]

### 2022-10-17 paper.tex

@@
 
+% \begin{figure}[t]
+%     \centering
+%     \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
+%     \caption[]{}
+%     \label{fig:simulations:NPMtimedyn}
+% \end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}
+%     \caption[]{}
+%     \label{fig:simulations:normtime}
+% \end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}
+%     \caption[]{}
+%     \label{fig:simulations:normstime}
+% \end{figure}
+
 \begin{figure}[t]
     \centering
+    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}\\\vspace*{-1.0cm}
+    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}\\\vspace*{-1.0cm}
     \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
@@
     \label{fig:simulations:NPMtimedyn}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}
-    \caption[]{}
-    \label{fig:simulations:normtime}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}
-    \caption[]{}
-    \label{fig:simulations:normstime}
 \end{figure}

### 2022-10-17 simulations/static.py
static plots

@@ -209,9 +209,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     data = result.df.groupby(["alg", "gamma", "iters"])
 
     # %%
+    textwidth = 245
     conv_frames = 500
     styles = ["-v", "-+", "-x", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.5))
+    fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma_i$ [1]")
     plt.ylabel("Avg. NPM [dB]")
@@ -282,7 +283,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # Plot
     mavg = 200
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(400, 1.0, (1, 1), 0.5))
+    fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")

### 2022-10-17 simulations/dynamic.py
need to include optimal

@@ -64,7 +64,8 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
             [0.0, 0.5, 0.5],
         ]
     )
-    nw.setAveragingWeights(W)
+    if alg != "opt":
+        nw.setAveragingWeights(W)
 
     rho = 1.0
     stepsize = 0.5
@@ -112,7 +113,10 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
     npm_error = []
     h_test = np.zeros(shape=h.shape)
     nw.reset()
-    nw.setRho(rho, stepsize, eta, 1, iters, gamma)
+    if alg == "opt":
+        nw.setRho(rho, stepsize, eta, 1)
+    else:
+        nw.setRho(rho, stepsize, eta, 1, iters, gamma)
     for k_admm_fq in range(0, len(true_norms) * N_s - 2 * L, hopsize):
         nw.step(x_x[k_admm_fq : k_admm_fq + 2 * L, :])
         error = 0
@@ -142,7 +146,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         runs=30,
         seed=573438,
         variables=[
-            {"alg": ["davgad"], "SNR": [10], "gamma": [0.0], "iters": [1]},
+            {"alg": ["davgad", "opt"], "SNR": [10], "gamma": [0.0], "iters": [1]},
         ],
     )
     # %%
@@ -192,10 +196,11 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
+    textwidth = 245
     plt.close("all")
     mavg = 10
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1), 0.4))
+    fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.4))
     # plt.title("Title")
     plt.xlabel("Time [frames]")
     plt.ylabel("NPM [dB]")
@@ -236,10 +241,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.ylim(-30, 0)
     plt.xlim(0, 15000)
     plt.tight_layout(pad=0.5)
-    plt.show()
 
     ax = plt.gca()
     box = ax.get_position()
+    plt.show()
[…]

### 2022-10-18 simulations/dynamic.py
plot add comparison

@@ -8,8 +8,8 @@ import python_utils.utils as utils
 import python_utils.simulation as simulation
 
 # %%
-import matplotlib
-import matplotlib.pyplot as plt
+# import matplotlib
+# import matplotlib.pyplot as plt
 
 # %%
 import matplotlib
@@ -130,10 +130,13 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
                 np.linalg.norm(e1) / np.linalg.norm(h[(n * L) : (n + 1) * L])
             )
         npm_error.append(np.sqrt(error))
-    norms_t = np.asarray(nw.norms_t).squeeze()
-    data = np.concatenate(
-        [npm_error, nw.norm_t, norms_t[:, 0], norms_t[:, 1], norms_t[:, 2]]
-    )
+    if alg != "opt":
+        norms_t = np.asarray(nw.norms_t).squeeze()
+        data = np.concatenate(
+            [npm_error, nw.norm_t, norms_t[:, 0], norms_t[:, 1], norms_t[:, 2]]
+        )
+    else:
+        data = np.concatenate([npm_error, np.zeros((len(npm_error) * 4,))])
     # ################################################################
     ## %%
     return data
@@ -211,6 +214,30 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         colors=["k", "k"],
         linestyles=["dashed", "dashed"],
         linewidth=[0.75, 0.75],
+    )
+    (line,) = plt.plot(
+        20 * np.log10(data.median().T["opt", 0.0, 1][:frames]),
+        "k-",
+        label=rf"_optimal",
+        markersize=4,
+        markevery=(20, 500),
+        alpha=0.25,
+    )
+    plt.plot(
+        20
+        * np.log10(
+            np.convolve(
+                data.median().T["opt", 0.0, 1][:frames],
+                np.ones(mavg) / mavg,
+                mode="valid",
+            )
+        ),
+        "-",
+        label=rf"optimal",
+        markersize=4,
+        markevery=(20, 500),
+        color=line.get_color(),
+        markerfacecolor="none",
     )
     (line,) = plt.plot(
         20 * np.log10(data.median().T["davgad", 0.0, 1][:frames]),

### 2022-10-18 paper.tex

@@
 \begin{abstract}
-    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce communication cost and computational complexity or avoid reliance on a single device for processing.
+    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks as to reduce communication cost and computational complexity or avoid reliance on a single device for processing.
     In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the knowledge of a stacked network-wide solution vector at each node, the computation of which requires either broadcasting or relaying of node-specific values to all other nodes.
@@
 Distributed algorithms have been an active area of research for quite some time, with numerous control, optimization, and signal processing applications.
-With the ever-growing number of smart multimedia devices in today's surroundings providing ubiquitous processing and communication capabilities, distributed audio and speech signal processing also found their way into the spotlight.
-Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154} amongst others, have been proposed.
+With the ever-growing number of smart multimedia devices in today's surroundings providing ubiquitous processing and communication capabilities, distributed audio and speech signal processing have also found their way into the spotlight.
+Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154} to name a few, have been proposed.
 The task of distributed single-input-multiple-output (SIMO) blind system identification (BSI) had contributions such as the adaptive cross-relation-based (CR) \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
@@
 All of the mentioned distributed BSI algorithms rely on information shared between neighboring sensor nodes within the network.
-However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to e.g.
-\cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003}), which manifests itself as one or more global variables.
-In this case, a global variable is a variable, the computation of which requires information from all nodes within the network.
-To overcome the need for the network to be fully connected, \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} use an average consensus \cite{xiaoFastLinearIterations2004} approach where a secondary recursion estimates the global variable for each signal frame.
+However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to, e.g., \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003}), which manifests itself as one or more global variables.
+In this case, the computation of the global variable requries information from all the nodes within the network.
 The algorithm in \cite{blochbergerDBSI} relies on node-wise values being relayed throughout the network.
+In contrast, to overcome the need for the network to be fully connected, \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} use an average consensus \cite{xiaoFastLinearIterations2004} approach where a secondary recursion estimates the global variable for each signal frame.
 Both approaches introduce additional transmissions of variables between nodes, the number of which, depending on network and neighborhood size, can be substantial or even unfeasable.
 
-In this paper, we extend \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable with the introduction of a mixing factor to include instantaneous values into the averaging recursion.
-The mixing factor allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
+In this paper, we extend \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable.
+This approach allows us to compute the global variable without the need of a fully connected network or broadcasting.
+Further, we introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
 Simulation results show how the extension leads to BSI performance close to an optimal case where all information is available without the need of broadcasting variables to all nodes or a large number of estimation iterations.
@@
 \label{sec:dbsi}
-In this section, we will introduce certain parts of an adaptive SIMO BSI algorithm based on Online-ADMM \cite{blochbergerDBSI}, which are necessary for the reader to understand its extension of it.
+In this section, we briefly outline the adaptive SIMO BSI algorithm proposed in [8], setting the scene for the distributed averaging scheme proposed herein.
+% In this section, we will introduce certain parts of an adaptive SIMO BSI algorithm based on Online-ADMM \cite{blochbergerDBSI}, which are necessary for the reader to understand its extension of it.
 We refer the reader to the publication cited above for the full derivation of the algorithm.
@@
 \subsection[]{Sensor network}
-We assume a set \(\Mset \triangleq \{1,\ldots,M\}\) sensor nodes and a set of edges \(\mathcal{E}\) which connect the nodes forming a sensor network.
-Each edge is an unordered pair of nodes \(\{i,j\} \in \mathcal{E}\), which represents the communication link between them.
-From this follows the neighborhood of a node \(i\), i.e., the other nodes it is directly connected to, defined as \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\).
-It is to note, that we define the set with \(i \in \Nset_i\) for ease of notation later.
-This does however not represent an actual inter-node link.
-Furthermore, we can define the symmetric adjacency matrix \(\mtxb{C}\) with elements
+We assume a set \(\Mset \triangleq \{1,\ldots,M\}\) sensor nodes indices and a set of edge tuples \(\mathcal{E}\), which connect the nodes forming a sensor network.
+Each edge is an unordered pair of node indices \(\{i,j\} \in \mathcal{E}\), which represents the communication link between them.
+We allow \(\{i,i\} \in \mathcal{E}\), in order to simplify notation later, however, this does not represent a link but rather indicates the obvious fact that node \(i\) has information of itself.
+Furthermore, let \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\) denote the neighborhood of node \(i\),
+% From this follows the neighborhood of a node \(i\), i.e., the other nodes it is directly connected to, defined as \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\).
+% It is to note, that we define the set with \(i \in \Nset_i\) for ease of notation later.
+% This does however not represent an actual inter-node link.
+We can define the symmetric adjacency matrix \(\mtxb{C}\) with elements
 \begin{equation}
     C_{ij} = \begin{cases}
-        1 \quad \text{if } i = j\\
-        1 \quad \text{if } i \neq j \text{ and }\{i,j\} \in \mathcal{E}\\
+        1 \quad \text{if } \{i,j\} \in \mathcal{E}\\
         0 \quad \text{otherwise}.
@@
 \end{equation}
-It is to note that in \cite{blochbergerDBSI}, the pairs \(\{i,j\} \in \mathcal{E}\) are ordered, which yields a directed graph and leads to two sets of neighborhoods ("transmit" and "receive") and therefore a non-symmetric adjacency matrix.
+It may be noted that in \cite{blochbergerDBSI}, the pairs \(\{i,j\} \in \mathcal{E}\) are ordered, which yields a directed graph and leads to two sets of neighborhoods ("transmit" and "receive") and therefore a non-symmetric adjacency matrix.
 For the sake of brevity, we limit the explanations in this paper to the undirected case.
+The case of directed graphs can be extended directly from the presented results.
 
 \subsection[]{Signal model}
-We consider a SIMO system with input signal \(\mtxb{s}(n) = [s(n),\,\ldots,\,s(n-2L+2)]^{\T}\) and \(M\) output signals \(\x_i(n)= [x_i(n),\,\ldots,\,x_i(n-L+1)]^{\T}\).
+We consider a SIMO system with 
+\begin{align}
+    \mtxb{s}(n) &= [s(n),\,\ldots,\,s(n-2L+2)]^{\T},\\
+    \x_i(n) &= [x_i(n),\,\ldots,\,x_i(n-L+1)]^{\T}, \quad i \in \Mset,
+\end{align}
+the input signal frame and \(M\) output signal frames, respectively.
 Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated with \(\mtxb{s}(n)\).
@@
 \subsection[]{Distributed BSI with Online-ADMM}
-In BSI, the coss-relation problem formulation only uses output signals \(\x_i(n)\), exploiting relative information between them, to identify the system, i.e., the acoustic or communication channels \(\h_t = [\h_1^\T,\,...,\,\h_M^\T]^\T\) (subscript \(t\) indicates \emph{true} system as opposed to an estimate).
+In BSI, the coss-relation problem formulation only uses output signals \(\x_i(n)\), exploiting relative information between them, to identify the system, i.e., the acoustic or communication channels \(\h = [\h_1^\T,\,...,\,\h_M^\T]^\T\).
 The solution to this problem is found by the minimization problem (cf.
@@
     \begin{aligned}
-        \h = \arg \min_{\h} \quad &\h^\herm \R \h \\
-        \text{s.t. } \quad &\h^\herm \h = 1.
+        \arg \min_{\h} \quad &\h^\herm \R \h \\
+        \text{s.t. } \quad &\|\h\| = 1.
     \end{aligned}\label{eq:frequency_domain:min_prob}
 \end{equation}
-Separating the cost function and applying general-form consensus ADMM as an adaptive algorithm leads to the update steps
-\begin{align}
-    \w_i^{m+1} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^m,\uu^m)\label{eq:general_consensus_admm:local}\\
-    \h^{m+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{m+1},\h,\uu^m)\label{eq:general_consensus_admm:global}\\
-    \uu_i^{m+1} &= \uu_i^{m} + \rho \left( \w_i^{m+1} - \tilde{\h}_i^{m+1} \right),\label{eq:general_consensus_admm:dual}
-\end{align}
-where \(\w_i\) represents channels estimates of lower dimensional subproblems, solved locally by node \(i\), \(\h = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) the consensus variable (estimate of the system), and \(\uu_i\) are the dual variables.
+% Separating the cost function and applying general-form consensus ADMM as an adaptive algorithm leads to the update steps
+% \begin{align}
+%     \w_i^{n+1} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^n,\uu^n)\label{eq:general_consensus_admm:local}\\
+%     \h^{n+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{n+1},\h,\uu^n)\label{eq:general_consensus_admm:global}\\
+%     \uu_i^{n+1} &= \uu_i^{n} + \rho \left( \w_i^{n+1} - \tilde{\h}_i^{n+1} \right),\label{eq:general_consensus_admm:dual}
+% \end{align}
+% where \(\w_i\) represents channels estimates of lower dimensional subproblems, solved locally by node \(i\), \(\h = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) the consensus variable (estimate of the system), and \(\uu_i\) are the dual variables.
+\begin{todo}
+    find a good way to introduce equation of interest without having to explain all the local, dual variables and parameter mapping in detail.
+    \(\h\) notation is confusing.
+\end{todo}
 The updates of \(\hat{\h}_i\) are of interest for this extension.
@@
 \begin{equation}
-    \hat{\h_i}^{m+1} = \frac{\bar{\h}_i^{m+1}}{\|\h^{m+1}\|}\label{eq:online_admm:consensus_update}
+    \hat{\h_i}^{n+1} = \frac{\bar{\h}_i^{n+1}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{n+1}\|^2}}.\label{eq:online_admm:consensus_update}
 \end{equation}
-for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{m+1}\), a combination of neigborhood averages of \(\w_j\) and \(\uu_j\), \(j \in \Nset_i\).
-The denominator of \eqref{eq:online_admm:consensus_update}, \(\|\h\|\), is the stacked vector of the full system. This vector, however, is not available at any of the nodes in the network.
-In \cite{blochbergerDBSI}, we assume that partial squared norms of \(\|\h\|^2 = \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) are relayed throughout the network until all nodes have the information necessary.
-In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}, a similar global value is estimated by a distributed averaging approach, iteratively combining values within neighborhoods until convergence to a network-wide average.
+% for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{n+1}\), a combination of neigborhood averages of \(\w_j\) and \(\uu_j\), \(j \in \Nset_i\).
+The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires  \(\|\bar{\h}_j^{n+1}\|\) from all nodes \(j \in \Mset\), which however, is not possible without a fully-connected network or broadcasting.
+In \cite{blochbergerDBSI}, we assume that partial squared norms are relayed throughout the network until all nodes have the information necessary.
+In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}, a global value is estimated by a distributed averaging approach, iteratively combining values within neighborhoods until convergence to a network-wide average.
 
@@
 
-\section{FDLA-based adaptive norm estimation}
+\section{Adaptive norm estimation}
 \label{sec:adaptivenormest}
@@
 \subsection[]{Distributed averaging}
-The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\hat{\h_i}\|^2\) at each node \(i \in \Mset\).
-To avoid the large number of transmission, which would be necessary to facilitate this, we will approximate the separable squared norm \(\hat{\phi}_i \approx \|\h\|^2= \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
+The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i\|^2\) at each node \(i \in \Mset\).
+To avoid the large number of transmission, which would be necessary to facilitate this, we will approximate the squared norm \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
 
-The FDLA problem, as introduced in \cite{xiaoFastLinearIterations2004}, looks to find optimal weights for distributed linear combinations of the form
+We look at distributed linear combinations with the iteration index \(k=0,...,K\),
 \begin{equation}
@@
 \end{equation}
-which can be written in vector form as \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\), a vector, which initially, at \(k=1\), contains a set of variables, an average of which should be computed.
-To find the optimal weights, the minimization problem
+which can be written in vector form as \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\).
+We want to find the matrix \(\mtxb{W}\), which ensure that for any initial value \(\bm{\phi}({0})\), each element of \(\bm{\phi}({k})\) converges to the average of the elements of \(\bm{\phi}({0})\) when \(k \to \infty\).
+In this application, the elements of \(\bm{\phi}(0)\) are the initial node-wise squared norm values \(\|\bar{\h}_i\|^2\) which then leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) for all \(i \in \Mset\).
+This is achieved by solving the fastest distributed linear averaging (FDLA) problem, introduced in \cite{xiaoFastLinearIterations2004}, in the form of
 \begin{equation}
@@
         \min& \quad \| \W - \bm{1}\bm{1}^\T/M\|_2\\
-        \text{s.t.}& \quad \W \in \mathcal{C},\, \bm{1}^\T \W = \bm{1}^\T,\, \W \bm{1}= \bm{1}
+        \text{s.t.}& \quad \W \in \mathcal{C},\, \bm{1}^\T \W = \bm{1}^\T,\, \W \bm{1}= \bm{1}.
     \end{aligned}\label{eq:adaptivenormest:fdlaminprob}
 \end{equation}
-is solved.
-The set \(\mathcal{C} = \{\W \in \mathbb{R}^{M \times M} \vert W_{ij} = 0 \text{ if } \{i,j\} \notin \mathcal{E}\}\) describes all matrices with the same sparsity pattern as the adjacency matrix \(\mtxb{C}\).
-Now, the \(i\)-th row of the optimal \(\W\) contains the neigborhood weights for node \(i\) as non-zero entries.
+Here, the set \(\mathcal{C} = \{\W \in \mathbb{R}^{M \times M} \vert W_{ij} = 0 \text{ if } \{i,j\} \notin \mathcal{E}\}\) describes all matrices with the same sparsity pattern as the adjacency matrix \(\mtxb{C}\).
+Now, the \(i\)-th row of \(\W\) contains the neigborhood weights for node \(i\) as non-zero entries.
 % \begin{todo}
@@
 Each iteration requires information exchange within neighborhoods, adding to the communication cost of the algorithm.
-We split iterations over frames to keep \(K\) as low as possible.
-For this, we further introduce an instantaneous weighted neighborhood average of node-wise squared norm values \(\bar{\phi}_i^{m} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^m\|^2\) which is then combined with the iterative average into
+In order to mitigate this, we split iterations over frames \(n\) to keep \(K\) as low as possible.
+However, as each frame introduces new data, we need to include this data into the recursion.
+To this end, we further introduce an instantaneous weighted neighborhood average of node-wise squared norm values \(\bar{\phi}_i^{n} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^n\|^2\) which is then combined with the iterative average into
 \begin{equation}
-    \hat{\phi}_i^{m+1} = \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m}(K)
+    \hat{\phi}_i^{n+1} = \gamma_i \bar{\phi}_i^{n} + (1-\gamma_i) \phi_i^{n}(K)
 \end{equation}
 where \(\gamma_i\) is a mixing factor.
-The factor balances instantaneous values and the distributed averaging iterations.
-This facilitates introduction of new information and the convergence of the distributed averaging, respectively.
+With the right choice of mixing factor \(\gamma_i\), this leads to a reduction of distributed averaging iterations \(K\) (see \autoref{sec:simulations}) and improves behaviour of the algorithm when the norms \(\|\h_i\|\) are time-variant.
 % The factor balances instantaneous values and the distributed averaging iterations, and we shoudl look at the two extreme cases for further insight.
-% For \(\gamma_i = 0\), only instantaneous neighborhood averages are used, which effectively leads to suboptimal computation, as \(\hat{\phi}_1^{m} = \hat{\phi}_2^{m} = \ldots = \hat{\phi}_M^{m}\) for large enough \(m\) will never be reached.
+% For \(\gamma_i = 0\), only instantaneous neighborhood averages are used, which effectively leads to suboptimal computation, as \(\hat{\phi}_1^{n} = \hat{\phi}_2^{n} = \ldots = \hat{\phi}_M^{n}\) for large enough \(m\) will never be reached.
 % For \(\gamma_i=1\), only the distributed averaging iterations are considered, i.e., we effectively combine the per-frame secondary recursion \eqref{eq:adaptivenormest:distlincomb} from \(K\) to \(mK\) iterations.
@@
 \subsection[]{Adaptive mixing factor}
-To avoid choosing a fixed value for \(\gamma_i\), we track stationarity of the instantaneous \(\bar{\phi}_i^{m}\).
-If the absolute difference between subsequent frames \(| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |\) nears 0, then this means that the estimation of \(\w_i, \bar{\h}_i\) is converging to a steady state.
+To avoid choosing a fixed value for \(\gamma_i\), we use information provided by \(\bar{\phi}_i^{n}\).
+If the absolute difference between subsequent frames \(| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |\) nears 0, then this means that the estimation of \(\bar{\h}_i\) is converging to a steady state.
 Is this the case, then the emphasis of the algorithm should lie on norm estimation, i.e. the distributed averaging recursion, which in turn means \(\gamma_i\) should go towards 0 as well.
-We set \(\gamma_i^{m}\) proportional to the absolute difference between subsequent frames and set an upper limit at 1,
+We set \(\gamma_i^{n}\) proportional to the absolute difference between subsequent frames and set an upper limit at 1,
 \begin{equation}
-    \gamma_i^{m} = \min \left\lbrace \frac{| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |}{\bar{\phi}_i^{m-1}},\,1\right\rbrace.\label{eq:adaptivenormest:adaptivegamma}
+    \gamma_i^{n} = \min \left\lbrace \frac{| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |}{\bar{\phi}_i^{n-1}},\,1\right\rbrace.\label{eq:adaptivenormest:adaptivegamma}
 \end{equation}
@@
     \(\bar{\phi}_i^{0} \gets 1, \forall i \in \Mset\)\;
-    \For(){\(m=1\dots\)}
+    \For(){\(n=1\dots\)}
     {
@@
             % \(\cdots\)\\
-            % \(\w_i^m \gets \operatorname{argmin}_{\w_i}\, \mathcal{L}_{\rho} (\w,\h^m,\uu^m)\)\;
-            % Compute \(\bar{\h}_i^{m}\)\;
+            % \(\w_i^n \gets \operatorname{argmin}_{\w_i}\, \mathcal{L}_{\rho} (\w,\h^n,\uu^n)\)\;
+            % Compute \(\bar{\h}_i^{n}\)\;
             % \(\cdots\)\\
@@
             \dotfill\\
-            Transmit \(\bar{\h}_i^{m}\) to nodes  \(j \in \Nset_i\)\;
-            \(\bar{\phi}_i^{m} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^m\|^2\)\;
-            \(\gamma_i^{m} \gets \min \left\lbrace \frac{| \bar{\phi}_i^{m} - \bar{\phi}_i^{m-1} |}{\bar{\phi}_i^{m-1}},\,1\right\rbrace\)\;
+            Transmit \(\bar{\h}_i^{n}\) to nodes  \(j \in \Nset_i\)\;
+            \(\bar{\phi}_i^{n} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^n\|^2\)\;
+            \(\gamma_i^{n} \gets \min \left\lbrace \frac{| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |}{\bar{\phi}_i^{n-1}},\,1\right\rbrace\)\;
             \eIf(){\(m = 1\)}
             {
-                \(\phi_i^{m}(1) \gets \|\bar{\h}_i^m\|^2\)\;
+                \(\phi_i^{n}(1) \gets \|\bar{\h}_i^n\|^2\)\;
             }
             {
-                \(\phi_i^{m}(1) \gets \hat{\phi}_i^{m-1}(K)\)\;
+                \(\phi_i^{n}(1) \gets \hat{\phi}_i^{n-1}(K)\)\;
             }
@@
             }
-            \(\hat{\phi}_i^{m} \gets \gamma_i \bar{\phi}_i^{m} + (1-\gamma) \phi_i^{m}(K)\)\;
-            \(\hat{\h_i}^{m} \gets \frac{\bar{\h}_i^{m}}{\sqrt{\hat{\phi}_i^{m}M}}\)\;
+            \(\hat{\phi}_i^{n} \gets \gamma_i \bar{\phi}_i^{n} + (1-\gamma) \phi_i^{n}(K)\)\;
+            \(\hat{\h_i}^{n} \gets \frac{\bar{\h}_i^{n}}{\sqrt{\hat{\phi}_i^{n}M}}\)\;
             \dotfill\\
@@
             % \(\cdots\)\\
-            % \(\uu_i^{m} \gets \uu_i^{m-1} + \rho \left( \w_i^{m} - \tilde{\h}_i^{m} \right)\)\;
+            % \(\uu_i^{n} \gets \uu_i^{n-1} + \rho \left( \w_i^{n} - \tilde{\h}_i^{n} \right)\)\;
             % \(\cdots\)\\
@@
 \label{sec:transcost}
+% \begin{table}[t]
+%     \centering
+%     \begin{tabular}{ |l|l|l| } 
+%         \hline
+%         & Transmit & Receive \\
+%         \hline\hline
+%         (1) Full & \(\mathcal{O}(M-1)\) & \(\mathcal{O}(M-1)\) \\
+%         \hline
+%         (2) Broadcast & \(\mathcal{O}(1)\) & \(\mathcal{O}(M-1)\) \\ 
+%         \hline
+%         (3) Neigborhood & \(\mathcal{O}(\bar{N}_i K)\) & \(\mathcal{O}(\bar{N}_i K)\) \\ 
+%         \hline
+%     \end{tabular}
+%     \caption[]{Comparison of communication cost.}
+%     \label{tab:transcost:table}
+% \end{table}
+\renewcommand{\arraystretch}{1.2}
 \begin{table}[t]
@@
         \hline\hline
-        (1) Full & \(\mathcal{O}(M-1)\) & \(\mathcal{O}(M-1)\) \\
+        (1) Fully connected & \(\mathcal{O}(M^2)\) & \(\mathcal{O}(M^2)\) \\
         \hline
-        (2) Broadcast & \(\mathcal{O}(1)\) & \(\mathcal{O}(M-1)\) \\ 
+        (2) Broadcast & \(\mathcal{O}(M)\) & \(\mathcal{O}(M^2)\) \\ 
         \hline
-        (3) Neigborhood & \(\mathcal{O}(\bar{N}_i K)\) & \(\mathcal{O}(\bar{N}_i K)\) \\ 
+        (3) Neigborhood & \(\mathcal{O}(M \bar{N}_i K)\) & \(\mathcal{O}(M \bar{N}_i K)\) \\ 
         \hline
@@
 \end{table}
+\renewcommand{\arraystretch}{1.0}
 To describe the communication cost within the network, we adopt the Big-\(\mathcal{O}\) notation, similar to the complexity analysis of algorithms.
-We consider the communication of a variable from one node to another as \(\mathcal{O}(1)+\mathcal{O}(1)\), where the two terms represent transmit and receive operations, respectively, as both require computational resources at a node.
+We consider the communication of a variable from one node to another as \(\mathcal{O}(1)\).
 The most useful measure in the case of this work is to analyze the cost per node.
@@
 The adaptive method yields results very close to the optimal method.
-A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).}
+A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).
+Hatched area indicates frames used in computations for \autoref{fig:simulations:avgNPMgamma}.}
     \label{fig:simulations:NPMtime}
@@
     \caption[]{Mean over time of median NPM of 30 randomized runs after convergence for varied values for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
-Results for optimal method, and adaptive \(\gamma_i\) included for comparison.}
+Results for optimal method, and adaptive \(\gamma_i\) included for comparison.
+Hatched area in \autoref{fig:simulations:NPMtime} indicates frames used for computation of avg.
+NPM.}
     \label{fig:simulations:avgNPMgamma}
@@
 The simulation setup is a network with \(M=5\) nodes arranged in a ring topology, each node having \(|N_i|=2\) neighbors.
-The input signal is zero-mean white Gaussian noise (WGN), the impulse responses of length \(L=16\) are zero-mean WGN as well, and at each channel, independent WGN is added with \(\text{SNR}=10\,\text{dB}\).
-The norms of the impulse responses are scaled to random values from the uniform distribution \(\mathcal{U}_{[0.5,2.0]}\).
+The input signal is zero-mean white Gaussian noise (WGN), the impulse responses of length \(L=16\) are drawn from a normal distribution, and at each channel, independent WGN is added with \(\text{SNR}=10\,\text{dB}\).
+The norms of the impulse responses are scaled to random values drawn from the uniform distribution \(\mathcal{U}_{[0.5,2.0]}\).
 A comparison is made between the following cases:

### 2022-10-18 simulations/dynamic.py
plots

@@ -328,9 +328,10 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.plot(
         [0, 5000, 5000, 10000, 10000, 15000],
         np.repeat(true_normed_norms, 2, axis=0),
-        "k-.",
-        linewidth=0.75,
+        "-.",
+        linewidth=1.0,
         label=["true", "_true", "_true"],
+        color="tab:gray"
     )
     # plt.vlines(
     #     [5000, 10000],

### 2022-10-18 simulations/dynamic.py
plots

@@ -325,14 +325,6 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # plt.xlabel("Time [frames]")
     plt.ylabel(r"$\|\hat{\mathbf{h}}_i\|$ [1]")
     # for n in range(true_normed_norms.shape[0]):
-    plt.plot(
-        [0, 5000, 5000, 10000, 10000, 15000],
-        np.repeat(true_normed_norms, 2, axis=0),
-        "-.",
-        linewidth=1.0,
-        label=["true", "_true", "_true"],
-        color="tab:gray"
-    )
     # plt.vlines(
     #     [5000, 10000],
     #     0,
@@ -356,7 +348,14 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         "-",
         label=r"$\|\hat{\mathbf{h}}_3\|$",
     )
-
+    plt.plot(
+        [0, 5000, 5000, 10000, 10000, 15000],
+        np.repeat(true_normed_norms, 2, axis=0),
+        "-.",
+        linewidth=1.0,
+        label=["true", "_true", "_true"],
+        color="tab:gray",
+    )
     # #########
     plt.legend(ncol=1, prop={"size": 7}, columnspacing=0.5)
     plt.grid()

### 2022-10-18 simulations/dynamic.py
plots

@@ -354,7 +354,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         "-.",
         linewidth=1.0,
         label=["true", "_true", "_true"],
-        color="tab:gray",
+        color="k",
     )
     # #########
     plt.legend(ncol=1, prop={"size": 7}, columnspacing=0.5)

### 2022-10-18 simulations/dynamic.py
plots

@@ -292,7 +292,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         linewidth=[0.75, 0.75],
     )
     (line,) = plt.plot(
-        data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy(),
+        np.sqrt(data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy()),
         "-",
     )
     # #########
@@ -334,23 +334,23 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     #     linewidth=[0.75, 0.75],
     # )
     (line,) = plt.plot(
-        data.mean().T["davgad", 0.0, 1][2 * frames : 3 * frames].to_numpy(),
+        np.sqrt(data.mean().T["davgad", 0.0, 1][2 * frames : 3 * frames].to_numpy()),
         "-",
         label=r"$\|\hat{\mathbf{h}}_1\|$",
     )
     (line,) = plt.plot(
-        data.mean().T["davgad", 0.0, 1][3 * frames : 4 * frames].to_numpy(),
+        np.sqrt(data.mean().T["davgad", 0.0, 1][3 * frames : 4 * frames].to_numpy()),
         "-",
         label=r"$\|\hat{\mathbf{h}}_2\|$",
     )
     (line,) = plt.plot(
-        data.mean().T["davgad", 0.0, 1][4 * frames : 5 * frames].to_numpy(),
+        np.sqrt(data.mean().T["davgad", 0.0, 1][4 * frames : 5 * frames].to_numpy()),
         "-",
         label=r"$\|\hat{\mathbf{h}}_3\|$",
     )
     plt.plot(
         [0, 5000, 5000, 10000, 10000, 15000],
-        np.repeat(true_normed_norms, 2, axis=0),
+        np.repeat(np.sqrt(true_normed_norms), 2, axis=0),
         "-.",
         linewidth=1.0,
         label=["true", "_true", "_true"],

### 2022-10-18 paper.tex
version for Toon,Randy

@@
 % ---------------
-\name{Matthias Blochberger\(^1\), Filip Elvander\(^2\), Toon, ...\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+\name{Matthias Blochberger\(^1\), Filip Elvander\(^2\), Randall Ali\(^1\), Toon van Waterschoot\(^1\),tbd\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
 This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
-This research received funding in part from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
-This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.}}
-\address{\(^1\)KU Leuven, Dept. of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept. of Signal Processing and Acoustics, 02150 Espoo, Finland}
+This research received funding in part from the Research Foundation - Flanders (FWO) grant 12ZD622N as well as from the European Union's Horizon 2020 research and innovation program / ERC Consolidator Grant: SONORA (No.\,773268).
+This paper reflects only the authors' views and the Union is not liable for any use that may be made of the contained information.
+Source code available at \textcolor{red}{ADD URL}}}
+\address{\(^1\)KU Leuven, Dept. of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept. of Signal Processing and Acoustics, 02150 Espoo, Finland\\tbd}
 
@@
     \begin{aligned}
-        \arg \min_{\h} \quad &\h^\herm \R \h \\
+        \hat{\h} = \arg \min_{\h} \quad &\h^\herm \R \h \\
         \text{s.t. } \quad &\|\h\| = 1.
@@
 \end{equation}
+where the estimate is \(\hat{\h} = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\).
+In \cite{blochbergerDBSI}, this problem is solved by a distributed adaptive algorithm that is based on separating the problem \eqref{eq:frequency_domain:min_prob} into node-wise subproblems of analogous form, whoever only using a subset channels, provided by neighboring nodes \(\Nset_i \subset \Mset\).
+General-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} is applied in an adaptive updating scheme (Online-ADMM) \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
+This leads to update steps for local, consensus, and dual variables (we refer the reader to \cite{blochbergerDBSI} for details).
+The consensus variable in the algorithm is the estimate of the system \(\hat{\h}\).
+In the distributed algorithm, each of its subvectors \(\hat{\h}_i\) is computed at the respective node \(i\).
+The update step for \(\hat{\h}_i\) is of interest for this extension.
 % Separating the cost function and applying general-form consensus ADMM as an adaptive algorithm leads to the update steps
@@
 \begin{todo}
-    find a good way to introduce equation of interest without having to explain all the local, dual variables and parameter mapping in detail.
-    \(\h\) notation is confusing.
+    Is this enough?
+I fear i have to use a full page introducing all the local, consensus, dual variables, parameter mapping and the lagrangian etc.
+only to get to \eqref{eq:online_admm:consensus_update} and say that the denominator is what we are looking at...
 \end{todo}
-The updates of \(\hat{\h}_i\) are of interest for this extension.
-It is defined \cite{blochbergerDBSI} as
+It is defined as
 \begin{equation}
@@
 The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i\|^2\) at each node \(i \in \Mset\).
-To avoid the large number of transmission, which would be necessary to facilitate this, we will approximate the squared norm \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
+To avoid the large number of transmissions, which would be necessary to facilitate this, we will approximate the squared norm \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
 
@@
 % In usual applications of the iteration \eqref{eq:adaptivenormest:distlincomb}, it is applied \(K \in \mathbb{N}\) times until convergence of the averages is reached.
-In an adaptive algorithm, where the resulting variable is required at each time frame \(m\) such as e.g.
+In an adaptive algorithm, where the resulting variable is required at each time frame \(n\) such as e.g.
 \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} and \cite{blochbergerDBSI}, it introduces \(K\) secondary iterations per frame.
@@
 where \(\gamma_i\) is a mixing factor.
-With the right choice of mixing factor \(\gamma_i\), this leads to a reduction of distributed averaging iterations \(K\) (see \autoref{sec:simulations}) and improves behaviour of the algorithm when the norms \(\|\h_i\|\) are time-variant.
+With the right choice of mixing factor \(\gamma_i\), this leads to a reduction of distributed averaging iterations \(K\) and improves behaviour of the algorithm when the norms \(\|\h_i\|\) are time-variant (see \autoref{sec:simulations}).
 % The factor balances instantaneous values and the distributed averaging iterations, and we shoudl look at the two extreme cases for further insight.
-% For \(\gamma_i = 0\), only instantaneous neighborhood averages are used, which effectively leads to suboptimal computation, as \(\hat{\phi}_1^{n} = \hat{\phi}_2^{n} = \ldots = \hat{\phi}_M^{n}\) for large enough \(m\) will never be reached.
+% For \(\gamma_i = 0\), only instantaneous neighborhood averages are used, which effectively leads to suboptimal computation, as \(\hat{\phi}_1^{n} = \hat{\phi}_2^{n} = \ldots = \hat{\phi}_M^{n}\) for large enough \(n\) will never be reached.
 % For \(\gamma_i=1\), only the distributed averaging iterations are considered, i.e., we effectively combine the per-frame secondary recursion \eqref{eq:adaptivenormest:distlincomb} from \(K\) to \(mK\) iterations.
@@
 \end{equation}
-The combination of instantaneous values and distributed averaging estimate should lead to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed should increase as well.
-\autoref{alg:davg_norm_est} summarizes the procedure as is is introduced in this section.
+The initial value for \(\bar{\phi}_i^{n-1}\) for \(n=0\) can be set to an arbitrary real number, in our case 1.
+% The combination of instantaneous values and distributed averaging estimate should lead to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed should increase as well.
+Refer to \autoref{alg:davg_norm_est} for the extended algorithm introduced in this section.
 
 \begin{algorithm}[t]
-    \caption{ADMM BSI with FDLA-based adaptive estimation of norm values}\label{alg:davg_norm_est}
+    \caption{ADMM BSI with distributed-averaging-based adaptive estimation of norm values}\label{alg:davg_norm_est}
     \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
-    \(\bar{\phi}_i^{0} \gets 1, \forall i \in \Mset\)\;
-    \For(){\(n=1\dots\)}
+    \(\bar{\phi}_i^{n-1} \gets 1, \forall i \in \Mset\)\;
+    \For(){\(n=0\dots\)}
     {
@@
             \(\gamma_i^{n} \gets \min \left\lbrace \frac{| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |}{\bar{\phi}_i^{n-1}},\,1\right\rbrace\)\;
-            \eIf(){\(m = 1\)}
+            \eIf(){\(m = 0\)}
             {
@@
             }
-            \For(){\(k=1,\dots,K\)}
+            \For(){\(k=0,\dots,K\)}
             {
-                Transmit \(\phi_i(k)\) to nodes  \(j \in \Nset_i\)\;
-                \(\phi_i({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j({k})\)\;
+                Transmit \(\phi_i^n(k)\) to nodes  \(j \in \Nset_i\)\;
+                \(\phi_i^n({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j^n({k})\)\;
             }
@@
 \label{sec:transcost}
+% \renewcommand{\arraystretch}{1.2}
 % \begin{table}[t]
 %     \centering
-%     \begin{tabular}{ |l|l|l| } 
+%     \begin{tabular}{ |l|l| } 
 %         \hline
-%         & Transmit & Receive \\
+%         & Cost \\
 %         \hline\hline
-%         (1) Full & \(\mathcal{O}(M-1)\) & \(\mathcal{O}(M-1)\) \\
+%         (1) Fully connected & \(\mathcal{O}(M)\) \\
 %         \hline
-%         (2) Broadcast & \(\mathcal{O}(1)\) & \(\mathcal{O}(M-1)\) \\ 
+%         (2) Broadcast & \(\mathcal{O}(M)\) \\ 
 %         \hline
-%         (3) Neigborhood & \(\mathcal{O}(\bar{N}_i K)\) & \(\mathcal{O}(\bar{N}_i K)\) \\ 
+%         (3) Neighborhood & \(\mathcal{O}(\bar{N}_i K)\) \\ 
 %         \hline
@@
 % \end{table}
+% \renewcommand{\arraystretch}{1.0}
 \renewcommand{\arraystretch}{1.2}
@@
     \centering
-    \begin{tabular}{ |l|l|l| }
+    \begin{tabular}{ |l|l|l|l| }
         \hline
-        & Transmit & Receive \\
+        & Trans. Ops. & Rec. Ops. & Local Compl. \\
         \hline\hline
-        (1) Fully connected & \(\mathcal{O}(M^2)\) & \(\mathcal{O}(M^2)\) \\
+        (1) Fully connected & \(M-1\) & \(M-1\) & \(\mathcal{O}(M^2 L^2)\) \\
         \hline
-        (2) Broadcast & \(\mathcal{O}(M)\) & \(\mathcal{O}(M^2)\) \\ 
+        (2) Broadcast & \(1\) & \(M-1\) & \(\mathcal{O}(N_i^2 L^2)\)  \\ 
         \hline
-        (3) Neigborhood & \(\mathcal{O}(M \bar{N}_i K)\) & \(\mathcal{O}(M \bar{N}_i K)\) \\ 
+        (3) Neighborhood & \(N_i K\) & \(N_i K\) & \(\mathcal{O}(N_i^2 L^2)\)\\ 
         \hline
     \end{tabular}
-    \caption[]{Comparison of communication cost.}
+    % \caption[]{Comparison of communication cost (transmission operations \& receive operations) and local problem complexity for a node \(i\) within the network.
+\(M\) is the number of nodes within the network, \(N_i\) is the number neighboring nodes, \(L\) is the lenght of channel responses, \(K\) is the number of distributed averaging iterations.}
+    \caption[]{Comparison of communication cost (transmission operations \& receive operations) and local problem complexity for a node \(i\) within the network.}
     \label{tab:transcost:table}
@@
 \renewcommand{\arraystretch}{1.0}
-To describe the communication cost within the network, we adopt the Big-\(\mathcal{O}\) notation, similar to the complexity analysis of algorithms.
-We consider the communication of a variable from one node to another as \(\mathcal{O}(1)\).
+To describe the communication cost within the network, we count the number of variables transmitted per time frame \(n\).
 The most useful measure in the case of this work is to analyze the cost per node.
-For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
-We compare the following communication schemes:
+% For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
+We compare the following communication schemes within the context of the algorithm \cite{blochbergerDBSI} this paper proposes the extension to:
 \begin{itemize}
     \itemsep-0.2em
-    \item[(1)] A fully connected network, i.e., all nodes are linked with all other nodes by direct links, \(\Nset_i = \Mset\).
-    \item[(2)] The nodes employ broadcasting, i.e., the nodes transmit to all other nodes without direct links.
-    \item[(3)] The nodes only communicate with neighboring nodes, \(\Nset_i \subset \Mset\).
+    \item[(1)] A fully connected network, where node \(i\) communicates \(\|\bar{\h}_i\|\) to all other nodes \(\{j \in \Nset_i = \Mset \setminus i\}\) directly, i.e., the neighborhood is the full network.
+    \item[(2)] The node \(i\) broadcasts \(\|\bar{\h}_i\|\), i.e., it transmit to all other nodes \(\{j \in \Mset \setminus i\}\) without direct links.
+    \item[(3)] The node \(i\) communicates \(\|\bar{\h}_i\|\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset \setminus i\}\) and applies \(K\) distributed averaging iterations.
 \end{itemize}
-For (1), the cost increases quadratically with increasing network size \(M\), both in transmit and receive operations, whereas for (2), the quadratic increase happens only at the latter.
-Using communication scheme (3), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed in this paper, cost in proportional to neighborhood size and iteration count \(K\).
-Refer to \autoref{tab:transcost:table} for the collected orders of communication cost.
-
+In this comparison, we only consider communication necessary for the computation of \eqref{eq:online_admm:consensus_update} as the rest of the algorithm is the same for our options.
+For (1) and (2), the cost per node increases linearly with network size \(M\), whereas for communication scheme (3), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only.
+The problem to be solved at each node \(i \in \Mset\) has complexity \(\mathcal{O}(M^2 L^2)\) for (1), with channel response length \(L\) (which means there is no reduction compared to a centralized approach).
+For (2) and (3), local complexity is \(\mathcal{O}(N_i^2 L^2)\), where \(N_i\) is the neighborhood size.
+Refer to \autoref{tab:transcost:table} for a direct comparison.
+% To describe the communication cost within the network, we adopt the Big-\(\mathcal{O}\) notation, similar to the complexity analysis of algorithms.
+% We consider the communication of a variable from one node to another as \(\mathcal{O}(1)\).
+% The most useful measure in the case of this work is to analyze the cost per node.
+% For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
+% We compare the following communication schemes:
+% \begin{itemize}
+%     \itemsep-0.2em
+%     \item[(1)] A fully connected network, i.e., all nodes are linked with all other nodes by direct links, \(\Nset_i = \Mset\).
+%     \item[(2)] The nodes employ broadcasting, i.e., the nodes transmit to all other nodes without direct links.
+%     \item[(3)] The nodes only communicate with neighboring nodes, \(\Nset_i \subset \Mset\).
+% \end{itemize}
+% For (1) and (2), the cost per node increases linearly with network size \(M\): \(\mathcal{O}(M)\).
+% Using communication scheme (3), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed as an extension to \cite{blochbergerDBSI} in this paper, cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only: \(\mathcal{O}(\bar{N}_i K)\).
+% \begin{todo}
+%     Unsure, about this.
+Filips feedback: "Don't you want the complexity for the whole system here so that you can compare things?
+That us write the complexity for the fully connected system as well as the distributed systems, parametrized in such away that the reader can compare the two.
+Here, the reader sees \(M\) and \(\bar{N}_i,K\) and has no idea of how they relate to each other."\\
+%     But this shows how the communication cost as defined here goes from \(\mathcal{O}(M)\) to \(\mathcal{O}(\bar{N}_i K)\).\\
+%     Other option: not just communication cost: fully connected \(\mathcal{O}(M^2 L^2)\), broadcast \(\)
+% \end{todo}
+% Refer to \autoref{tab:transcost:table} for the collected orders of communication cost.
 % \begin{figure}[t]
@@
 
-\subsection[]{Simulation}
+\subsection[]{Simulations}
 \begin{figure}[t]
@@
     \input{simulations/plots/icassp2023-static-time/icassp2023-static-time.pgf}
-    \caption[]{Median NPM of 30 randomized runs over time for optimal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
-The adaptive method yields results very close to the optimal method.
+    \vspace*{-0.6cm}
+    \caption[]{Median NPM of 30 Monte-Carlo runs over time for optimal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
 A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).
@@
     \input{simulations/plots/icassp2023-static/icassp2023-static.pgf}
-    \caption[]{Mean over time of median NPM of 30 randomized runs after convergence for varied values for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
+    \vspace*{-0.6cm}
+    \caption[]{Mean of 500 post-convergence frames of median NPM of 30 Monte-Carlo runs for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
 Results for optimal method, and adaptive \(\gamma_i\) included for comparison.
@@
 \end{figure}
-To evaluate the effectiveness of the proposed method, simulations were run.
-For this we define the error measure, the normalized projection misalignment
+To evaluate the effectiveness of the proposed extension, simulations were run.
+For this, we define the error measure as the normalized projection misalignment
 \begin{equation}
     \begin{aligned}
-        \text{NPM}(m) &= 20\,\log_{10} \frac{\left\| \mtxb{e} \right\|}{\left\|\h(m)\right\|},\\
-        \text{with}\quad \mtxb{e} &= \h(m) - \frac{\h^\T (m) \h_{\text{t}}}{\h_{\text{t}}^\T \h_{\text{t}}}\h(m),
+        \text{NPM}(n) &= 20\,\log_{10} \frac{\left\| \mtxb{e} \right\|}{\left\|\hat{\h}(n)\right\|},\\
+        \text{with}\quad \mtxb{e} &= \hat{\h}(n) - \frac{\hat{\h}^\T (n) \h}{\h^\T \h}\hat{\h}(n),
     \end{aligned}
 \end{equation}
-commonly used in BSI to compare estimated \(\h\) and true \(\h_t\).
-The simulation setup is a network with \(M=5\) nodes arranged in a ring topology, each node having \(|N_i|=2\) neighbors.
+commonly used in BSI to compare estimated \(\hat{\h}(n)\) and true \(\h\).
+
+The first simulation setup is a network with \(M=5\) nodes arranged in a ring topology, each node having \(|N_i|=2\) neighbors.
 The input signal is zero-mean white Gaussian noise (WGN), the impulse responses of length \(L=16\) are drawn from a normal distribution, and at each channel, independent WGN is added with \(\text{SNR}=10\,\text{dB}\).
@@
     \itemsep-0.2em
-    \item[(a)] all information is available for global norm computation ("optimal" in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
-    \item[(b)] neighborhood communication with fixed \(\gamma_i \in [0.0, 0.4]\) and \(K \in \{1,2,10\}\),
-    \item[(c)] neighborhood communication with adaptive \(\gamma_i\) \eqref{eq:adaptivenormest:adaptivegamma} and \(K=1\).
+    \item[(a)] \(\|\bar{\h}_i\|^2\) of all \(i \in \Mset\) is available for global norm computation ("optimal" in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
+    \item[(b)] Inter-neighborhood communication with fixed \(\gamma_i \in [0.0, 0.4]\) and \(K \in \{1,2,10\}\),
+    \item[(c)] Inter-neighborhood communication with adaptive \(\gamma_i\) \eqref{eq:adaptivenormest:adaptivegamma} and \(K=1\).
 \end{itemize}
@@
 
-\begin{todo}
-    TODO: dynamic scenario: add comparisons with optimal and static \(\gamma\) case, and describe in text, add figure captions, extend conclusion
-\end{todo}
+The second simulation setup is a \(3\)-node ring topology with a neighborhood size of \(|N_i|=2\).
+The input signal, impulse responses, additive noise, and SNR have the same parameters as the first simulation.
+To test the algorithms response to time-variant scenarios, the 3 impulse responses are then scaled to norms of \([2.2, 0.5, 1.2],\, [2.2, 1.0, 1.2],\, [2.2, 0.5, 2.0]\) at frames \(0,\, 5000,\, 10000\) respectively.
+\autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.
+It further shows the damped oscillations that appear in the estimates of \(\|\h^n\|\) around the target value 1 \autoref{fig:simulations:NPMtimedyn} (top) and \(\|\hat{\h}_i^n\|\) around the rescaled true norms \autoref{fig:simulations:NPMtimedyn} (middle), respectively.
 
-% \begin{figure}[t]
-%     \centering
-%     \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
-%     \caption[]{}
-%     \label{fig:simulations:NPMtimedyn}
-% \end{figure}
-% \begin{figure}[t]
-%     \centering
-%     \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}
-%     \caption[]{}
-%     \label{fig:simulations:normtime}
-% \end{figure}
-% \begin{figure}[t]
-%     \centering
-%     \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}
-%     \caption[]{}
-%     \label{fig:simulations:normstime}
-% \end{figure}
+In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case with \(K=1\) distributed averaging iterations.
+Further, introducing an adaptive \(\gamma_i^n\) allows the algorithm to converge faster and deal with time-variant systems.
+This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017} needing only \(K=1\) instead of \(K=50\) iterations.
 
@@
     \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
-    \caption[]{}
+    \vspace*{-0.6cm}
+    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^n\|\) over time, shown is the mean.
+Middle: Estimated \(\|\hat{\h}_i^n\|\) over time, shown is the mean.
+Dot-dashed lines are true values.
+Bottom: Median NPM, comparing optimal algorithm and proposed extended algorithm.
+Dashed vertical lines indicate rescaling events.}
     \label{fig:simulations:NPMtimedyn}
@@
 The mixing factor, which balances new data with recursion data, is set adaptively dependent on instantaneous channel estimate norms.
-
-These introductions reduce inter-node transmissions for each time frame and improve steady-state estimation performance to values close to the optimal case, where network-wide information is available at all nodes.
+These introductions reduce inter-node transmissions for each time frame while still delivering steady-state estimation performance close to the optimal case where network-wide information is available at all nodes.
+The reduction that can be achieved goes as far as only needing a single iteration and, therefore, one additional inter-neighborhood information exchange per time frame.
+We show this in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
+\begin{todo}
+    Could use the little space that's left for an illustration in the beginning or something :)
+\end{todo}
 
@@
 
-\vfill\pagebreak
+% \vfill\pagebreak
 

### 2022-10-18 paper.tex
version for Toon,Randy

@@
 Results for optimal method, and adaptive \(\gamma_i\) included for comparison.
-Hatched area in \autoref{fig:simulations:NPMtime} indicates frames used for computation of avg.
-NPM.}
+Hatched area in \autoref{fig:simulations:NPMtime} indicates frames used for computation of mean NPM.}
     \label{fig:simulations:avgNPMgamma}
@@
 \begin{todo}
-    Could use the little space that's left for an illustration in the beginning or something :)
+    Could use the little space that's left for an illustration in the beginning or something.
+Or add a comparison of numbers put into \autoref{tab:transcost:table} for different setups varying \(M,N_i,K\).
 \end{todo}

### 2022-10-18 paper.tex
version for Toon,Randy

@@
     We introduce an adaptive mixing factor between instantaneous and recursion values for adaptivity in a time-varying system.
-    Simulation results show that the extension provides estimation results close to the optimal fully-connected-network case while reducing inter-node transmission significantly.
+    Simulation results show that the extension provides estimation results close to the optimal fully-connected-network or broadcasting case while reducing inter-node transmission significantly.
 \end{abstract}

### 2022-10-18 paper.tex
version for Toon,Randy

@@
 \begin{todo}
-    Could use the little space that's left for an illustration in the beginning or something.
-Or add a comparison of numbers put into \autoref{tab:transcost:table} for different setups varying \(M,N_i,K\).
+    \begin{itemize}
+        \item Could use the little space that's left for an illustration in the beginning or something.
+        \item Or add a comparison of numbers put into \autoref{tab:transcost:table} for different setups varying \(M,N_i,K\).
+        \item Can increase \(L\) for simulations, not sure if necessary to show what the extension does.
+    \end{itemize}
 \end{todo}

### 2022-10-18 paper.tex
version for Toon,Randy

@@
     \itemsep-0.2em
-    \item[(1)] A fully connected network, where node \(i\) communicates \(\|\bar{\h}_i\|\) to all other nodes \(\{j \in \Nset_i = \Mset \setminus i\}\) directly, i.e., the neighborhood is the full network.
+    \item[(1)] A fully connected network, where node \(i\) communicates \(\|\bar{\h}_i\|\) to all other nodes \(\{j \in \Nset_i = \Mset\}\) directly, i.e., the neighborhood is the full network.
     \item[(2)] The node \(i\) broadcasts \(\|\bar{\h}_i\|\), i.e., it transmit to all other nodes \(\{j \in \Mset \setminus i\}\) without direct links.
-    \item[(3)] The node \(i\) communicates \(\|\bar{\h}_i\|\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset \setminus i\}\) and applies \(K\) distributed averaging iterations.
+    \item[(3)] The node \(i\) communicates \(\|\bar{\h}_i\|\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset\}\) and applies \(K\) distributed averaging iterations.
 \end{itemize}
 In this comparison, we only consider communication necessary for the computation of \eqref{eq:online_admm:consensus_update} as the rest of the algorithm is the same for our options.
-For (1) and (2), the cost per node increases linearly with network size \(M\), whereas for communication scheme (3), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only.
+For (1) and (2), the cost per node increases linearly with network size \(M\), whereas for communication scheme (3), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only and therefore independent of network size.
 The problem to be solved at each node \(i \in \Mset\) has complexity \(\mathcal{O}(M^2 L^2)\) for (1), with channel response length \(L\) (which means there is no reduction compared to a centralized approach).

### 2022-10-20 paper.tex
Included Randy's feedback

--- 2022-10-18 paper.tex
@@
 
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+
 % Title.
 % ------
-\title{SOMETHING ABOUT THE DISTRIBUTED AVERAGING BASED APPROXIMATION IN SENSOR NETWORKS}
+\title{Distributed averaging-based approach to BSI with ADMM}
 %
@@
 % ---------------
-\name{Matthias Blochberger\(^1\), Filip Elvander\(^2\), Randall Ali\(^1\), Toon van Waterschoot\(^1\),tbd\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+\name{M.
+Blochberger\(^1\), R.
+Ali\(^1\), F.
+Elvander\(^2\), T.
+van Waterschoot\(^1\),tbd\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
 This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
@@
 \begin{abstract}
-    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks as to reduce communication cost and computational complexity or avoid reliance on a single device for processing.
+    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce communication cost and computational complexity or avoid reliance on a single device for processing.
     In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the knowledge of a stacked network-wide solution vector at each node, the computation of which requires either broadcasting or relaying of node-specific values to all other nodes.
@@
 Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154} to name a few, have been proposed.
-The task of distributed single-input-multiple-output (SIMO) blind system identification (BSI) had contributions such as the adaptive cross-relation-based (CR) \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
+Another important task in audio and communication applications, which however has not recived as much attention, is multi-channel system identification, i.e.
+estimating channel responses in time or frequency domain.
+Distributed single-input-multiple-output (SIMO) blind system identification (BSI) had contributions such as the adaptive cross-relation-based (CR) \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
 Furthermore, we recently introduced an adaptive CR-based algorithm \cite{blochbergerDBSI} using the alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011}.
-All of the mentioned distributed BSI algorithms rely on information shared between neighboring sensor nodes within the network.
-However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to, e.g., \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003}), which manifests itself as one or more global variables.
-In this case, the computation of the global variable requries information from all the nodes within the network.
+
+All of the aforementioned distributed BSI algorithms rely on shared information between neighboring sensor nodes within the network.
+However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to, e.g., \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003}), which manifests itself as one or more variables that require network-wide shared information for their computation.
 The algorithm in \cite{blochbergerDBSI} relies on node-wise values being relayed throughout the network.
@@
 This approach allows us to compute the global variable without the need of a fully connected network or broadcasting.
-Further, we introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
-Simulation results show how the extension leads to BSI performance close to an optimal case where all information is available without the need of broadcasting variables to all nodes or a large number of estimation iterations.
+We also introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
+Simulation results demonstrate how the extension leads to BSI performance close to an optimal case where all information is available without the need of a fully connected network or a large number of estimation iterations.
 
@@
 % This does however not represent an actual inter-node link.
-We can define the symmetric adjacency matrix \(\mtxb{C}\) with elements
-\begin{equation}
-    C_{ij} = \begin{cases}
-        1 \quad \text{if } \{i,j\} \in \mathcal{E}\\
-        0 \quad \text{otherwise}.
-    \end{cases}
-\end{equation}
-It may be noted that in \cite{blochbergerDBSI}, the pairs \(\{i,j\} \in \mathcal{E}\) are ordered, which yields a directed graph and leads to two sets of neighborhoods ("transmit" and "receive") and therefore a non-symmetric adjacency matrix.
+We can define the symmetric adjacency matrix \(\mtxb{C}\) with elements \(C_{ij} = 1\) if \(\{i,j\} \in \mathcal{E}\) and 0 otherwise.
+It may be noted that in \cite{blochbergerDBSI}, the pairs \(\{i,j\} \in \mathcal{E}\) are ordered, which yields a directed graph and leads to two sets of neighborhoods (``transmit'' and ``receive'') and therefore a non-symmetric adjacency matrix.
 For the sake of brevity, we limit the explanations in this paper to the undirected case.
@@
 \begin{align}
+    % \textstyle
     \mtxb{s}(n) &= [s(n),\,\ldots,\,s(n-2L+2)]^{\T},\\
@@
 In BSI, the coss-relation problem formulation only uses output signals \(\x_i(n)\), exploiting relative information between them, to identify the system, i.e., the acoustic or communication channels \(\h = [\h_1^\T,\,...,\,\h_M^\T]^\T\).
-The solution to this problem is found by the minimization problem (cf.
-e.g.
-\cite{langtongBlindIdentificationEqualization1994,huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003,blochbergerDBSI})
+The solution to this problem is found by the minimization problem \cite{langtongBlindIdentificationEqualization1994,huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003,blochbergerDBSI}:
 \begin{equation}
@@
 \end{equation}
-where the estimate is \(\hat{\h} = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\).
-In \cite{blochbergerDBSI}, this problem is solved by a distributed adaptive algorithm that is based on separating the problem \eqref{eq:frequency_domain:min_prob} into node-wise subproblems of analogous form, whoever only using a subset channels, provided by neighboring nodes \(\Nset_i \subset \Mset\).
+where \(\hat{\h} = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) is the vector of estimated channel responses.
+In \cite{blochbergerDBSI}, this problem is solved by a distributed adaptive algorithm that is based on separating the problem \eqref{eq:frequency_domain:min_prob} into node-wise subproblems,
+\begin{equation}
+    \begin{aligned}
+        \underset{\w,\,\h}{\min} \quad &\sum_{i \in \Mset} \w_i^\herm \aRhof_i \w_i\\
+        \text{s.t.} \quad &(\w_i)_j = \h_{\mathcal{G}(i,j)}\quad i \in \Mset,\,j \in \Nset_i\\
+        &\|\h\| = 1.
+    \end{aligned}\label{eq:general_consensus_admm:min_prob}
+\end{equation}
+Here, each subproblem \(\w_i^\herm \aRhof_i \w_i\), with the node-local estimates \(\w_i\) and data matrix \(\aRhof_i\).
+Both are analogous to \(\h_i\) and \(\R\) in \eqref{eq:frequency_domain:min_prob}, however, only using a subset channels, provided by neighboring nodes \(\Nset_i \subset \Mset\).
+The first constraint enforces a consensus of local estimates, and \(\mathcal{G}(i,j)\) is a parameter mapping function equating local estimates of nodes connected by edge \((i,j) \in \mathcal{E}\).
 General-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} is applied in an adaptive updating scheme (Online-ADMM) \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
-This leads to update steps for local, consensus, and dual variables (we refer the reader to \cite{blochbergerDBSI} for details).
-The consensus variable in the algorithm is the estimate of the system \(\hat{\h}\).
-In the distributed algorithm, each of its subvectors \(\hat{\h}_i\) is computed at the respective node \(i\).
-The update step for \(\hat{\h}_i\) is of interest for this extension.
+ADMM leads to update steps for local, consensus, and dual variables.
+We refer the reader to \cite{blochbergerDBSI} for details.
+The algorithm's consensus variable is the system's estimate, \(\hat{\h}\).
+Each node \(i\) computes the respective subvector \(\hat{\h}_i\) locally, which is the computation step of interest for this extension.
 % Separating the cost function and applying general-form consensus ADMM as an adaptive algorithm leads to the update steps
 % \begin{align}
-%     \w_i^{n+1} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^n,\uu^n)\label{eq:general_consensus_admm:local}\\
-%     \h^{n+1} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{n+1},\h,\uu^n)\label{eq:general_consensus_admm:global}\\
-%     \uu_i^{n+1} &= \uu_i^{n} + \rho \left( \w_i^{n+1} - \tilde{\h}_i^{n+1} \right),\label{eq:general_consensus_admm:dual}
+%     \w_i^{(n+1)} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^{(n)},\uu^{(n)})\label{eq:general_consensus_admm:local}\\
+%     \h^{(n+1)} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{(n+1)},\h,\uu^{(n)})\label{eq:general_consensus_admm:global}\\
+%     \uu_i^{(n+1)} &= \uu_i^{(n)} + \rho \left( \w_i^{(n+1)} - \tilde{\h}_i^{(n+1)} \right),\label{eq:general_consensus_admm:dual}
 % \end{align}
 % where \(\w_i\) represents channels estimates of lower dimensional subproblems, solved locally by node \(i\), \(\h = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) the consensus variable (estimate of the system), and \(\uu_i\) are the dual variables.
-\begin{todo}
-    Is this enough?
+% \begin{todo}
+%     Is this enough?
 I fear i have to use a full page introducing all the local, consensus, dual variables, parameter mapping and the lagrangian etc.
 only to get to \eqref{eq:online_admm:consensus_update} and say that the denominator is what we are looking at...
-\end{todo}
+% \end{todo}
 It is defined as
 \begin{equation}
-    \hat{\h_i}^{n+1} = \frac{\bar{\h}_i^{n+1}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{n+1}\|^2}}.\label{eq:online_admm:consensus_update}
+    \hat{\h_i}^{(n+1)} = \frac{\bar{\h}_i^{(n+1)}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{(n+1)}\|^2}}\label{eq:online_admm:consensus_update}
 \end{equation}
-% for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{n+1}\), a combination of neigborhood averages of \(\w_j\) and \(\uu_j\), \(j \in \Nset_i\).
-The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires  \(\|\bar{\h}_j^{n+1}\|\) from all nodes \(j \in \Mset\), which however, is not possible without a fully-connected network or broadcasting.
+for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{(n+1)}\), a combination of neigborhood averages of local estimates and dual variables, see \cite{blochbergerDBSI}.
+The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires  \(\|\bar{\h}_j^{(n+1)}\|\) from all nodes \(j \in \Mset\), which however, is not possible without a fully-connected network or broadcasting.
 In \cite{blochbergerDBSI}, we assume that partial squared norms are relayed throughout the network until all nodes have the information necessary.
-In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}, a global value is estimated by a distributed averaging approach, iteratively combining values within neighborhoods until convergence to a network-wide average.
 
-Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need of network wide data transmission, with the further introduction of an adaptive mixing factor to include instantaneous values in the recursion.
+In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016},
+a global value is estimated by a related iterative averaging approach, combining values within neighborhoods until convergence to a network-wide average.
+
+Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need of network wide data transmission.
+The approach described in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} employs a related iterative averaging scheme within a distributed gradient descent algorithm for BSI in order to estimate a global variable, however, necessitating many iterations per frame.
+So we further introduce an adaptive mixing factor to include instantaneous values in the recursion to separate avaraging iterations onto time frames of the adaptive algorithm.
 
@@
 \subsection[]{Distributed averaging}
-The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i\|^2\) at each node \(i \in \Mset\).
-To avoid the large number of transmissions, which would be necessary to facilitate this, we will approximate the squared norm \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
+% The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i\|^2\) at each node \(i \in \Mset\).
+% To avoid the large number of transmissions, which would be necessary to facilitate this, we will approximate the squared norm \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
+First, assuming we have some unnormalized consensus variables \(\bar{\h}_i\) for \(i \in \Mset\), we look to distributively compute a sum of their squared norms, \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\), for \eqref{eq:online_admm:consensus_update} at each node \(i\).
 
-We look at distributed linear combinations with the iteration index \(k=0,...,K\),
+Distributed linear combinations allow us to compute an average in a distributed manner, which makes computing the desired sum straightforward.
+They have the form of
 \begin{equation}
@@
 \end{equation}
-which can be written in vector form as \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\).
-We want to find the matrix \(\mtxb{W}\), which ensure that for any initial value \(\bm{\phi}({0})\), each element of \(\bm{\phi}({k})\) converges to the average of the elements of \(\bm{\phi}({0})\) when \(k \to \infty\).
-In this application, the elements of \(\bm{\phi}(0)\) are the initial node-wise squared norm values \(\|\bar{\h}_i\|^2\) which then leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) for all \(i \in \Mset\).
-This is achieved by solving the fastest distributed linear averaging (FDLA) problem, introduced in \cite{xiaoFastLinearIterations2004}, in the form of
+with iteration index \(k=0,...,K\).
+This can be written in vector form \(\bm{\phi}({k+1}) = \W \bm{\phi}({k})\) with \(\bm{\phi}(k) = \begin{bmatrix} \phi_1(k) & \ldots & \phi_M(k) \end{bmatrix}^\T\).
+We want to find the matrix \(\mtxb{W}\), which will ensure that for any initial value \(\bm{\phi}({0})\), each element of \(\bm{\phi}({k})\) converges to the average of the elements of \(\bm{\phi}({0})\) when \(k \to \infty\).
+In this application, the elements of \(\bm{\phi}(0)\) are the initial node-wise squared norm values \(\|\bar{\h}_i\|^2\), of which we want to compute the sum of.
+This leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) for all \(i \in \Mset\).
+Computing the desired \(\mtxb{W}\) is done by solving the fastest distributed linear averaging (FDLA) problem, introduced in \cite{xiaoFastLinearIterations2004}, in the form of
 \begin{equation}
@@
 Now, the \(i\)-th row of \(\W\) contains the neigborhood weights for node \(i\) as non-zero entries.
+It is to note that this has to be done only once for any fixed network \(\Mset\) and \(\mathcal{E}\).
 % \begin{todo}
@@
 % In usual applications of the iteration \eqref{eq:adaptivenormest:distlincomb}, it is applied \(K \in \mathbb{N}\) times until convergence of the averages is reached.
-In an adaptive algorithm, where the resulting variable is required at each time frame \(n\) such as e.g.
-\cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} and \cite{blochbergerDBSI}, it introduces \(K\) secondary iterations per frame.
-Each iteration requires information exchange within neighborhoods, adding to the communication cost of the algorithm.
-In order to mitigate this, we split iterations over frames \(n\) to keep \(K\) as low as possible.
-However, as each frame introduces new data, we need to include this data into the recursion.
-To this end, we further introduce an instantaneous weighted neighborhood average of node-wise squared norm values \(\bar{\phi}_i^{n} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^n\|^2\) which is then combined with the iterative average into
+\subsection[]{Proposed adaptive estimation}
+Given that the BSI algorithm being extended \cite{blochbergerDBSI} is adaptive and the unnormalized consensus estimates \(\bar{\h}_i^{(n)}\) are therefore time-varying, computing a distributed sum of their norms has to be adapted.
+The baseline approach is to compute \(K\) iterations \eqref{eq:adaptivenormest:distlincomb} per frame index \(n\).
+For this iterative approach to converge, \(K\) has to be sufficiently large (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
+This is suboptimal, as each iteration requires that a node \(i\) shares the averaging variable \(\phi_i(k)\) with its neighborhood \(\Nset_i\).
+Therefore, we first propose to split iterations over time frames, i.e., each \(n\), we set the initial values \(\phi_i^{(n)}(0) = \phi_i^{(n-1)}(K)\), that is, the result of the last iteration of the previous frame.
+This means \(K\) can be chosen small, given that after sufficient frames \(n\), convergence will be reached.
+This rudimentary first modification, however, does not factor in the adaptive approach to channel identification.
+That is, when letting \(\phi_i^{(n)}(0) = \|\bar{\h}_i^{(0)}\|\), with \(\bar{\h}_i^{(0)}\) being estimates at the inital frame \(n=0\), the approach converges to the sum of these inital - bad - estimates.
+Therefore we factor in the instantaneous approximation, the weighted in-neighborhood sum \(\eta_i^{(n)} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\).
+This leads to
 \begin{equation}
-    \hat{\phi}_i^{n+1} = \gamma_i \bar{\phi}_i^{n} + (1-\gamma_i) \phi_i^{n}(K)
+    \hat{\phi}_i^{(n+1)} = \gamma_i \eta_i^{(n)} + (1-\gamma_i) \phi_i^{(n)}(K),
 \end{equation}
 where \(\gamma_i\) is a mixing factor.
-With the right choice of mixing factor \(\gamma_i\), this leads to a reduction of distributed averaging iterations \(K\) and improves behaviour of the algorithm when the norms \(\|\h_i\|\) are time-variant (see \autoref{sec:simulations}).
-% The factor balances instantaneous values and the distributed averaging iterations, and we shoudl look at the two extreme cases for further insight.
-% For \(\gamma_i = 0\), only instantaneous neighborhood averages are used, which effectively leads to suboptimal computation, as \(\hat{\phi}_1^{n} = \hat{\phi}_2^{n} = \ldots = \hat{\phi}_M^{n}\) for large enough \(n\) will never be reached.
-% For \(\gamma_i=1\), only the distributed averaging iterations are considered, i.e., we effectively combine the per-frame secondary recursion \eqref{eq:adaptivenormest:distlincomb} from \(K\) to \(mK\) iterations.
-% There however, no new data is introduced which leads to performance degradadation in the adaptive algorithm as it only considers inital estimates from \(m=1\), which might be far of the optimum.
-
-\subsection[]{Adaptive mixing factor}
-To avoid choosing a fixed value for \(\gamma_i\), we use information provided by \(\bar{\phi}_i^{n}\).
-If the absolute difference between subsequent frames \(| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |\) nears 0, then this means that the estimation of \(\bar{\h}_i\) is converging to a steady state.
-Is this the case, then the emphasis of the algorithm should lie on norm estimation, i.e. the distributed averaging recursion, which in turn means \(\gamma_i\) should go towards 0 as well.
-We set \(\gamma_i^{n}\) proportional to the absolute difference between subsequent frames and set an upper limit at 1,
+We exploit the instantaneous information \(\eta_i^{(n)}\) to find values for the mixing factor.
+If the absolute difference between subsequent frames \(| \eta_i^{(n)} - \eta_i^{(n-1)} | \to 0\), then the estimation of \(\bar{\h}_i\) is converging to a steady state.
+The algorithm's emphasis should then lie on norm estimation, i.e., the distributed averaging recursion, which means \(\gamma_i \to 0\).
+We heuristically set \(\gamma_i^{(n)}\) proportional to the absolute difference of instantaneous approximations between subsequent frames and set an upper limit at 1,
 \begin{equation}
-    \gamma_i^{n} = \min \left\lbrace \frac{| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |}{\bar{\phi}_i^{n-1}},\,1\right\rbrace.\label{eq:adaptivenormest:adaptivegamma}
+    \gamma_i^{(n)} = \min \left\lbrace \frac{| \eta_i^{(n)} - \eta_i^{(n-1)} |}{\eta_i^{(n-1)}},\,1\right\rbrace.\label{eq:adaptivenormest:adaptivegamma}
 \end{equation}
-The initial value for \(\bar{\phi}_i^{n-1}\) for \(n=0\) can be set to an arbitrary real number, in our case 1.
+The initial value for \(\eta_i^{(n-1)}\) for \(n=0\) can be set to an arbitrary real number, in our case 1.
 % The combination of instantaneous values and distributed averaging estimate should lead to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed should increase as well.
 Refer to \autoref{alg:davg_norm_est} for the extended algorithm introduced in this section.
-
-\begin{algorithm}[t]
-    \caption{ADMM BSI with distributed-averaging-based adaptive estimation of norm values}\label{alg:davg_norm_est}
-    \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
-    \(\bar{\phi}_i^{n-1} \gets 1, \forall i \in \Mset\)\;
-    \For(){\(n=0\dots\)}
-    {
-        \For(){\(i \in \Mset\)}
-        {
-            % \(\cdots\)\\
-            % \(\w_i^n \gets \operatorname{argmin}_{\w_i}\, \mathcal{L}_{\rho} (\w,\h^n,\uu^n)\)\;
-            % Compute \(\bar{\h}_i^{n}\)\;
-            % \(\cdots\)\\
-            \emph{The steps before are as introduced in }\cite{blochbergerDBSI}\\
-            \dotfill\\
-            Transmit \(\bar{\h}_i^{n}\) to nodes  \(j \in \Nset_i\)\;
-            \(\bar{\phi}_i^{n} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^n\|^2\)\;
-            \(\gamma_i^{n} \gets \min \left\lbrace \frac{| \bar{\phi}_i^{n} - \bar{\phi}_i^{n-1} |}{\bar{\phi}_i^{n-1}},\,1\right\rbrace\)\;
-            \eIf(){\(m = 0\)}
-            {
-                \(\phi_i^{n}(1) \gets \|\bar{\h}_i^n\|^2\)\;
-            }
-            {
-                \(\phi_i^{n}(1) \gets \hat{\phi}_i^{n-1}(K)\)\;
-            }
-            \For(){\(k=0,\dots,K\)}
-            {
-                Transmit \(\phi_i^n(k)\) to nodes  \(j \in \Nset_i\)\;
-                \(\phi_i^n({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j^n({k})\)\;
-            }
-            \(\hat{\phi}_i^{n} \gets \gamma_i \bar{\phi}_i^{n} + (1-\gamma) \phi_i^{n}(K)\)\;
-            \(\hat{\h_i}^{n} \gets \frac{\bar{\h}_i^{n}}{\sqrt{\hat{\phi}_i^{n}M}}\)\;
-            \dotfill\\
-            \emph{The steps after are as introduced in }\cite{blochbergerDBSI}\\
-            % \(\cdots\)\\
-            % \(\uu_i^{n} \gets \uu_i^{n-1} + \rho \left( \w_i^{n} - \tilde{\h}_i^{n} \right)\)\;
-            % \(\cdots\)\\
-            % % \,\\
-        }
-    }
-\end{algorithm}
 
@@
 %         \hline
-%         (3) Neighborhood & \(\mathcal{O}(\bar{N}_i K)\) \\ 
+%         (2) Neighborhood & \(\mathcal{O}(\bar{N}_i K)\) \\ 
 %         \hline
@@
 % \renewcommand{\arraystretch}{1.0}
-\renewcommand{\arraystretch}{1.2}
-\begin{table}[t]
-    \centering
-    \begin{tabular}{ |l|l|l|l| }
-        \hline
-        & Trans. Ops. & Rec. Ops. & Local Compl. \\
-        \hline\hline
-        (1) Fully connected & \(M-1\) & \(M-1\) & \(\mathcal{O}(M^2 L^2)\) \\
-        \hline
-        (2) Broadcast & \(1\) & \(M-1\) & \(\mathcal{O}(N_i^2 L^2)\)  \\ 
-        \hline
-        (3) Neighborhood & \(N_i K\) & \(N_i K\) & \(\mathcal{O}(N_i^2 L^2)\)\\ 
-        \hline
-    \end{tabular}
-    % \caption[]{Comparison of communication cost (transmission operations \& receive operations) and local problem complexity for a node \(i\) within the network.
-\(M\) is the number of nodes within the network, \(N_i\) is the number neighboring nodes, \(L\) is the lenght of channel responses, \(K\) is the number of distributed averaging iterations.}
-    \caption[]{Comparison of communication cost (transmission operations \& receive operations) and local problem complexity for a node \(i\) within the network.}
-    \label{tab:transcost:table}
-\end{table}
-\renewcommand{\arraystretch}{1.0}
 To describe the communication cost within the network, we count the number of variables transmitted per time frame \(n\).
@@
     \itemsep-0.2em
-    \item[(1)] A fully connected network, where node \(i\) communicates \(\|\bar{\h}_i\|\) to all other nodes \(\{j \in \Nset_i = \Mset \setminus i\}\) directly, i.e., the neighborhood is the full network.
-    \item[(2)] The node \(i\) broadcasts \(\|\bar{\h}_i\|\), i.e., it transmit to all other nodes \(\{j \in \Mset \setminus i\}\) without direct links.
-    \item[(3)] The node \(i\) communicates \(\|\bar{\h}_i\|\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset \setminus i\}\) and applies \(K\) distributed averaging iterations.
+    \item[(1)] A fully-connected network, where node \(i\) communicates \(\|\bar{\h}_i\|^2\) to all other nodes \(\{j \in \Nset_i = \Mset\}\) directly, i.e., the neighborhood is the full network.
+    % \item[(2)] The node \(i\) broadcasts \(\|\bar{\h}_i\|\), i.e., it transmits to all other nodes \(\{j \in \Mset \setminus i\}\) without direct links.
+    \item[(2)] The node \(i\) communicates \(\|\bar{\h}_i\|^2\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset\}\) and applies \(K\) distributed averaging iterations.
 \end{itemize}
-In this comparison, we only consider communication necessary for the computation of \eqref{eq:online_admm:consensus_update} as the rest of the algorithm is the same for our options.
-For (1) and (2), the cost per node increases linearly with network size \(M\), whereas for communication scheme (3), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only.
-The problem to be solved at each node \(i \in \Mset\) has complexity \(\mathcal{O}(M^2 L^2)\) for (1), with channel response length \(L\) (which means there is no reduction compared to a centralized approach).
-For (2) and (3), local complexity is \(\mathcal{O}(N_i^2 L^2)\), where \(N_i\) is the neighborhood size.
-Refer to \autoref{tab:transcost:table} for a direct comparison.
+\autoref{tab:transcost:table} compares the number of transmit and receive operations a node \(i\) has to apply in order to compute \eqref{eq:online_admm:consensus_update}.
+Further, it shows the complexity of the problem a node \(i\) has to solve according to \cite{blochbergerDBSI} given the two types of network topology, assuming it uses all information it receives.
+The advantage of the fully distributed algorithm becomes clear when \(M>>N_i\), as the additional communication and local complexity depends on neighborhood size \(N_i\) and not on network size \(M\).
+% In this comparison, we only consider communication necessary for the computation of \eqref{eq:online_admm:consensus_update} as the rest of the algorithm is the same for our options.
+% For (1), the cost per node increases linearly with network size \(M\), whereas for communication scheme (2), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only and therefore independent of network size.
+% The problem to be solved at each node \(i \in \Mset\) has complexity \(\mathcal{O}(M^2 L^2)\) for (1), with channel response length \(L\) (which means there is no reduction compared to a centralized approach).
+% For (2), local complexity is \(\mathcal{O}(N_i^2 L^2)\), where \(N_i\) is the neighborhood size.
+\vspace*{-0.6em}
+\renewcommand{\arraystretch}{1.2}
+\begin{table}[h]
+    \centering
+    \begin{tabular}{ |l|l|l|l| }
+        \hline
+        & Trans. Ops. & Rec. Ops. & Local Compl. \\
+        \hline\hline
+        (1) Fully con. & \(M-1\) & \(M-1\) & \(\mathcal{O}(M^2 L^2)\) \\
+        \hline
+        % (2) Broadcast & \(1\) & \(M-1\) & \(\mathcal{O}(N_i^2 L^2)\)  \\ 
+        % \hline
+        (2) Neighborh. & \(N_i K\) & \(N_i K\) & \(\mathcal{O}(N_i^2 L^2)\)\\ 
+        \hline
+    \end{tabular}
+    % \caption[]{Comparison of communication cost (transmission operations \& receive operations) and local problem complexity for a node \(i\) within the network.
+\(M\) is the number of nodes within the network, \(N_i\) is the number neighboring nodes, \(L\) is the lenght of channel responses, \(K\) is the number of distributed averaging iterations.}
+    \caption[]{Communication cost per node and frame \(n\) for computation of \eqref{eq:online_admm:consensus_update}.}
+    \label{tab:transcost:table}
+\end{table}
+\renewcommand{\arraystretch}{1.0}
 % To describe the communication cost within the network, we adopt the Big-\(\mathcal{O}\) notation, similar to the complexity analysis of algorithms.
@@
 %     \item[(2)] The nodes employ broadcasting, i.e., the nodes transmit to all other nodes without direct links.
-%     \item[(3)] The nodes only communicate with neighboring nodes, \(\Nset_i \subset \Mset\).
+%     \item[(2)] The nodes only communicate with neighboring nodes, \(\Nset_i \subset \Mset\).
 % \end{itemize}
 % For (1) and (2), the cost per node increases linearly with network size \(M\): \(\mathcal{O}(M)\).
-% Using communication scheme (3), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed as an extension to \cite{blochbergerDBSI} in this paper, cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only: \(\mathcal{O}(\bar{N}_i K)\).
+% Using communication scheme (2), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed as an extension to \cite{blochbergerDBSI} in this paper, cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only: \(\mathcal{O}(\bar{N}_i K)\).
 % \begin{todo}
@@
     \caption[]{Mean of 500 post-convergence frames of median NPM of 30 Monte-Carlo runs for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
-Results for optimal method, and adaptive \(\gamma_i\) included for comparison.
+Results for optimal algorithm, and adaptive \(\gamma_i\) included for comparison.
 Hatched area in \autoref{fig:simulations:NPMtime} indicates frames used for computation of mean NPM.}
@@
 \end{figure}
-To evaluate the effectiveness of the proposed extension, simulations were run.
-For this, we define the error measure as the normalized projection misalignment
+To evaluate the effectiveness of the proposed extension, simulations were run, where we define the error measure as the normalized projection misalignment
 \begin{equation}
@@
     \itemsep-0.2em
-    \item[(a)] \(\|\bar{\h}_i\|^2\) of all \(i \in \Mset\) is available for global norm computation ("optimal" in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
+    \item[(a)] \(\|\bar{\h}_i\|^2\) of all \(i \in \Mset\) is available for global norm computation (``optimal'' in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
     \item[(b)] Inter-neighborhood communication with fixed \(\gamma_i \in [0.0, 0.4]\) and \(K \in \{1,2,10\}\),
@@
 With \(K=10\), the performance comes close to the optimal case at the cost of additional communication between nodes.
-Compare that to the case with adaptive \(\gamma_i\) where even at \(K=1\), i.e., no additional communication for the recursive estimation scheme, convergence speed and steady-state error are close to the optimal case.
+This in contrast to the case with adaptive \(\gamma_i\) where even at \(K=1\), i.e., no additional communication for the recursive estimation scheme, convergence speed and steady-state error are close to the optimal case.
 
@@
 \autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.
-It further shows the damped oscillations that appear in the estimates of \(\|\h^n\|\) around the target value 1 \autoref{fig:simulations:NPMtimedyn} (top) and \(\|\hat{\h}_i^n\|\) around the rescaled true norms \autoref{fig:simulations:NPMtimedyn} (middle), respectively.
+It further shows the damped oscillations that appear in the estimates of \(\|\hat{\h}^{(n)}\|\) around the target value 1 \autoref{fig:simulations:NPMtimedyn} (top) and \(\|\hat{\h}_i^{(n)}\|\) around the rescaled true norms \autoref{fig:simulations:NPMtimedyn} (middle), respectively.
 
 In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case with \(K=1\) distributed averaging iterations.
-Further, introducing an adaptive \(\gamma_i^n\) allows the algorithm to converge faster and deal with time-variant systems.
+Further, introducing an adaptive \(\gamma_i^{(n)}\) allows the algorithm to converge faster and deal with time-variant systems.
 This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017} needing only \(K=1\) instead of \(K=50\) iterations.
@@
     \vspace*{-0.6cm}
-    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^n\|\) over time, shown is the mean.
-Middle: Estimated \(\|\hat{\h}_i^n\|\) over time, shown is the mean.
+    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^{(n)}\|\) over time, shown is the mean.
+Middle: Estimated \(\|\hat{\h}_i^{(n)}\|\) over time, shown is the mean.
 Dot-dashed lines are true values.
@@
 \begin{todo}
-    Could use the little space that's left for an illustration in the beginning or something.
-Or add a comparison of numbers put into \autoref{tab:transcost:table} for different setups varying \(M,N_i,K\).
+    \begin{itemize}
+        \item Scale up simulation (for first setup) to \(M >> N_i\), like M = 50 and neighborhoods like in Toon's paper.
+        \item minor changes to plot labels, legend layouts
+    \end{itemize}
 \end{todo}
 
-% Below is an example of how to insert images. Delete the ``\vspace'' line,
-% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
-% with a suitable PostScript file name.
-% -------------------------------------------------------------------------
-% \begin{figure}[htb]
+\begin{algorithm}[t]
+    \caption{ADMM BSI with distributed-averaging-based adaptive estimation of norm values}\label{alg:davg_norm_est}
+    \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
+    \(\eta_i^{(n-1)} \gets 1, \forall i \in \Mset\)\;
+    \For(){\(n=0\dots\)}
+    {
+        \For(){\(i \in \Mset\)}
+        {
+            % \(\cdots\)\\
+            % \(\w_i^{(n)} \gets \operatorname{argmin}_{\w_i}\, \mathcal{L}_{\rho} (\w,\h^{(n)},\uu^{(n)})\)\;
+            % Compute \(\bar{\h}_i^{(n)}\)\;
+            % \(\cdots\)\\
+            \emph{The steps before are as introduced in }\cite{blochbergerDBSI}\\
+            \dotfill\\
+            Transmit \(\bar{\h}_i^{(n)}\) to nodes  \(j \in \Nset_i\)\;
+            \(\eta_i^{(n)} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\)\;
+            \(\gamma_i^{(n)} \gets \min \left\lbrace \frac{| \eta_i^{(n)} - \eta_i^{(n-1)} |}{\eta_i^{(n-1)}},\,1\right\rbrace\)\;
+            \eIf(){\(n = 0\)}
+            {
+                \(\phi_i^{(n)}(1) \gets \|\bar{\h}_i^{(n)}\|^2\)\;
+            }
+            {
+                \(\phi_i^{(n)}(1) \gets \hat{\phi}_i^{(n-1)}(K)\)\;
+            }
+            \For(){\(k=0,\dots,K\)}
+            {
+                Transmit \(\phi_i^{(n)}(k)\) to nodes  \(j \in \Nset_i\)\;
+                \(\phi_i^{(n)}({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j^{(n)}({k})\)\;
+            }
+            \(\hat{\phi}_i^{(n)} \gets \gamma_i \eta_i^{(n)} + (1-\gamma) \phi_i^{(n)}(K)\)\;
+            \(\hat{\h_i}^{(n)} \gets \frac{\bar{\h}_i^{(n)}}{\sqrt{\hat{\phi}_i^{(n)}M}}\)\;
+            \dotfill\\
+            \emph{The steps after are as introduced in }\cite{blochbergerDBSI}\\
+            % \(\cdots\)\\
+            % \(\uu_i^{(n)} \gets \uu_i^{(n-1)} + \rho \left( \w_i^{(n)} - \tilde{\h}_i^{(n)} \right)\)\;
+            % \(\cdots\)\\
+            % % \,\\
+        }
+    }
+\end{algorithm}
 
-% \begin{minipage}[b]{1.0\linewidth}
-%   \centering
-%   \centerline{\includegraphics[width=8.5cm]{image1}}
-% %  \vspace{2.0cm}
-%   \centerline{(a) Result 1}\medskip
-% \end{minipage}
-% %
-% \begin{minipage}[b]{.48\linewidth}
-%   \centering
-%   \centerline{\includegraphics[width=4.0cm]{image3}}
-% %  \vspace{1.5cm}
-%   \centerline{(b) Results 3}\medskip
-% \end{minipage}
-% \hill
-% \begin{minipage}[b]{0.48\linewidth}
-%   \centering
-%   \centerline{\includegraphics[width=4.0cm]{image4}}
-% %  \vspace{1.5cm}
-%   \centerline{(c) Result 4}\medskip
-% \end{minipage}
-% %
-% \caption{Example of placing a figure with experimental results.}
-% \label{fig:res}
-% %
-% \end{figure}
-
-% \vfill\pagebreak
+\vfill\pagebreak
 

### 2022-10-20 paper.tex
Included Randy's feedback

@@
 \end{itemize}
-\autoref{fig:simulations:NPMtime} shows the median of 30 Monte-Carlo runs.
-We can observe that when fixing \(\gamma_i\), a tradeoff between convergence speed and steady-state error arises at low iteration counts (cf. also \autoref{fig:simulations:avgNPMgamma}).
-With \(K=10\), the performance comes close to the optimal case at the cost of additional communication between nodes.
-This in contrast to the case with adaptive \(\gamma_i\) where even at \(K=1\), i.e., no additional communication for the recursive estimation scheme, convergence speed and steady-state error are close to the optimal case.
-
-The second simulation setup is a \(3\)-node ring topology with a neighborhood size of \(|N_i|=2\).
-The input signal, impulse responses, additive noise, and SNR have the same parameters as the first simulation.
-To test the algorithms response to time-variant scenarios, the 3 impulse responses are then scaled to norms of \([2.2, 0.5, 1.2],\, [2.2, 1.0, 1.2],\, [2.2, 0.5, 2.0]\) at frames \(0,\, 5000,\, 10000\) respectively.
-\autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.
-It further shows the damped oscillations that appear in the estimates of \(\|\hat{\h}^{(n)}\|\) around the target value 1 \autoref{fig:simulations:NPMtimedyn} (top) and \(\|\hat{\h}_i^{(n)}\|\) around the rescaled true norms \autoref{fig:simulations:NPMtimedyn} (middle), respectively.
-
-In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case with \(K=1\) distributed averaging iterations.
-Further, introducing an adaptive \(\gamma_i^{(n)}\) allows the algorithm to converge faster and deal with time-variant systems.
-This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017} needing only \(K=1\) instead of \(K=50\) iterations.
-
-\begin{figure}[t]
-    \centering
-    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}\\\vspace*{-1.0cm}
-    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}\\\vspace*{-1.0cm}
-    \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
-    \vspace*{-0.6cm}
-    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^{(n)}\|\) over time, shown is the mean.
-Middle: Estimated \(\|\hat{\h}_i^{(n)}\|\) over time, shown is the mean.
-Dot-dashed lines are true values.
-Bottom: Median NPM, comparing optimal algorithm and proposed extended algorithm.
-Dashed vertical lines indicate rescaling events.}
-    \label{fig:simulations:NPMtimedyn}
-\end{figure}
-
-\section[]{Conclusions}
-\label{sec:conclusions}
-In this contribution, we propose an extension to a distributed adaptive BSI algorithm applied in sensor networks.
-Based on distributed averaging, only using the information provided by neighboring nodes in the sensor network, we compute estimates of norm values of channel estimates in order to enforce a norm constraint.
-By balancing the averaging with introducing new data into the recursion, we allow the algorithm to follow an adaptive updating scheme.
-The mixing factor, which balances new data with recursion data, is set adaptively dependent on instantaneous channel estimate norms.
-These introductions reduce inter-node transmissions for each time frame while still delivering steady-state estimation performance close to the optimal case where network-wide information is available at all nodes.
-The reduction that can be achieved goes as far as only needing a single iteration and, therefore, one additional inter-neighborhood information exchange per time frame.
-We show this in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
-\begin{todo}
-    \begin{itemize}
-        \item Scale up simulation (for first setup) to \(M >> N_i\), like M = 50 and neighborhoods like in Toon's paper.
-        \item minor changes to plot labels, legend layouts
-    \end{itemize}
-\end{todo}
-
 \begin{algorithm}[t]
@@
             \dotfill\\
-            Transmit \(\bar{\h}_i^{(n)}\) to nodes  \(j \in \Nset_i\)\;
+            % Transmit \(\bar{\h}_i^{(n)}\) to nodes  \(j \in \Nset_i\)\;
             \(\eta_i^{(n)} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\)\;
@@
 \end{algorithm}
+\autoref{fig:simulations:NPMtime} shows the median of 30 Monte-Carlo runs.
+We can observe that when fixing \(\gamma_i\), a tradeoff between convergence speed and steady-state error arises at low iteration counts (cf. also \autoref{fig:simulations:avgNPMgamma}).
+With \(K=10\), the performance comes close to the optimal case at the cost of additional communication between nodes.
+This in contrast to the case with adaptive \(\gamma_i\) where even at \(K=1\), i.e., no additional communication for the recursive estimation scheme, convergence speed and steady-state error are close to the optimal case.
+
+The second simulation setup is a \(3\)-node ring topology with a neighborhood size of \(|N_i|=2\).
+The input signal, impulse responses, additive noise, and SNR have the same parameters as the first simulation.
+To test the algorithms response to time-variant scenarios, the 3 impulse responses are then scaled to norms of \([2.2, 0.5, 1.2],\, [2.2, 1.0, 1.2],\, [2.2, 0.5, 2.0]\) at frames \(0,\, 5000,\, 10000\) respectively.
+\autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.
+It further shows the damped oscillations that appear in the estimates of \(\|\hat{\h}^{(n)}\|\) around the target value 1 \autoref{fig:simulations:NPMtimedyn} (top) and \(\|\hat{\h}_i^{(n)}\|\) around the rescaled true norms \autoref{fig:simulations:NPMtimedyn} (middle), respectively.
+
+In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case with \(K=1\) distributed averaging iterations.
+Further, introducing an adaptive \(\gamma_i^{(n)}\) allows the algorithm to converge faster and deal with time-variant systems.
+This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017} needing only \(K=1\) instead of \(K=50\) iterations per frame.
+\looseness=-1
+
+\begin{figure}[t]
+    \centering
+    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}\\\vspace*{-1.0cm}
+    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}\\\vspace*{-1.0cm}
+    \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
+    \vspace*{-0.6cm}
+    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^{(n)}\|\) over time, shown is the mean.
+Middle: Estimated \(\|\hat{\h}_i^{(n)}\|\) over time, shown is the mean.
+Dot-dashed lines are true values.
+Bottom: Median NPM, comparing optimal algorithm and proposed extended algorithm.
+Dashed vertical lines indicate rescaling events.}
+    \label{fig:simulations:NPMtimedyn}
+\end{figure}
+\section[]{Conclusions}
+\label{sec:conclusions}
+In this contribution, we propose an extension to a distributed adaptive BSI algorithm applied in sensor networks.
+Based on distributed averaging, only using the information provided by neighboring nodes in the sensor network, we compute estimates of norm values of channel estimates in order to enforce a norm constraint.
+By balancing the averaging with introducing new data into the recursion, we allow the algorithm to follow an adaptive updating scheme.
+The mixing factor, which balances new data with recursion data, is set adaptively dependent on instantaneous channel estimate norms.
+These introductions reduce inter-node transmissions for each time frame while still delivering steady-state estimation performance close to the optimal case where network-wide information is available at all nodes.
+The reduction that can be achieved goes as far as only needing a single iteration and, therefore, one additional inter-neighborhood information exchange per time frame.
+We show this in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
+\begin{todo}
+    \begin{itemize}
+        \item Scale up simulation (for first setup) to \(M >> N_i\), like M = 50 and neighborhoods like in Toon's paper.
+        \item minor changes to plot labels, legend layouts
+        \item cite Bilgesu's paper somewhere :)
+    \end{itemize}
+\end{todo}
 

### 2022-10-21 simulations/dynamic.py
dynamic plot

@@ -277,38 +277,38 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     # Plot
-    mavg = 200
-    styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
-    fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.4))
-    # plt.title("Title")
-    # plt.xlabel("Time [frames]")
-    plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
-    plt.vlines(
-        [5000, 10000],
-        0.75,
-        1.25,
-        colors=["k", "k"],
-        linestyles=["dashed", "dashed"],
-        linewidth=[0.75, 0.75],
-    )
-    (line,) = plt.plot(
-        np.sqrt(data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy()),
-        "-",
-    )
-    # #########
-    # plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
-    plt.grid()
-    plt.ylim(0.75, 1.25)
-    plt.xlim(0, 15000)
-    # plt.tight_layout(pad=0.5)
-    ax = plt.gca()
-    ax.set_xticklabels([])
-    # ax.set_position(box.shrunk(1.0, relative_height))
-    ax.set_position(box)
-    plt.show()
+    # mavg = 200
+    # styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
+    # fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.4))
+    # # plt.title("Title")
+    # # plt.xlabel("Time [frames]")
+    # plt.ylabel(r"$\|\mathbf{h}\|$ [1]")
+    # plt.vlines(
+    #     [5000, 10000],
+    #     0.75,
+    #     1.25,
+    #     colors=["k", "k"],
+    #     linestyles=["dashed", "dashed"],
+    #     linewidth=[0.75, 0.75],
+    # )
+    # (line,) = plt.plot(
+    #     np.sqrt(data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy()),
+    #     "-",
+    # )
+    # # #########
+    # # plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
+    # plt.grid()
+    # plt.ylim(0.75, 1.25)
+    # plt.xlim(0, 15000)
[…]

### 2022-10-21 simulations/dynamic.py
plots

@@ -263,7 +263,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         color=line.get_color(),
         markerfacecolor="none",
     )
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5, loc="upper center")
     plt.grid()
     plt.ylim(-30, 0)
     plt.xlim(0, 15000)

### 2022-10-21 simulations/static.py

@@ -214,7 +214,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     styles = ["-v", "-+", "-x", "-s", "-o", "k-"]
     fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
-    plt.xlabel(r"Mixing factor $\gamma_i$ [1]")
+    plt.xlabel(r"Mixing factor $\gamma_i$")
     plt.ylabel("Avg. NPM [dB]")
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -269,7 +269,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     plt.grid()
     plt.ylim(-40, -20)
     plt.xlim(0, 0.04)
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5, handlelength=1)
     plt.tight_layout(pad=0.5)
     plt.show()
 
@@ -436,7 +436,8 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markerfacecolor="none",
     )
     # #########
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5)
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5,
+        handlelength=1)
     plt.grid()
     plt.ylim(-40, 0)
     plt.xlim(0, 6000)

### 2022-10-21 simulations/static.py
plots

@@ -211,7 +211,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     textwidth = 245
     conv_frames = 500
-    styles = ["-v", "-+", "-x", "-s", "-o", "k-"]
+    styles = ["-v", "-+", "-x", "-s", "--o", "k--"]
     fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma_i$")

### 2022-10-21 simulations/static.py
plots

@@ -211,7 +211,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     textwidth = 245
     conv_frames = 500
-    styles = ["-v", "-+", "-x", "-s", "--o", "k--"]
+    styles = ["-v", "-+", "-x", "-s", "--o", "k-."]
     fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))
     # plt.title(f"SNR={cfg.variables['SNR'][0]}dB")
     plt.xlabel(r"Mixing factor $\gamma_i$")
@@ -436,8 +436,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markerfacecolor="none",
     )
     # #########
-    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5,
-        handlelength=1)
+    plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5, handlelength=1)
     plt.grid()
     plt.ylim(-40, 0)
     plt.xlim(0, 6000)

### 2022-10-21 simulations/dynamic.py
plots

@@ -200,6 +200,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     # Plot
     textwidth = 245
+    linewidth = 1.0
     plt.close("all")
     mavg = 10
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]
@@ -222,6 +223,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(20, 500),
         alpha=0.25,
+        linewidth=linewidth,
     )
     plt.plot(
         20
@@ -238,6 +240,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markevery=(20, 500),
         color=line.get_color(),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     (line,) = plt.plot(
         20 * np.log10(data.median().T["davgad", 0.0, 1][:frames]),
@@ -246,6 +249,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(20, 500),
         alpha=0.25,
+        linewidth=linewidth,
     )
     plt.plot(
         20
@@ -262,6 +266,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markevery=(20, 500),
         color=line.get_color(),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     plt.legend(ncol=2, prop={"size": 7}, columnspacing=0.5, loc="upper center")
     plt.grid()
@@ -328,6 +333,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=r"$\|\hat{\mathbf{h}}_1\|$",
         markersize=4,
         markevery=[2000, 7000, 12000],
+        linewidth=linewidth,
     )
     (line,) = plt.plot(
         np.sqrt(data.mean().T["davgad", 0.0, 1][3 * frames : 4 * frames].to_numpy()),
@@ -335,6 +341,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         label=r"$\|\hat{\mathbf{h}}_2\|$",
         markersize=4,
         markevery=[2500, 7500, 12500],
+        linewidth=linewidth,
     )
     (line,) = plt.plot(
[…]

### 2022-10-21 simulations/static.py

@@ -210,6 +210,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     textwidth = 245
+    linewidth = 1.0
     conv_frames = 500
     styles = ["-v", "-+", "-x", "-s", "--o", "k-."]
     fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))
@@ -226,6 +227,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(1, 2),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -237,6 +239,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(2, 2),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -246,6 +249,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(1, 2),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -255,6 +259,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(2, 2),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     plt.plot(
         cfg.variable_values[2]["gamma"],
@@ -264,6 +269,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(1, 2),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
 
     plt.grid()
@@ -305,6 +311,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=(1, 500),
         alpha=0.25,
+        linewidth=linewidth,
     )
     plt.plot(
         20
@@ -319,6 +326,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markevery=(1, 500),
         color=line.get_color(),
         markerfacecolor="none",
+        linewidth=linewidth,
     )
     # #########
     (line,) = plt.plot(
@@ -328,6 +336,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
[…]

### 2022-10-21 simulations/dynamic.py
plots

@@ -334,6 +334,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=[2000, 7000, 12000],
         linewidth=linewidth,
+        markerfacecolor="none",
     )
     (line,) = plt.plot(
         np.sqrt(data.mean().T["davgad", 0.0, 1][3 * frames : 4 * frames].to_numpy()),
@@ -342,6 +343,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=[2500, 7500, 12500],
         linewidth=linewidth,
+        markerfacecolor="none",
     )
     (line,) = plt.plot(
         np.sqrt(data.mean().T["davgad", 0.0, 1][4 * frames : 5 * frames].to_numpy()),
@@ -350,6 +352,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         markersize=4,
         markevery=[3000, 8000, 13000],
         linewidth=linewidth,
+        markerfacecolor="none",
     )
     (line,) = plt.plot(
         np.sqrt(data.mean().T["davgad", 0.0, 1][frames : 2 * frames].to_numpy()),

### 2022-10-21 simulations/dynamic.py
plots

@@ -200,7 +200,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # %%
     # Plot
     textwidth = 245
-    linewidth = 1.0
+    linewidth = 1.2
     plt.close("all")
     mavg = 10
     styles = ["-+", "-x", "-<", "->", "-v", "-s", "-o", "k-"]

### 2022-10-21 simulations/static.py

@@ -210,7 +210,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
 
     # %%
     textwidth = 245
-    linewidth = 1.0
+    linewidth = 1.2
     conv_frames = 500
     styles = ["-v", "-+", "-x", "-s", "--o", "k-."]
     fig = plt.figure(figsize=utils.set_size(textwidth, 1.0, (1, 1), 0.5))

### 2022-10-21 paper.tex
Included Toon's feedback

--- 2022-10-20 paper.tex
@@
 % ------
-\title{Distributed averaging-based approach to BSI with ADMM}
+\title{Distributed Adaptive Nrom Estimation For Blind System\\Identification in Wireless Sensor Networks}
 %
@@
 Ali\(^1\), F.
-Elvander\(^2\), T.
-van Waterschoot\(^1\),tbd\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
+Elvander\(^2\), tbd, T.
+van Waterschoot\(^1\)\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
 This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No.\,956369.
@@
 \begin{abstract}
-    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce communication cost and computational complexity or avoid reliance on a single device for processing.
-    In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the knowledge of a stacked network-wide solution vector at each node, the computation of which requires either broadcasting or relaying of node-specific values to all other nodes.
-    The extended algorithm employs a distributed-averaging-based estimation scheme to estimate the network-wide norm value by only using the information provided by neighboring sensor nodes.
-    We introduce an adaptive mixing factor between instantaneous and recursion values for adaptivity in a time-varying system.
+    Distributed signal-processing algorithms in (wireless) sensor networks often aim to decentralize processing tasks to reduce communication cost and computational complexity or avoid reliance on a single device (i.e., fusion center) for processing.
+    In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the estimation of a stacked network-wide consensus vector at each node, the computation of which requires either broadcasting or relaying of node-specific values (i.e., local vector norms) to all other nodes.
+    The extended algorithm employs a distributed-averaging-based estimation scheme to estimate the network-wide consensus norm value by only using the local vector norm provided by neighboring sensor nodes.
+    We introduce an adaptive mixing factor between instantaneous and recursive estimates of these norms for adaptivity in a time-varying system.
     Simulation results show that the extension provides estimation results close to the optimal fully-connected-network or broadcasting case while reducing inter-node transmission significantly.
@@
 With the ever-growing number of smart multimedia devices in today's surroundings providing ubiquitous processing and communication capabilities, distributed audio and speech signal processing have also found their way into the spotlight.
-Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154} to name a few, have been proposed.
+Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154,6309434} to name a few, have been proposed.
 Another important task in audio and communication applications, which however has not recived as much attention, is multi-channel system identification, i.e.
-estimating channel responses in time or frequency domain.
-Distributed single-input-multiple-output (SIMO) blind system identification (BSI) had contributions such as the adaptive cross-relation-based (CR) \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
-Furthermore, we recently introduced an adaptive CR-based algorithm \cite{blochbergerDBSI} using the alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011}.
+estimating channel responses in the time or frequency domain.
+Distributed single-input-multiple-output (SIMO) blind system identification (BSI) has been addressed with adaptive cross-relation-based (CR) algorithms \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
+In this context, we recently introduced an adaptive CR-based algorithm \cite{blochbergerDBSI} using the alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011}.
 
@@
 
-In this paper, we extend \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable.
-This approach allows us to compute the global variable without the need of a fully connected network or broadcasting.
+In this paper, we extend the algorithm of \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable.
+This approach allows us, similar to further approaches like \cite{6334305,9914798}, to compute the global variable without the need of a fully connected network or broadcasting.
 We also introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
@@
 \label{sec:dbsi}
-In this section, we briefly outline the adaptive SIMO BSI algorithm proposed in [8], setting the scene for the distributed averaging scheme proposed herein.
-% In this section, we will introduce certain parts of an adaptive SIMO BSI algorithm based on Online-ADMM \cite{blochbergerDBSI}, which are necessary for the reader to understand its extension of it.
+In this section, we briefly outline the adaptive SIMO BSI algorithm proposed in \cite{blochbergerDBSI}, setting the scene for the distributed averaging scheme proposed herein.
 We refer the reader to the publication cited above for the full derivation of the algorithm.
@@
 \subsection[]{Sensor network}
-We assume a set \(\Mset \triangleq \{1,\ldots,M\}\) sensor nodes indices and a set of edge tuples \(\mathcal{E}\), which connect the nodes forming a sensor network.
+We assume a set of nodes with one sensor each, that is, each node provides one signal.
+Let this set of node be \(\Mset \triangleq \{1,\ldots,M\}\) and \(\mathcal{E}\) be a set of edge tuples, which connect the nodes forming a sensor network.
 Each edge is an unordered pair of node indices \(\{i,j\} \in \mathcal{E}\), which represents the communication link between them.
 We allow \(\{i,i\} \in \mathcal{E}\), in order to simplify notation later, however, this does not represent a link but rather indicates the obvious fact that node \(i\) has information of itself.
-Furthermore, let \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\) denote the neighborhood of node \(i\),
-% From this follows the neighborhood of a node \(i\), i.e., the other nodes it is directly connected to, defined as \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\).
-% It is to note, that we define the set with \(i \in \Nset_i\) for ease of notation later.
-% This does however not represent an actual inter-node link.
+Furthermore, let \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\) denote the neighborhood of node \(i\).
 We can define the symmetric adjacency matrix \(\mtxb{C}\) with elements \(C_{ij} = 1\) if \(\{i,j\} \in \mathcal{E}\) and 0 otherwise.
@@
 \end{align}
-the input signal frame and \(M\) output signal frames, respectively.
+the \(2L \times 1\) input signal frame and \(M\) \(L \times 1\)  output signal frames, respectively.
 Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated with \(\mtxb{s}(n)\).
@@
 \subsection[]{Distributed BSI with Online-ADMM}
-In BSI, the coss-relation problem formulation only uses output signals \(\x_i(n)\), exploiting relative information between them, to identify the system, i.e., the acoustic or communication channels \(\h = [\h_1^\T,\,...,\,\h_M^\T]^\T\).
+In BSI, the cross-relation problem formulation only uses output signals \(\x_i(n)\), exploiting relative information between them, to identify the system, i.e., the acoustic or communication channels \(\h = [\h_1^\T,\,...,\,\h_M^\T]^\T\).
 The solution to this problem is found by the minimization problem \cite{langtongBlindIdentificationEqualization1994,huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003,blochbergerDBSI}:
@@
 \end{equation}
-where \(\hat{\h} = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) is the vector of estimated channel responses.
+where \(\hat{\h} = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) is the vector of estimated channel responses and \(\R\) is the so-called cross-relation (CR) matrix.
 In \cite{blochbergerDBSI}, this problem is solved by a distributed adaptive algorithm that is based on separating the problem \eqref{eq:frequency_domain:min_prob} into node-wise subproblems,
@@
 \end{equation}
-Here, each subproblem \(\w_i^\herm \aRhof_i \w_i\), with the node-local estimates \(\w_i\) and data matrix \(\aRhof_i\).
-Both are analogous to \(\h_i\) and \(\R\) in \eqref{eq:frequency_domain:min_prob}, however, only using a subset channels, provided by neighboring nodes \(\Nset_i \subset \Mset\).
+Here, each subproblem is represented by a cost function \(\w_i^\herm \aRhof_i \w_i\), with the node-local channel estimates \(\w_i\) and CR matrix \(\aRhof_i\).
+Both are analogous to \(\h_i\) and \(\R\) in \eqref{eq:frequency_domain:min_prob}, however, only using a subset channels, corresponding to \(\Nset_i \subset \Mset\).
 The first constraint enforces a consensus of local estimates, and \(\mathcal{G}(i,j)\) is a parameter mapping function equating local estimates of nodes connected by edge \((i,j) \in \mathcal{E}\).
-General-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} is applied in an adaptive updating scheme (Online-ADMM) \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
+The general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} is applied in an adaptive updating scheme (Online-ADMM) \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
 ADMM leads to update steps for local, consensus, and dual variables.
@@
 Each node \(i\) computes the respective subvector \(\hat{\h}_i\) locally, which is the computation step of interest for this extension.
-% Separating the cost function and applying general-form consensus ADMM as an adaptive algorithm leads to the update steps
-% \begin{align}
-%     \w_i^{(n+1)} &= \underset{\w_i}{\operatorname{argmin}} \, \mathcal{L}_{\rho} (\w,\h^{(n)},\uu^{(n)})\label{eq:general_consensus_admm:local}\\
-%     \h^{(n+1)} &= \underset{\h, \|\h\| = 1}{\operatorname{argmin}}\, \mathcal{L}_{\rho} (\w^{(n+1)},\h,\uu^{(n)})\label{eq:general_consensus_admm:global}\\
-%     \uu_i^{(n+1)} &= \uu_i^{(n)} + \rho \left( \w_i^{(n+1)} - \tilde{\h}_i^{(n+1)} \right),\label{eq:general_consensus_admm:dual}
-% \end{align}
-% where \(\w_i\) represents channels estimates of lower dimensional subproblems, solved locally by node \(i\), \(\h = [\hat{\h}_1^\T,\,...,\,\hat{\h}_M^\T]^\T\) the consensus variable (estimate of the system), and \(\uu_i\) are the dual variables.
-% \begin{todo}
-%     Is this enough?
-I fear i have to use a full page introducing all the local, consensus, dual variables, parameter mapping and the lagrangian etc.
-only to get to \eqref{eq:online_admm:consensus_update} and say that the denominator is what we are looking at...
-% \end{todo}
 It is defined as
 \begin{equation}
-    \hat{\h_i}^{(n+1)} = \frac{\bar{\h}_i^{(n+1)}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{(n+1)}\|^2}}\label{eq:online_admm:consensus_update}
+    \hat{\h_i}^{(n)} = \frac{\bar{\h}_i^{(n)}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{(n)}\|^2}}\label{eq:online_admm:consensus_update}
 \end{equation}
-for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{(n+1)}\), a combination of neigborhood averages of local estimates and dual variables, see \cite{blochbergerDBSI}.
-The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires  \(\|\bar{\h}_j^{(n+1)}\|\) from all nodes \(j \in \Mset\), which however, is not possible without a fully-connected network or broadcasting.
+for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{(n)}\), a combination of neigborhood averages of local estimates and dual variables, see \cite{blochbergerDBSI}.
+The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires  \(\|\bar{\h}_j^{(n)}\|\) from all nodes \(j \in \Mset\), which however, is not possible without a fully-connected network or broadcasting.
 In \cite{blochbergerDBSI}, we assume that partial squared norms are relayed throughout the network until all nodes have the information necessary.
@@
 
-Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need of network wide data transmission.
+Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need of network-wide data transmission.
 The approach described in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} employs a related iterative averaging scheme within a distributed gradient descent algorithm for BSI in order to estimate a global variable, however, necessitating many iterations per frame.
-So we further introduce an adaptive mixing factor to include instantaneous values in the recursion to separate avaraging iterations onto time frames of the adaptive algorithm.
+To alleviate this, we further introduce an adaptive mixing factor to include instantaneous values in the recursion to separate avaraging iterations onto time frames of the adaptive algorithm.
 
@@
 \subsection[]{Distributed averaging}
-% The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires knowledge of all \(\|\bar{\h}_i\|^2\) at each node \(i \in \Mset\).
-% To avoid the large number of transmissions, which would be necessary to facilitate this, we will approximate the squared norm \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\) at each node \(i\) only using information shared within its neighborhood \(\Nset_i\).
-First, assuming we have some unnormalized consensus variables \(\bar{\h}_i\) for \(i \in \Mset\), we look to distributively compute a sum of their squared norms, \(\sum_{i \in \Mset} \|\bar{\h}_i\|^2\), for \eqref{eq:online_admm:consensus_update} at each node \(i\).
+First, assuming we have some unnormalized consensus variables \(\bar{\h}_i\) for \(i \in \Mset\), we look to distributively compute a sum of their squared norms, \(\sum_{j \in \Mset} \|\bar{\h}_j\|^2\), for \eqref{eq:online_admm:consensus_update} at each node \(i\).
 
 Distributed linear combinations allow us to compute an average in a distributed manner, which makes computing the desired sum straightforward.
-They have the form of
+They generally have the form of
 \begin{equation}
@@
 We want to find the matrix \(\mtxb{W}\), which will ensure that for any initial value \(\bm{\phi}({0})\), each element of \(\bm{\phi}({k})\) converges to the average of the elements of \(\bm{\phi}({0})\) when \(k \to \infty\).
-In this application, the elements of \(\bm{\phi}(0)\) are the initial node-wise squared norm values \(\|\bar{\h}_i\|^2\), of which we want to compute the sum of.
-This leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{i \in \Mset} \|\bar{\h}_i\|^2\) for all \(i \in \Mset\).
+In this application, the elements of \(\bm{\phi}(0)\) are the initial node-wise squared norm values \(\|\bar{\h}_i\|^2\), which we want to compute the sum of.
+This leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{j \in \Mset} \|\bar{\h}_j\|^2\) for all \(i \in \Mset\).
 Computing the desired \(\mtxb{W}\) is done by solving the fastest distributed linear averaging (FDLA) problem, introduced in \cite{xiaoFastLinearIterations2004}, in the form of
@@
 Now, the \(i\)-th row of \(\W\) contains the neigborhood weights for node \(i\) as non-zero entries.
-It is to note that this has to be done only once for any fixed network \(\Mset\) and \(\mathcal{E}\).
-% \begin{todo}
-%     This section reads awkward
-% \end{todo}
-% In usual applications of the iteration \eqref{eq:adaptivenormest:distlincomb}, it is applied \(K \in \mathbb{N}\) times until convergence of the averages is reached.
+It is to note that this has to be done only once for any fixed-topology network \(\Mset\) and \(\mathcal{E}\).
 \subsection[]{Proposed adaptive estimation}
-Given that the BSI algorithm being extended \cite{blochbergerDBSI} is adaptive and the unnormalized consensus estimates \(\bar{\h}_i^{(n)}\) are therefore time-varying, computing a distributed sum of their norms has to be adapted.
+\begin{figure}[t]
+    \centering
+    \input{simulations/plots/icassp2023-static-time/icassp2023-static-time.pgf}
+    \vspace*{-0.6cm}
+    \caption[]{Median NPM of 30 Monte-Carlo runs over time for optimal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
+A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).
+Hatched area indicates frames used in computations for \autoref{fig:simulations:avgNPMgamma}.}
+    \label{fig:simulations:NPMtime}
+\end{figure}
+Given that the BSI algorithm being extended \cite{blochbergerDBSI} is adaptive and the unnormalized consensus estimates \(\bar{\h}_i^{(n)}\) are therefore time-varying, computing a distributed sum of their norms has to be performed adaptively.
 The baseline approach is to compute \(K\) iterations \eqref{eq:adaptivenormest:distlincomb} per frame index \(n\).
-For this iterative approach to converge, \(K\) has to be sufficiently large (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
+For iterative approach to converge, \(K\) has to be sufficiently large (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
 This is suboptimal, as each iteration requires that a node \(i\) shares the averaging variable \(\phi_i(k)\) with its neighborhood \(\Nset_i\).
-Therefore, we first propose to split iterations over time frames, i.e., each \(n\), we set the initial values \(\phi_i^{(n)}(0) = \phi_i^{(n-1)}(K)\), that is, the result of the last iteration of the previous frame.
-This means \(K\) can be chosen small, given that after sufficient frames \(n\), convergence will be reached.
-This rudimentary first modification, however, does not factor in the adaptive approach to channel identification.
-That is, when letting \(\phi_i^{(n)}(0) = \|\bar{\h}_i^{(0)}\|\), with \(\bar{\h}_i^{(0)}\) being estimates at the inital frame \(n=0\), the approach converges to the sum of these inital - bad - estimates.
-Therefore we factor in the instantaneous approximation, the weighted in-neighborhood sum \(\eta_i^{(n)} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\).
-This leads to
+Therefore, we first propose to split iterations over time frames.
+Each \(n\), we could set the initial values \(\phi_i^{(n)}(0)\) to the result of the \(K\)-th iteration \(\phi_i^{(n-1)}(K)\) of the previous frame \(n-1\).
+With sufficiently large \(n\), convergence will be reached even when \(K\) is chosen small.
+However, this rudimentary modification does not factor in the adaptive approach to channel identification.
+That is, when letting \(\phi_i^{(0)}(0) = \|\bar{\h}_i^{(0)}\|\), with \(\bar{\h}_i^{(0)}\) being estimates at the inital frame \(n=0\), it converges to the sum of these initial - bad - estimates.
+Therefore, we factor in the instantaneous approximation, the weighted in-neighborhood sum \(\eta_i^{(n)} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\), which will introduce new information gained by more accurate estimates of \(\bar{\h}_i^{(n)}\).
+We add this information by linearly combining it with the \(K\)-th iterate of \(\phi_i^{(n)}(k)\) and set it as the initial value for the next frame:
 \begin{equation}
-    \hat{\phi}_i^{(n+1)} = \gamma_i \eta_i^{(n)} + (1-\gamma_i) \phi_i^{(n)}(K),
+    \phi_i^{(n)}(0) = \gamma_i \eta_i^{(n)} + (1-\gamma_i) \phi_i^{(n-1)}(K),
 \end{equation}
@@
 The initial value for \(\eta_i^{(n-1)}\) for \(n=0\) can be set to an arbitrary real number, in our case 1.
-% The combination of instantaneous values and distributed averaging estimate should lead to lower steady-state error when \(\gamma_i\) is chosen right, while with adaptive \(\gamma_i\), convergence speed should increase as well.
-Refer to \autoref{alg:davg_norm_est} for the extended algorithm introduced in this section.
-
-% \section{Transmission cost}
+Refer to \autoref{alg:davg_norm_est} for the order of computations of the extended algorithm we introduced here.
 
@@
 \label{sec:simulations}
+\begin{figure}[t]
+    \centering
+    \input{simulations/plots/icassp2023-static/icassp2023-static.pgf}
+    \vspace*{-0.6cm}
+    \caption[]{Mean of 500 post-convergence frames of median NPM of 30 Monte-Carlo runs for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
+Results for optimal algorithm, and adaptive \(\gamma_i\) included for comparison.}
+    \label{fig:simulations:avgNPMgamma}
+\end{figure}
 \subsection[]{Communication cost}
 \label{sec:transcost}
-% \renewcommand{\arraystretch}{1.2}
-% \begin{table}[t]
-%     \centering
-%     \begin{tabular}{ |l|l| } 
-%         \hline
-%         & Cost \\
-%         \hline\hline
-%         (1) Fully connected & \(\mathcal{O}(M)\) \\
-%         \hline
-%         (2) Broadcast & \(\mathcal{O}(M)\) \\ 
-%         \hline
-%         (2) Neighborhood & \(\mathcal{O}(\bar{N}_i K)\) \\ 
-%         \hline
-%     \end{tabular}
-%     \caption[]{Comparison of communication cost.}
-%     \label{tab:transcost:table}
-% \end{table}
-% \renewcommand{\arraystretch}{1.0}
 To describe the communication cost within the network, we count the number of variables transmitted per time frame \(n\).
 The most useful measure in the case of this work is to analyze the cost per node.
-% For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
 We compare the following communication schemes within the context of the algorithm \cite{blochbergerDBSI} this paper proposes the extension to:
@@
     \item[(1)] A fully-connected network, where node \(i\) communicates \(\|\bar{\h}_i\|^2\) to all other nodes \(\{j \in \Nset_i = \Mset\}\) directly, i.e., the neighborhood is the full network.
-    % \item[(2)] The node \(i\) broadcasts \(\|\bar{\h}_i\|\), i.e., it transmits to all other nodes \(\{j \in \Mset \setminus i\}\) without direct links.
     \item[(2)] The node \(i\) communicates \(\|\bar{\h}_i\|^2\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset\}\) and applies \(K\) distributed averaging iterations.
@@
 Further, it shows the complexity of the problem a node \(i\) has to solve according to \cite{blochbergerDBSI} given the two types of network topology, assuming it uses all information it receives.
-The advantage of the fully distributed algorithm becomes clear when \(M>>N_i\), as the additional communication and local complexity depends on neighborhood size \(N_i\) and not on network size \(M\).
-% In this comparison, we only consider communication necessary for the computation of \eqref{eq:online_admm:consensus_update} as the rest of the algorithm is the same for our options.
-% For (1), the cost per node increases linearly with network size \(M\), whereas for communication scheme (2), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only and therefore independent of network size.
-% The problem to be solved at each node \(i \in \Mset\) has complexity \(\mathcal{O}(M^2 L^2)\) for (1), with channel response length \(L\) (which means there is no reduction compared to a centralized approach).
-% For (2), local complexity is \(\mathcal{O}(N_i^2 L^2)\), where \(N_i\) is the neighborhood size.
+The advantage of the fully distributed algorithm becomes clear when \(M \gg N_i\), as the additional communication and local complexity depends on neighborhood size \(N_i\) and not on network size \(M\).
 \vspace*{-0.6em}
@@
         \hline
-        % (2) Broadcast & \(1\) & \(M-1\) & \(\mathcal{O}(N_i^2 L^2)\)  \\ 
-        % \hline
         (2) Neighborh. & \(N_i K\) & \(N_i K\) & \(\mathcal{O}(N_i^2 L^2)\)\\ 
@@
     \end{tabular}
-    % \caption[]{Comparison of communication cost (transmission operations \& receive operations) and local problem complexity for a node \(i\) within the network.
-\(M\) is the number of nodes within the network, \(N_i\) is the number neighboring nodes, \(L\) is the lenght of channel responses, \(K\) is the number of distributed averaging iterations.}
     \caption[]{Communication cost per node and frame \(n\) for computation of \eqref{eq:online_admm:consensus_update}.}
@@
 \renewcommand{\arraystretch}{1.0}
-% To describe the communication cost within the network, we adopt the Big-\(\mathcal{O}\) notation, similar to the complexity analysis of algorithms.
-% We consider the communication of a variable from one node to another as \(\mathcal{O}(1)\).
-% The most useful measure in the case of this work is to analyze the cost per node.
-% For this we define an average neighborhood size \(\bar{N}_i = \frac{1}{M} \sum_{i \in \Mset} N_i\) where \(N_i = | \Nset_i |\) is the cardinality/size of the neigborhood set for node \(i\).
-% We compare the following communication schemes:
-% \begin{itemize}
-%     \itemsep-0.2em
-%     \item[(1)] A fully connected network, i.e., all nodes are linked with all other nodes by direct links, \(\Nset_i = \Mset\).
-%     \item[(2)] The nodes employ broadcasting, i.e., the nodes transmit to all other nodes without direct links.
-%     \item[(2)] The nodes only communicate with neighboring nodes, \(\Nset_i \subset \Mset\).
-% \end{itemize}
-% For (1) and (2), the cost per node increases linearly with network size \(M\): \(\mathcal{O}(M)\).
-% Using communication scheme (2), as in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} and proposed as an extension to \cite{blochbergerDBSI} in this paper, cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only: \(\mathcal{O}(\bar{N}_i K)\).
-% \begin{todo}
-%     Unsure, about this.
-Filips feedback: "Don't you want the complexity for the whole system here so that you can compare things?
-That us write the complexity for the fully connected system as well as the distributed systems, parametrized in such away that the reader can compare the two.
-Here, the reader sees \(M\) and \(\bar{N}_i,K\) and has no idea of how they relate to each other."\\
-%     But this shows how the communication cost as defined here goes from \(\mathcal{O}(M)\) to \(\mathcal{O}(\bar{N}_i K)\).\\
-%     Other option: not just communication cost: fully connected \(\mathcal{O}(M^2 L^2)\), broadcast \(\)
-% \end{todo}
-% Refer to \autoref{tab:transcost:table} for the collected orders of communication cost.
-% \begin{figure}[t]
-%     \centering
-%     \input{simulations/plots/transcostnode/transcostnode.pgf}
-%     % \vspace*{-0.8cm}
-%     \caption[]{A graphical representation of the order of transmission cost of a single node within the network dependent on network size.
-One can observe that for the neigborhood-only communication scheme, cost stays constant.
-(This plot might be unnecessary and space consuming)}
-%     \label{fig:transcost:bigo}
-% \end{figure}
 
 \subsection[]{Simulations}
-\begin{figure}[t]
-    \centering
-    \input{simulations/plots/icassp2023-static-time/icassp2023-static-time.pgf}
-    \vspace*{-0.6cm}
-    \caption[]{Median NPM of 30 Monte-Carlo runs over time for optimal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
-A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).
-Hatched area indicates frames used in computations for \autoref{fig:simulations:avgNPMgamma}.}
-    \label{fig:simulations:NPMtime}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \input{simulations/plots/icassp2023-static/icassp2023-static.pgf}
-    \vspace*{-0.6cm}
-    \caption[]{Mean of 500 post-convergence frames of median NPM of 30 Monte-Carlo runs for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
-Results for optimal algorithm, and adaptive \(\gamma_i\) included for comparison.
-Hatched area in \autoref{fig:simulations:NPMtime} indicates frames used for computation of mean NPM.}
-    \label{fig:simulations:avgNPMgamma}
-\end{figure}
 To evaluate the effectiveness of the proposed extension, simulations were run, where we define the error measure as the normalized projection misalignment
@@
     \begin{aligned}
-        \text{NPM}(n) &= 20\,\log_{10} \frac{\left\| \mtxb{e} \right\|}{\left\|\hat{\h}(n)\right\|},\\
-        \text{with}\quad \mtxb{e} &= \hat{\h}(n) - \frac{\hat{\h}^\T (n) \h}{\h^\T \h}\hat{\h}(n),
+        \text{NPM}(n) &= 20\,\log_{10} \frac{\left\| \mtxb{e} \right\|}{\left\|\hat{\h}^{(n)}\right\|},\\
+        \text{with}\quad \mtxb{e} &= \hat{\h}^{(n)} - \frac{\h^\T \hat{\h}^{(n)}}{\h^\T \h}\hat{\h}^{(n)},
     \end{aligned}
 \end{equation}
-commonly used in BSI to compare estimated \(\hat{\h}(n)\) and true \(\h\).
+commonly used in BSI to compare the estimated \(\hat{\h}^{(n)}\) and true \(\h\).
 
@@
 \end{itemize}
+\begin{algorithm}[t]
+    \caption{ADMM BSI with distributed-averaging-based adaptive estimation of norm values}\label{alg:davg_norm_est}
+    \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
+    \(\eta_i^{(n-1)} \gets 1, \forall i \in \Mset\)\;
+    \For(){\(n=0\dots\)}
+    {
+        \For(){\(i \in \Mset\)}
+        {
+            \emph{The steps before are as introduced in }\cite{blochbergerDBSI}\\
+            \dotfill\\
+            \(\eta_i^{(n)} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\)\;
+            \(\gamma_i^{(n)} \gets \min \left\lbrace \frac{| \eta_i^{(n)} - \eta_i^{(n-1)} |}{\eta_i^{(n-1)}},\,1\right\rbrace\)\;
+            \eIf(){\(n = 0\)}
+            {
+                \(\phi_i^{(0)}(0) \gets \|\bar{\h}_i^{(0)}\|^2\)\;
+            }
+            {
+                \(\phi_i^{(n)}(0) \gets \gamma_i^{(n)} \eta_i^{(n)} + (1-\gamma_i^{(n)}) \phi_i^{(n-1)}(K)\)\;
+            }
+            \For(){\(k=0,\dots,K\)}
+            {
+                Transmit \(\phi_i^{(n)}(k)\) to nodes  \(j \in \Nset_i\)\;
+                \(\phi_i^{(n)}({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j^{(n)}({k})\)\;
+            }
+            \(\hat{\h_i}^{(n)} \gets \frac{\bar{\h}_i^{(n)}}{\sqrt{M \phi_i^{(n)}(K)}}\)\;
+            \dotfill\\
+            \emph{The steps after are as introduced in }\cite{blochbergerDBSI}\\
+        }
+    }
+\end{algorithm}
 \autoref{fig:simulations:NPMtime} shows the median of 30 Monte-Carlo runs.
@@
 \autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.
-It further shows the damped oscillations that appear in the estimates of \(\|\hat{\h}^{(n)}\|\) around the target value 1 \autoref{fig:simulations:NPMtimedyn} (top) and \(\|\hat{\h}_i^{(n)}\|\) around the rescaled true norms \autoref{fig:simulations:NPMtimedyn} (middle), respectively.
+It further shows the damped oscillations that appear in the estimates of \(\|\hat{\h}^{(n)}\|\) around the desired value 1 and \(\|\hat{\h}_i^{(n)}\|\) around the rescaled true norms in \autoref{fig:simulations:NPMtimedyn} (top), respectively.
 
-In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case with \(K=1\) distributed averaging iterations.
+In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case even with \(K=1\) distributed averaging iterations.
 Further, introducing an adaptive \(\gamma_i^{(n)}\) allows the algorithm to converge faster and deal with time-variant systems.
-This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{liuDistributedBlindIdentification2016,liuDistributedRecursiveBlind2017} needing only \(K=1\) instead of \(K=50\) iterations.
+This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} needing only \(K=1\) instead of \(K=50\) iterations per frame.
 
@@
     \centering
-    \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}\\\vspace*{-1.0cm}
-    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}\\\vspace*{-1.0cm}
+    % \input{simulations/plots/icassp2023-dynamic-norm/icassp2023-dynamic-norm.pgf}\\\vspace*{-1.0cm}
+    \input{simulations/plots/icassp2023-dynamic-norms/icassp2023-dynamic-norms.pgf}\\\vspace*{-1.2cm}
     \input{simulations/plots/icassp2023-dynamic-time/icassp2023-dynamic-time.pgf}
     \vspace*{-0.6cm}
-    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^{(n)}\|\) over time, shown is the mean.
-Middle: Estimated \(\|\hat{\h}_i^{(n)}\|\) over time, shown is the mean.
+    \caption[]{Results of 30 Monte-Carlo runs: Top: Estimated \(\|\h^{(n)}\|\), \(\|\hat{\h}_i^{(n)}\|\) over time, shown is the mean.
 Dot-dashed lines are true values.
@@
 \end{figure}
-
 \section[]{Conclusions}
@@
 The reduction that can be achieved goes as far as only needing a single iteration and, therefore, one additional inter-neighborhood information exchange per time frame.
-We show this in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
-\begin{todo}
-    \begin{itemize}
-        \item Scale up simulation (for first setup) to \(M >> N_i\), like M = 50 and neighborhoods like in Toon's paper.
-        \item minor changes to plot labels, legend layouts
-    \end{itemize}
-\end{todo}
-
-\begin{algorithm}[t]
-    \caption{ADMM BSI with distributed-averaging-based adaptive estimation of norm values}\label{alg:davg_norm_est}
-    \(\W \gets\) \eqref{eq:adaptivenormest:fdlaminprob}\;
-    \(\eta_i^{(n-1)} \gets 1, \forall i \in \Mset\)\;
-    \For(){\(n=0\dots\)}
-    {
-        \For(){\(i \in \Mset\)}
-        {
-            % \(\cdots\)\\
-            % \(\w_i^{(n)} \gets \operatorname{argmin}_{\w_i}\, \mathcal{L}_{\rho} (\w,\h^{(n)},\uu^{(n)})\)\;
-            % Compute \(\bar{\h}_i^{(n)}\)\;
-            % \(\cdots\)\\
-            \emph{The steps before are as introduced in }\cite{blochbergerDBSI}\\
-            \dotfill\\
-            Transmit \(\bar{\h}_i^{(n)}\) to nodes  \(j \in \Nset_i\)\;
-            \(\eta_i^{(n)} \gets \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\)\;
-            \(\gamma_i^{(n)} \gets \min \left\lbrace \frac{| \eta_i^{(n)} - \eta_i^{(n-1)} |}{\eta_i^{(n-1)}},\,1\right\rbrace\)\;
-            \eIf(){\(n = 0\)}
-            {
-                \(\phi_i^{(n)}(1) \gets \|\bar{\h}_i^{(n)}\|^2\)\;
-            }
-            {
-                \(\phi_i^{(n)}(1) \gets \hat{\phi}_i^{(n-1)}(K)\)\;
-            }
-            \For(){\(k=0,\dots,K\)}
-            {
-                Transmit \(\phi_i^{(n)}(k)\) to nodes  \(j \in \Nset_i\)\;
-                \(\phi_i^{(n)}({k+1}) \gets \sum_{j \in \Nset_i} W_{ij} \phi_j^{(n)}({k})\)\;
-            }
-            \(\hat{\phi}_i^{(n)} \gets \gamma_i \eta_i^{(n)} + (1-\gamma) \phi_i^{(n)}(K)\)\;
-            \(\hat{\h_i}^{(n)} \gets \frac{\bar{\h}_i^{(n)}}{\sqrt{\hat{\phi}_i^{(n)}M}}\)\;
-            \dotfill\\
-            \emph{The steps after are as introduced in }\cite{blochbergerDBSI}\\
-            % \(\cdots\)\\
-            % \(\uu_i^{(n)} \gets \uu_i^{(n-1)} + \rho \left( \w_i^{(n)} - \tilde{\h}_i^{(n)} \right)\)\;
-            % \(\cdots\)\\
-            % % \,\\
-        }
-    }
-\end{algorithm}
+We illustrate the performance in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
+% \begin{todo}
+%     \begin{itemize}
+%         \item Scale up simulation (for first setup) to \(M >> N_i\), like M = 50 and neighborhoods like in Toon's paper.
+%     \end{itemize}
+% \end{todo}
 
@@
 \bibliographystyle{IEEEbib}
-\bibliography{refs}
+\bibliography{bib_abbrev,refs}
 

### 2022-10-21 paper.tex
Included Toon's feedback

@@
 % ------
-\title{Distributed Adaptive Nrom Estimation For Blind System\\Identification in Wireless Sensor Networks}
+\title{Distributed Adaptive Norm Estimation For Blind System\\Identification in Wireless Sensor Networks}
 %
@@
 Ali\(^1\), F.
-Elvander\(^2\), tbd, T.
+Elvander\(^2\), M.
+Moonen\(^1\), tbd, T.
 van Waterschoot\(^1\)\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
@@
     In this contribution, we extend a distributed adaptive algorithm for blind system identification that relies on the estimation of a stacked network-wide consensus vector at each node, the computation of which requires either broadcasting or relaying of node-specific values (i.e., local vector norms) to all other nodes.
-    The extended algorithm employs a distributed-averaging-based estimation scheme to estimate the network-wide consensus norm value by only using the local vector norm provided by neighboring sensor nodes.
+    The extended algorithm employs a distributed-averaging-based scheme to estimate the network-wide consensus norm value by only using the local vector norm provided by neighboring sensor nodes.
     We introduce an adaptive mixing factor between instantaneous and recursive estimates of these norms for adaptivity in a time-varying system.

### 2022-10-24 paper.tex
Jan's comments

@@
 \name{M.
-Blochberger\(^1\), R.
-Ali\(^1\), F.
-Elvander\(^2\), M.
-Moonen\(^1\), tbd, T.
+Blochberger\(^1\), F.
+Elvander\(^2\), R.
+Ali\(^1\), J.
+Østergaard\(^3\), J.
+Jensen\(^3\),  M.
+Moonen\(^1\), T.
 van Waterschoot\(^1\)\thanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network.
@@
 Source code available at \textcolor{red}{ADD URL}}}
-\address{\(^1\)KU Leuven, Dept. of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept. of Signal Processing and Acoustics, 02150 Espoo, Finland\\tbd}
+\address{\(^1\)KU Leuven, Dept.
+of Electrical Engineering (ESAT), STADIUS, 3001 Leuven, Belgium\\\(^2\)Aalto University, Dept.
+of Signal Processing and Acoustics, 02150 Espoo, Finland\\\(^3\)Aalborg University, Dept.
+of Electronic Systems, 9220 Aalborg, Denmark}
 
@@
 
-In this paper, we extend the algorithm of \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable.
-This approach allows us, similar to further approaches like \cite{6334305,9914798}, to compute the global variable without the need of a fully connected network or broadcasting.
-We also introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (down to 1) and (ii) track time-varying systems.
+In this paper, we extend our algorithm in \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable.
+This approach allows us, similarly to \cite{6334305,9914798}, to compute the global variable without the need of a fully connected network or broadcasting.
+We also introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (from 50 in existing approaches, down to 1) and (ii) track time-varying systems.
 Simulation results demonstrate how the extension leads to BSI performance close to an optimal case where all information is available without the need of a fully connected network or a large number of estimation iterations.
@@
 We assume a set of nodes with one sensor each, that is, each node provides one signal.
-Let this set of node be \(\Mset \triangleq \{1,\ldots,M\}\) and \(\mathcal{E}\) be a set of edge tuples, which connect the nodes forming a sensor network.
+Let this set of nodes be \(\Mset \triangleq \{1,\ldots,M\}\) and \(\mathcal{E}\) be a set of edge tuples, which connect the nodes forming a sensor network.
 Each edge is an unordered pair of node indices \(\{i,j\} \in \mathcal{E}\), which represents the communication link between them.
-We allow \(\{i,i\} \in \mathcal{E}\), in order to simplify notation later, however, this does not represent a link but rather indicates the obvious fact that node \(i\) has information of itself.
+We allow \(\{i,i\} \in \mathcal{E}\), in order to simplify notation later, however, this does not represent a link but rather indicates the obvious fact that node \(i\) has information about itself.
 Furthermore, let \(\Nset_i = \{j|\{i,j\} \in \mathcal{E}\}\) denote the neighborhood of node \(i\).
@@
 Each output \(\x_i(n)\) is the convolution of \(\mtxb{s}(n)\) with the respective channel impulse response \(\h_i\) and an additive noise term \(\mtxb{v}_i(n)\), assumed to be zero-mean and uncorrelated with \(\mtxb{s}(n)\).
-The signal model is \(\x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n),\)
+The signal model is
+\begin{equation}
+    \x_i(n) = \mtxb{H}_i \mtxb{s}(n) + \mtxb{v}_i(n),
+\end{equation}
 with \(\mtxb{H}_i\), the \(L \times (2L-1)\) linear convolution matrix of the \(i\)th channel using the elements of \(\h_i\) of length \(L\).
@@
         \hat{\h} = \arg \min_{\h} \quad &\h^\herm \R \h \\
-        \text{s.t. } \quad &\|\h\| = 1.
+        \text{s.t. } \quad &\|\h\| = 1,
     \end{aligned}\label{eq:frequency_domain:min_prob}
@@
 Here, each subproblem is represented by a cost function \(\w_i^\herm \aRhof_i \w_i\), with the node-local channel estimates \(\w_i\) and CR matrix \(\aRhof_i\).
-Both are analogous to \(\h_i\) and \(\R\) in \eqref{eq:frequency_domain:min_prob}, however, only using a subset channels, corresponding to \(\Nset_i \subset \Mset\).
-The first constraint enforces a consensus of local estimates, and \(\mathcal{G}(i,j)\) is a parameter mapping function equating local estimates of nodes connected by edge \((i,j) \in \mathcal{E}\).
+Both are analogous to \(\h_i\) and \(\R\) in \eqref{eq:frequency_domain:min_prob}, however, only using a subset of channels, corresponding to \(\Nset_i \subset \Mset\).
+The first constraint enforces a consensus of local estimates, and \(\mathcal{G}(i,j)\) is a map equating local estimates of nodes connected by edge \((i,j) \in \mathcal{E}\).
 The general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} is applied in an adaptive updating scheme (Online-ADMM) \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.
@@
 In this application, the elements of \(\bm{\phi}(0)\) are the initial node-wise squared norm values \(\|\bar{\h}_i\|^2\), which we want to compute the sum of.
-This leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{j \in \Mset} \|\bar{\h}_j\|^2\) for all \(i \in \Mset\).
+This leads to \(\lim_{k \to \infty} M \phi_i(k) = \sum_{j \in \Mset} \|\bar{\h}_j\|^2\) for all \(i \in \Mset\), \cite{xiaoFastLinearIterations2004}.
 Computing the desired \(\mtxb{W}\) is done by solving the fastest distributed linear averaging (FDLA) problem, introduced in \cite{xiaoFastLinearIterations2004}, in the form of
@@
 The baseline approach is to compute \(K\) iterations \eqref{eq:adaptivenormest:distlincomb} per frame index \(n\).
-For iterative approach to converge, \(K\) has to be sufficiently large (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
-This is suboptimal, as each iteration requires that a node \(i\) shares the averaging variable \(\phi_i(k)\) with its neighborhood \(\Nset_i\).
+For the baseline iterative approach to converge, \(K\) has to be sufficiently large (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
+This is suboptimal in terms of communication cost, as each iteration requires that a node \(i\) shares the averaging variable \(\phi_i(k)\) with its neighborhood \(\Nset_i\).
 Therefore, we first propose to split iterations over time frames.
-Each \(n\), we could set the initial values \(\phi_i^{(n)}(0)\) to the result of the \(K\)-th iteration \(\phi_i^{(n-1)}(K)\) of the previous frame \(n-1\).
+For each \(n\), we could set the initial values \(\phi_i^{(n)}(0)\) to the result of the \(K\)-th iteration \(\phi_i^{(n-1)}(K)\) of the previous frame \(n-1\).
 With sufficiently large \(n\), convergence will be reached even when \(K\) is chosen small.
 However, this rudimentary modification does not factor in the adaptive approach to channel identification.
-That is, when letting \(\phi_i^{(0)}(0) = \|\bar{\h}_i^{(0)}\|\), with \(\bar{\h}_i^{(0)}\) being estimates at the inital frame \(n=0\), it converges to the sum of these initial - bad - estimates.
+That is, when letting \(\phi_i^{(0)}(0) = \|\bar{\h}_i^{(0)}\|\), with \(\bar{\h}_i^{(0)}\) being estimated at the inital frame \(n=0\), it converges to the sum of these initial - poor - estimates.
 Therefore, we factor in the instantaneous approximation, the weighted in-neighborhood sum \(\eta_i^{(n)} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\), which will introduce new information gained by more accurate estimates of \(\bar{\h}_i^{(n)}\).
@@
 \end{itemize}
-\autoref{tab:transcost:table} compares the number of transmit and receive operations a node \(i\) has to apply in order to compute \eqref{eq:online_admm:consensus_update}.
-Further, it shows the complexity of the problem a node \(i\) has to solve according to \cite{blochbergerDBSI} given the two types of network topology, assuming it uses all information it receives.
+\autoref{tab:transcost:table} compares the number of transmit and receive operations node \(i\) has to apply in order to compute \eqref{eq:online_admm:consensus_update}.
+Further, it shows the complexity of the problem node \(i\) has to solve according to \cite{blochbergerDBSI} given the two types of network topology, assuming it uses all information it receives.
 The advantage of the fully distributed algorithm becomes clear when \(M \gg N_i\), as the additional communication and local complexity depends on neighborhood size \(N_i\) and not on network size \(M\).
@@
 
-The first simulation setup is a network with \(M=5\) nodes arranged in a ring topology, each node having \(|N_i|=2\) neighbors.
+The first simulation setup is a network with \(M=5\) nodes arranged in a ring topology, each node having \(N_i=3\) neighbors (including node \(i\)).
 The input signal is zero-mean white Gaussian noise (WGN), the impulse responses of length \(L=16\) are drawn from a normal distribution, and at each channel, independent WGN is added with \(\text{SNR}=10\,\text{dB}\).
@@
 
-The second simulation setup is a \(3\)-node ring topology with a neighborhood size of \(|N_i|=2\).
+The second simulation setup is a \(3\)-node ring topology with a neighborhood size of \(N_i=2\) (including node \(i\)).
 The input signal, impulse responses, additive noise, and SNR have the same parameters as the first simulation.
-To test the algorithms response to time-variant scenarios, the 3 impulse responses are then scaled to norms of \([2.2, 0.5, 1.2],\, [2.2, 1.0, 1.2],\, [2.2, 0.5, 2.0]\) at frames \(0,\, 5000,\, 10000\) respectively.
+To test the algorithms response to time-varying scenarios, the 3 impulse responses are then scaled to norms of \([2.2, 0.5, 1.2],\, [2.2, 1.0, 1.2],\, [2.2, 0.5, 2.0]\) at frames \(0,\, 5000,\, 10000\) respectively.
 \autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.

### 2022-10-25 simulations/admm_fq_distavg_ad.py
new plots, change optimal to ideal

@@ -411,7 +411,7 @@ class Network:
         delta_norm_inst = np.abs(self.norm_inst - norm_inst)
         # gamma_ad = delta_norm_inst / self.norm_inst
 
-        gamma_ad = np.clip(delta_norm_inst / self.norm_inst, 0.0, 1)
+        gamma_ad = np.clip(delta_norm_inst / self.norm_inst, self.gamma, 1)
 
         self.gamma_ad.append(gamma_ad)
 

### 2022-10-25 simulations/dynamic.py

@@ -219,7 +219,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     (line,) = plt.plot(
         20 * np.log10(data.median().T["opt", 0.0, 1][:frames]),
         "k-",
-        label=rf"_optimal",
+        label=rf"_ideal",
         markersize=4,
         markevery=(20, 500),
         alpha=0.25,
@@ -235,7 +235,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
             )
         ),
         "-",
-        label=rf"optimal",
+        label=rf"ideal",
         markersize=4,
         markevery=(20, 500),
         color=line.get_color(),

### 2022-10-25 simulations/static.py

@@ -223,7 +223,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
         * np.log10(data.median().T.tail(conv_frames).mean()["opt", 1.0, 1])
         * np.ones_like(cfg.variable_values[2]["gamma"]),
         styles.pop(),
-        label=f"optimal",
+        label=f"ideal",
         markersize=4,
         markevery=(1, 2),
         markerfacecolor="none",
@@ -307,7 +307,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     (line,) = plt.plot(
         20 * np.log10(data.median().T["opt", 1.0, 1]),
         "k-",
-        label=f"_optimal",
+        label=f"_ideal",
         markersize=4,
         markevery=(1, 500),
         alpha=0.25,
@@ -321,7 +321,7 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
             )
         ),
         "-",
-        label=f"optimal",
+        label=f"ideal",
         markersize=4,
         markevery=(1, 500),
         color=line.get_color(),

### 2022-10-25 simulations/static_large.py

@@ -1,0 +1,480 @@
+# %%
+import os
+import pandas as pd
+import numpy as np
+
+# import matplotlib.pyplot as plt
+import python_utils.utils as utils
+import python_utils.simulation as simulation
+
+# %%
+# import matplotlib
+# import matplotlib.pyplot as plt
+
+# # %%
+# import matplotlib
+
+# matplotlib.use("pgf")
+# import matplotlib.pyplot as plt
+
+# plt.rcParams.update(
+#     {
+#         "font.family": "serif",  # use serif/main font for text elements
+#         "text.usetex": True,  # use inline math for ticks
+#         "pgf.rcfonts": False,  # don't setup fonts from rc parameters
+#         "font.size": 9,
+#     }
+# )
+
+
+# %%
+# Define the simulation function.
+# You can define any number of arguments instead of a, b.
+# Remember to add them in SimConfig
+# DO NOT CHANGE run and seed arguments and argument positions!
+def simulate(alg, SNR, gamma, iters, run: int, seed: int):
+    ## %%
+    # All required imports for simulation need to be in here, e.g.,
+    import numpy as np
+
+    if alg == "opt":
+        import admm_fq as adf
+    if alg == "davg":
+        import admm_fq_distavg_opt as adf
+    if alg == "davgad":
+        import admm_fq_distavg_ad as adf
+    from cvxpy import Variable, sum_squares, Minimize, Problem, vec
+
+    rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
+    ## %%
+    # ################################################################
+    # Put the simulation code here
+    N_sens = 20
+    L = 16
+
+    nw = adf.Network(L)
+
+    next_pos = np.array([0, 0])
+    node_pos = np.empty((N_sens, 2))
+    # fig = plt.figure(figsize=(8, 8))
+    nbs = []
+    ok = []
+    edges = []
+    radius = 2
+    for i in range(N_sens):
+        nw.addNode(i, 1)
+        rangle = rng.uniform(-np.pi / 4, np.pi / 4) + rng.integers(0, 2) * np.pi
+        # print(rangle)
+        # rd = rng.uniform(0.8 * radius, 0.99*radius)
+        rd = radius * 0.95
[…]

### 2022-10-25 paper.tex
Jesper's comments

@@
 Algorithms for distributed signal estimation \cite{5483092}, noise control and echo cancellation \cite{9670697}, as well as beamforming \cite{6663655,6329934,MARKOVICHGOLAN20154,6309434} to name a few, have been proposed.
-Another important task in audio and communication applications, which however has not recived as much attention, is multi-channel system identification, i.e.
-estimating channel responses in the time or frequency domain.
+Another essential task in audio and communication applications, which has received less attention, is multi-channel system identification, i.e., estimating channel responses in the time or frequency domain.
 Distributed single-input-multiple-output (SIMO) blind system identification (BSI) has been addressed with adaptive cross-relation-based (CR) algorithms \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016}.
@@
 
-All of the aforementioned distributed BSI algorithms rely on shared information between neighboring sensor nodes within the network.
-However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to, e.g., \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003}), which manifests itself as one or more variables that require network-wide shared information for their computation.
+The aforementioned distributed BSI algorithms rely on shared information between neighboring sensor nodes within the network.
+However, the CR-based BSI task necessitates a non-triviality constraint on the full system to be identified (we refer the reader to, e.g., \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003} for details), which manifests itself as one or more variables that require network-wide shared information for their computation.
 The algorithm in \cite{blochbergerDBSI} relies on node-wise values being relayed throughout the network.
 In contrast, to overcome the need for the network to be fully connected, \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} use an average consensus \cite{xiaoFastLinearIterations2004} approach where a secondary recursion estimates the global variable for each signal frame.
-Both approaches introduce additional transmissions of variables between nodes, the number of which, depending on network and neighborhood size, can be substantial or even unfeasable.
+Both approaches introduce additional transmissions of variables between nodes, the number of which, depending on network and neighborhood size, can be substantial or even unfeasible depending on the application.
 
 In this paper, we extend our algorithm in \cite{blochbergerDBSI} with a distributed averaging-based \cite{xiaoFastLinearIterations2004} estimation scheme for the global variable.
-This approach allows us, similarly to \cite{6334305,9914798}, to compute the global variable without the need of a fully connected network or broadcasting.
-We also introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (from 50 in existing approaches, down to 1) and (ii) track time-varying systems.
-Simulation results demonstrate how the extension leads to BSI performance close to an optimal case where all information is available without the need of a fully connected network or a large number of estimation iterations.
+This approach allows us, similarly to \cite{6334305,9914798}, to compute the global variable without needing a fully connected network or broadcasting.
+We also introduce a mixing factor to include instantaneous values into the averaging recursion, which then allows us (i) to reduce the number of secondary iterations significantly (from 50 in existing approaches down to 1) and (ii) track time-varying systems.
+Simulation results demonstrate how the proposed reduced-communication algorithm using in-neighborhood information delivers BSI performance close to an idealized one where network-wide information is available.
 
@@
 In this section, we briefly outline the adaptive SIMO BSI algorithm proposed in \cite{blochbergerDBSI}, setting the scene for the distributed averaging scheme proposed herein.
-We refer the reader to the publication cited above for the full derivation of the algorithm.
+We refer the reader to \cite{blochbergerDBSI} for the full derivation of the algorithm.
 
 \subsection[]{Sensor network}
-We assume a set of nodes with one sensor each, that is, each node provides one signal.
+We assume a set of network nodes with one sensor each, that is, each node provides one signal.
 Let this set of nodes be \(\Mset \triangleq \{1,\ldots,M\}\) and \(\mathcal{E}\) be a set of edge tuples, which connect the nodes forming a sensor network.
-Each edge is an unordered pair of node indices \(\{i,j\} \in \mathcal{E}\), which represents the communication link between them.
+Each edge is an unordered pair of node indices \(\{i,j\} \in \mathcal{E}\), which represents the communication link, which we assume is instantaneoud and error free, between them.
 We allow \(\{i,i\} \in \mathcal{E}\), in order to simplify notation later, however, this does not represent a link but rather indicates the obvious fact that node \(i\) has information about itself.
@@
 The algorithm's consensus variable is the system's estimate, \(\hat{\h}\).
-Each node \(i\) computes the respective subvector \(\hat{\h}_i\) locally, which is the computation step of interest for this extension.
+Each node \(i\) computes the respective subvector \(\hat{\h}_i\) locally, which is the computation step of interest for the extension proposed in this paper.
 It is defined as
 \begin{equation}
-    \hat{\h_i}^{(n)} = \frac{\bar{\h}_i^{(n)}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{(n)}\|^2}}\label{eq:online_admm:consensus_update}
+    \hat{\h}_i^{(n)} = \frac{\bar{\h}_i^{(n)}}{\sqrt{\sum_{j \in \Mset} \|\bar{\h}_j^{(n)}\|^2}}\label{eq:online_admm:consensus_update}
 \end{equation}
-for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{(n)}\), a combination of neigborhood averages of local estimates and dual variables, see \cite{blochbergerDBSI}.
+for each node \(i \in \Mset\) with the local unnormalized consensus \(\bar{\h}_i^{(n)} = \bar{\w}_i^{(n)} + \frac{1}{\rho} \bar{\uu}_i^{(n-1)}\), a combination of in-neigborhood averages of node-wise local estimates \(\bar{\w}_i^{(n)}\) and dual (Lagrangian) variables \(\bar{\uu}_i^{(n-1)}\), where \(\rho\) is the ADMM penalty parameter.
+A proper introduction of these variables is unfortunately out of scope for this paper, so for details, see \cite{blochbergerDBSI}.
 The computation of the denominator of \eqref{eq:online_admm:consensus_update} requires  \(\|\bar{\h}_j^{(n)}\|\) from all nodes \(j \in \Mset\), which however, is not possible without a fully-connected network or broadcasting.
-In \cite{blochbergerDBSI}, we assume that partial squared norms are relayed throughout the network until all nodes have the information necessary.
+In \cite{blochbergerDBSI}, we assume that partial squared norms are relayed/broadcasted throughout the network until all nodes have the information necessary.
 
-In \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016},
-a global value is estimated by a related iterative averaging approach, combining values within neighborhoods until convergence to a network-wide average.
-
-Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need of network-wide data transmission.
-The approach described in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} employs a related iterative averaging scheme within a distributed gradient descent algorithm for BSI in order to estimate a global variable, however, necessitating many iterations per frame.
-To alleviate this, we further introduce an adaptive mixing factor to include instantaneous values in the recursion to separate avaraging iterations onto time frames of the adaptive algorithm.
+Subsequently, we introduce an extension to the algorithm described in \cite{blochbergerDBSI} using a fastest distributed linear averaging (FDLA) approach \cite{xiaoFastLinearIterations2004} to avoid the need for network-wide data transmission.
+A related approach described in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016} employs a similar iterative averaging scheme within a distributed gradient descent algorithm for BSI in order to estimate a global variable.
+It, however, necessitates many iterations per frame.
+To alleviate this, we further introduce an adaptive mixing factor to include instantaneous values in the recursion to separate averaging iterations onto time frames of the adaptive algorithm.
 
@@
     \vspace*{-0.6cm}
-    \caption[]{Median NPM of 30 Monte-Carlo runs over time for optimal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
+    \caption[]{Median NPM of 30 Monte-Carlo runs over time for ideal case where all node information is available (fully connected network/broadcasting), fixed values of \(\gamma_i\) with \(K \in \{1,10\}\), adaptive \(\gamma_i\) with \(K=1\).
 A moving average filter was applied to result curves for better readability (compare transparent and opaque lines).
@@
 \end{figure}
-Given that the BSI algorithm being extended \cite{blochbergerDBSI} is adaptive and the unnormalized consensus estimates \(\bar{\h}_i^{(n)}\) are therefore time-varying, computing a distributed sum of their norms has to be performed adaptively.
-The baseline approach is to compute \(K\) iterations \eqref{eq:adaptivenormest:distlincomb} per frame index \(n\).
-For the baseline iterative approach to converge, \(K\) has to be sufficiently large (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
-This is suboptimal in terms of communication cost, as each iteration requires that a node \(i\) shares the averaging variable \(\phi_i(k)\) with its neighborhood \(\Nset_i\).
+Given that the unnormalized consensus estimates \(\bar{\h}_i^{(n)}\) \cite{blochbergerDBSI} are time-varying, computing a distributed sum of their norms has to be performed adaptively as well.
+The baseline approach is to compute \(K\) iterations \eqref{eq:adaptivenormest:distlincomb} per frame index \(n\), where \(K\) has to be sufficiently large for convergence (e.g., \(K=50\) in \cite{yuDistributedBlindSystem2014,liuDistributedBlindIdentification2016}).
+This is undesirable, as each iteration requires that a node \(i\) shares the averaging variable \(\phi_i(k)\) with its neighborhood \(\Nset_i\).
 Therefore, we first propose to split iterations over time frames.
-For each \(n\), we could set the initial values \(\phi_i^{(n)}(0)\) to the result of the \(K\)-th iteration \(\phi_i^{(n-1)}(K)\) of the previous frame \(n-1\).
+One obvious approach would be - at each frame \(n\) - to set the initial values \(\phi_i^{(n)}(0)\) to the result of the \(K\)-th iteration \(\phi_i^{(n-1)}(K)\) of the previous frame \(n-1\).
 With sufficiently large \(n\), convergence will be reached even when \(K\) is chosen small.
@@
 That is, when letting \(\phi_i^{(0)}(0) = \|\bar{\h}_i^{(0)}\|\), with \(\bar{\h}_i^{(0)}\) being estimated at the inital frame \(n=0\), it converges to the sum of these initial - poor - estimates.
-Therefore, we factor in the instantaneous approximation, the weighted in-neighborhood sum \(\eta_i^{(n)} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\), which will introduce new information gained by more accurate estimates of \(\bar{\h}_i^{(n)}\).
-We add this information by linearly combining it with the \(K\)-th iterate of \(\phi_i^{(n)}(k)\) and set it as the initial value for the next frame:
+Instead, we factor in the instantaneous approximation, the weighted in-neighborhood sum \(\eta_i^{(n)} = \sum_{j \in \Nset_i} W_{ij} \|\bar{\h}_i^{(n)}\|^2\), which will introduce new information gained by more accurate estimates of \(\bar{\h}_i^{(n)}\).
+We add this information by linearly combining it with the \(K\)-th iterate of \(\phi_i^{(n-1)}(k)\) and set it as the initial value fo the following frame
 \begin{equation}
@@
 \end{equation}
-where \(\gamma_i\) is a mixing factor.
+where \(0 \leq \gamma_i \leq 1\) is a mixing factor.
 We exploit the instantaneous information \(\eta_i^{(n)}\) to find values for the mixing factor.
-If the absolute difference between subsequent frames \(| \eta_i^{(n)} - \eta_i^{(n-1)} | \to 0\), then the estimation of \(\bar{\h}_i\) is converging to a steady state.
-The algorithm's emphasis should then lie on norm estimation, i.e., the distributed averaging recursion, which means \(\gamma_i \to 0\).
-We heuristically set \(\gamma_i^{(n)}\) proportional to the absolute difference of instantaneous approximations between subsequent frames and set an upper limit at 1,
+Experimental observations show that convergence is faster with larger \(\gamma_i\), while with smaller, steady-state error is lower.
+We postulate that when the estimation of \(\bar{\h}_i\) is converging to a steady state, the absolute difference between subsequent frames \(| \eta_i^{(n)} - \eta_i^{(n-1)} | \to 0\).
+Then - after faster convergence with larger \(\gamma_i\) - the algorithm's emphasis should lie on norm estimation, i.e., the distributed averaging recursion, which means \(\gamma_i \to 0\).
+Based on this heuristic, we set \(\gamma_i^{(n)}\) proportional to the absolute difference of instantaneous approximations between subsequent frames and set an upper limit at 1,
 \begin{equation}
@@
 The initial value for \(\eta_i^{(n-1)}\) for \(n=0\) can be set to an arbitrary real number, in our case 1.
+
+The adaptive estimate \(\phi_i^{(n)}(K)\) is then used in the denominator of \eqref{eq:online_admm:consensus_update} as \(\sqrt{M \, \phi_i^{(n)}(K)}\).
 Refer to \autoref{alg:davg_norm_est} for the order of computations of the extended algorithm we introduced here.
@@
     \caption[]{Mean of 500 post-convergence frames of median NPM of 30 Monte-Carlo runs for fixed \(\gamma_i\) on the interval \([0.0, 0.04]\) and \(K \in \{1,2,10\}\).
-Results for optimal algorithm, and adaptive \(\gamma_i\) included for comparison.}
+Results for ideal algorithm, and adaptive \(\gamma_i\) included for comparison.}
     \label{fig:simulations:avgNPMgamma}
@@
 \autoref{tab:transcost:table} compares the number of transmit and receive operations node \(i\) has to apply in order to compute \eqref{eq:online_admm:consensus_update}.
-Further, it shows the complexity of the problem node \(i\) has to solve according to \cite{blochbergerDBSI} given the two types of network topology, assuming it uses all information it receives.
+Further, it shows the complexity of the local problem at node \(i\), assuming it uses all information that it receives.
 The advantage of the fully distributed algorithm becomes clear when \(M \gg N_i\), as the additional communication and local complexity depends on neighborhood size \(N_i\) and not on network size \(M\).
@@
 \subsection[]{Simulations}
-To evaluate the effectiveness of the proposed extension, simulations were run, where we define the error measure as the normalized projection misalignment
+To evaluate the effectiveness of the proposed extension, simulations were run, where we define the error measure as the normalized projection misalignment (e.g, \cite{huangAdaptiveMultichannelLeast2002,huangClassFrequencydomainAdaptive2003,habetsOnlineQuasiNewtonAlgorithm2010})
 \begin{equation}
-    \begin{aligned}
-        \text{NPM}(n) &= 20\,\log_{10} \frac{\left\| \mtxb{e} \right\|}{\left\|\hat{\h}^{(n)}\right\|},\\
-        \text{with}\quad \mtxb{e} &= \hat{\h}^{(n)} - \frac{\h^\T \hat{\h}^{(n)}}{\h^\T \h}\hat{\h}^{(n)},
-    \end{aligned}
+        \text{NPM}(n) = 20\,\log_{10} \left(\left\| \hat{\h}^{(n)} - \frac{\h^\T \hat{\h}^{(n)}}{\h^\T \h}\hat{\h}^{(n)} \right\| / \left\|\hat{\h}^{(n)}\right\|\right),
 \end{equation}
@@
     \itemsep-0.2em
-    \item[(a)] \(\|\bar{\h}_i\|^2\) of all \(i \in \Mset\) is available for global norm computation (``optimal'' in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
+    \item[(a)] \(\|\bar{\h}_i\|^2\) of all \(i \in \Mset\) is available for global norm computation (``ideal'' in \autoref{fig:simulations:NPMtime} \& \autoref{fig:simulations:avgNPMgamma}),
     \item[(b)] Inter-neighborhood communication with fixed \(\gamma_i \in [0.0, 0.4]\) and \(K \in \{1,2,10\}\),
@@
 The input signal, impulse responses, additive noise, and SNR have the same parameters as the first simulation.
-To test the algorithms response to time-varying scenarios, the 3 impulse responses are then scaled to norms of \([2.2, 0.5, 1.2],\, [2.2, 1.0, 1.2],\, [2.2, 0.5, 2.0]\) at frames \(0,\, 5000,\, 10000\) respectively.
+To test the algorithms response to time-varying scenarios, the 3 impulse responses are then scaled to norms of \(\{2.2, 0.5, 1.2\},\, \{2.2, 1.0, 1.2\},\, \{2.2, 0.5, 2.0\}\) at frames \(n \in \{0,\, 5000,\, 10000\}\) respectively.
 \autoref{fig:simulations:NPMtimedyn} (bottom) shows the median NPM of 30 Monte-Carlo runs, where we can observe very similar behavior of the optimal and distributed-averaging-based algorithms, where both algorithms reach a converged state after the rescaling events.
@@
 
-In summary, the simulations show that the right choice of fixed \(\gamma_i\) leads to results close to an optimal case even with \(K=1\) distributed averaging iterations.
+In summary, the simulations show that depending on the choice of fixed \(\gamma_i\), it can lead to results close to an idealized case even with \(K=1\) distributed averaging iterations.
 Further, introducing an adaptive \(\gamma_i^{(n)}\) allows the algorithm to converge faster and deal with time-variant systems.
-This is an improvement over \cite{blochbergerDBSI} as communication is only required within neighborhoods and over \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} needing only \(K=1\) instead of \(K=50\) iterations per frame.
+This is an improvement over \cite{blochbergerDBSI} as inter-node communication is only required within node neighborhoods and over \cite{yuDistributedBlindSystem2014, liuDistributedBlindIdentification2016} needing only \(K=1\) instead of \(K=50\) iterations per frame.
 
@@
 Dot-dashed lines are true values.
-Bottom: Median NPM, comparing optimal algorithm and proposed extended algorithm.
+Bottom: Median NPM, comparing idealized algorithm and proposed extended algorithm.
 Dashed vertical lines indicate rescaling events.}

### 2022-10-26 simulations/dynamic.py
remove non-simulation content

@@ -144,17 +144,17 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
 
 # %%
 if __name__ == "__main__":  # Necessary for module loading in condor processes :(
-    cfg = simulation.SimConfig(
-        id="icassp2023-dynamic",
-        runs=30,
-        seed=573438,
-        variables=[
-            {"alg": ["davgad", "opt"], "SNR": [10], "gamma": [0.0], "iters": [1]},
-        ],
-    )
+    # cfg = simulation.SimConfig(
+    #     id="icassp2023-dynamic",
+    #     runs=30,
+    #     seed=573438,
+    #     variables=[
+    #         {"alg": ["davgad", "opt"], "SNR": [10], "gamma": [0.0], "iters": [1]},
+    #     ],
+    # )
     # %%
     # You can save the simulation configuration to a json file
-    cfg.save("icassp2023-dynamic")
+    # cfg.save("icassp2023-dynamic")
     # %%
     # Load a saved configuration
     cfg = simulation.SimConfig.load("icassp2023-dynamic")
@@ -166,33 +166,34 @@ if __name__ == "__main__":  # Necessary for module loading in condor processes :
     # sim.clearTmpData()
     # %%
     # Run the simulation locally with n processes
-    sim.runLocal(nprocesses=8, showprogress=True)
+    sim.runLocal(nprocesses=8, showprogress=False)
     # %%
     # Get the result after completion
     result = sim.getResult()
     # %%
+    # THIS IS FOR RUNING THE SIMULTION ON A THCONDOR CLUSTER
     # Define condor job parameters
-    user_submit = {
-        "request_walltime": "3600",  # Time in seconds
-        "initialdir": ".",
-        "notification": "Error",
-        "executable": "/users/sista/mblochbe/python_venvs/admmstuff/bin/python",
-        "request_cpus": "1",
-        "request_memory": "1GB",
-    }
+    # user_submit = {
+    #     "request_walltime": "3600",  # Time in seconds
+    #     "initialdir": ".",
+    #     "notification": "Error",
+    #     "executable": "/path/to/python",
+    #     "request_cpus": "1",
+    #     "request_memory": "1GB",
+    # }
     # %%
     # Submit the condor jobs
-    sim.runCondor(user_submit)
+    # sim.runCondor(user_submit)
     # %%
     # Show status of condor jobs
-    sim.getJobStatus()
+    # sim.getJobStatus()
     # %%
[…]

### 2022-10-26 simulations/static.py

@@ -127,46 +127,46 @@ def simulate(alg, SNR, gamma, iters, run: int, seed: int):
 
 # %%
 if __name__ == "__main__":  # Necessary for module loading in condor processes :(
-    cfg = simulation.SimConfig(
-        id="icassp2023-static",
-        runs=30,
-        seed=573438,
-        variables=[
-            {"alg": ["opt"], "SNR": [10], "gamma": [1.0], "iters": [1]},
-            {"alg": ["davgad"], "SNR": [10], "gamma": [1.0], "iters": [1]},
-            {
-                "alg": ["davg"],
-                "SNR": [10],
-                "gamma": [
-                    0.0,
-                    0.002,
-                    0.004,
-                    0.006,
-                    0.008,
-                    0.01,
-                    0.012,
-                    0.014,
-                    0.016,
-                    0.018,
-                    0.02,
-                    0.022,
-                    0.024,
-                    0.026,
-                    0.028,
-                    0.03,
-                    0.032,
-                    0.034,
-                    0.036,
-                    0.038,
-                    0.04,
-                ],
-                "iters": [1, 2, 10],
-            },
-        ],
-    )
+    # cfg = simulation.SimConfig(
+    #     id="icassp2023-static",
+    #     runs=30,
+    #     seed=573438,
+    #     variables=[
+    #         {"alg": ["opt"], "SNR": [10], "gamma": [1.0], "iters": [1]},
+    #         {"alg": ["davgad"], "SNR": [10], "gamma": [1.0], "iters": [1]},
+    #         {
+    #             "alg": ["davg"],
+    #             "SNR": [10],
+    #             "gamma": [
+    #                 0.0,
+    #                 0.002,
+    #                 0.004,
+    #                 0.006,
+    #                 0.008,
+    #                 0.01,
+    #                 0.012,
+    #                 0.014,
+    #                 0.016,
+    #                 0.018,
+    #                 0.02,
+    #                 0.022,
+    #                 0.024,
+    #                 0.026,
+    #                 0.028,
+    #                 0.03,
+    #                 0.032,
+    #                 0.034,
+    #                 0.036,
+    #                 0.038,
+    #                 0.04,
+    #             ],
+    #             "iters": [1, 2, 10],
+    #         },
+    #     ],
+    # )
     # %%
[…]

### 2022-10-26 simulations/static_large.py

@@ -1,480 +1,0 @@
-# %%
-import os
-import pandas as pd
-import numpy as np
-
-# import matplotlib.pyplot as plt
-import python_utils.utils as utils
-import python_utils.simulation as simulation
-
-# %%
-# import matplotlib
-# import matplotlib.pyplot as plt
-
-# # %%
-# import matplotlib
-
-# matplotlib.use("pgf")
-# import matplotlib.pyplot as plt
-
-# plt.rcParams.update(
-#     {
-#         "font.family": "serif",  # use serif/main font for text elements
-#         "text.usetex": True,  # use inline math for ticks
-#         "pgf.rcfonts": False,  # don't setup fonts from rc parameters
-#         "font.size": 9,
-#     }
-# )
-
-
-# %%
-# Define the simulation function.
-# You can define any number of arguments instead of a, b.
-# Remember to add them in SimConfig
-# DO NOT CHANGE run and seed arguments and argument positions!
-def simulate(alg, SNR, gamma, iters, run: int, seed: int):
-    ## %%
-    # All required imports for simulation need to be in here, e.g.,
-    import numpy as np
-
-    if alg == "opt":
-        import admm_fq as adf
-    if alg == "davg":
-        import admm_fq_distavg_opt as adf
-    if alg == "davgad":
-        import admm_fq_distavg_ad as adf
-    from cvxpy import Variable, sum_squares, Minimize, Problem, vec
-
-    rng = np.random.default_rng(np.random.PCG64DXSM(seed).jumped(run))
-    ## %%
-    # ################################################################
-    # Put the simulation code here
-    N_sens = 20
-    L = 16
-
-    nw = adf.Network(L)
-
-    next_pos = np.array([0, 0])
-    node_pos = np.empty((N_sens, 2))
-    # fig = plt.figure(figsize=(8, 8))
-    nbs = []
-    ok = []
-    edges = []
-    radius = 2
-    for i in range(N_sens):
-        nw.addNode(i, 1)
-        rangle = rng.uniform(-np.pi / 4, np.pi / 4) + rng.integers(0, 2) * np.pi
-        # print(rangle)
-        # rd = rng.uniform(0.8 * radius, 0.99*radius)
-        rd = radius * 0.95
[…]

### 2022-10-26 simulations/transcost.py

@@ -1,101 +1,0 @@
-# %%
-import numpy as np
-import python_utils.utils as utils
-
-# %%
-import matplotlib
-
-matplotlib.use("pgf")
-import matplotlib.pyplot as plt
-
-plt.rcParams.update(
-    {
-        "font.family": "serif",  # use serif/main font for text elements
-        "text.usetex": True,  # use inline math for ticks
-        "pgf.rcfonts": False,  # don't setup fonts from rc parameters
-    }
-)
-
-# %%
-M = np.arange(10, 5000)
-
-# %%
-N_bar = [5, 10]
-
-# %%
-R = [1, 50]
-
-# %%
-# fig = plt.figure(figsize=(6, 4))
-# # plt.title("Title")
-# plt.xlabel("Network size M [1]")
-# plt.ylabel(r"$\log \mathcal{O}(.)$ [1]")
-# plt.plot(M,2*M**2, "k--", label="full direct")
-# plt.plot(M,M+M**2, "-.", label="broadcast")
-# for n_bar in N_bar:
-#     for r in R:
-#         plt.plot(M,M*n_bar*r + M*n_bar*r, label=r"$\bar{N}=$%d,$R=$%d"%(n_bar, r))
-# plt.legend()
-# plt.grid()
-# plt.tight_layout()
-# plt.show()
-
-# %%
-styles = ["-<", "->", "-v", "-s", "-o"]
-fig = plt.figure(figsize=utils.set_size(245, 1.0, (1, 1)))
-# plt.title("Title")
-plt.xlabel("Network size M [1]")
-plt.ylabel(r"$\mathcal{O}(.)$ [1]")
-plt.plot(M, 2 * M**2, "k-", label="full direct")
-plt.plot(M, M + M**2, "--", label="broadcast")
-ss = 0
-for n_bar in N_bar:
-    for r in R:
-        plt.plot(
-            M,
-            M * n_bar * r + M * n_bar * r,
-            styles.pop(),
-            label=r"$\bar{N}=$%d,$R=$%d" % (n_bar, r),
-            markevery=(ss, 500),
-            markersize=3,
-        )
-        ss += 50
-plt.legend(ncol=2, prop={"size": 7})
-plt.grid()
-plt.yscale("log")
-plt.xlim(0, 5000)
-plt.tight_layout()
-plt.show()
-# %%
-utils.savefig(fig, "transcost", format="pgf", pgf_font="serif")
-
-# %%
[…]
